### 2014-07-24 analysis/figures/snr.tex
Figure layout latex added

\documentclass[]{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{float}
\usepackage{graphicx}
\usepackage{hyperref}

\pagestyle{plain}

\begin{document}
\tableofcontents
\section{SSVEP}
\subsection{SSVEP 10 Hz}
\clearpage
\subsubsection{SSVEP 10 Hz (Experiment)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
& Rabbit 9 & Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Basilar Tip 1} & 
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_11_13_41_ssvep_10-crop.pdf} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_12_07_13_ssvep_10-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Mid-Basilar} & 
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_14_00_01_ssvep_10-crop.pdf} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_14_19_09_ssvep_10-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}VB Junction} & 
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_14_40_36_ssvep_10-crop.pdf} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_16_00_33_ssvep_10-crop.pdf} \\
\rotatebox{90}{\hspace{0.2cm}Cervical Ventebral Dens} & 
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_15_10_16_ssvep_10-crop.pdf} &
\includegraphics[scale=0.18,draft]{../ssvep/matlab_data/_Tue_06_05_2014_11_13_41_ssvep_10-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Basilar Tip 2} & 
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_15_46_00_ssvep_10-crop.pdf} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_16_36_31_ssvep_10-crop.pdf}
\end{tabular}
\caption{Basilar tip, Mid-Basilar, VB Junction, Cervical Ventebral Dens (not for rabbit 10), Basiliar tip.}
\end{center}
\end{figure}
\subsubsection{SSVEP 10 Hz (Live Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
& Rabbit 9 & Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Basilar Tip} & 
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_11_21_50_ssvep_10-crop.pdf} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_12_12_15_ssvep_ctr_10-crop.pdf} \\
\end{tabular}
\caption{Basilar tip. Rabbit 9 basilar tip has the experiment start/stop twice.}
\end{center}
\end{figure}
\subsubsection{SSVEP 10 Hz (Dead Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1.7cm}Unspecified} & 
\includegraphics[scale=0.30]{../ssvep/matlab_data/_Thu_15_05_2014_17_15_37_ssvep_10-crop.pdf}
\end{tabular}
\caption{Only measured for rabbit 10. Unspecified location.}
\end{center}
\end{figure}
\subsection{SSVEP 40 Hz}
\clearpage
\subsubsection{SSVEP 40 Hz (Experiment)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
& Rabbit 9 & Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Basilar Tip 1} & 
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Mid-Basilar} & 
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_14_02_01_ssvep_40-crop.pdf} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}VB Junction} & 
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_14_41_46_ssvep_40-crop.pdf} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf} \\
\rotatebox{90}{\hspace{0.2cm}Cervical Ventebral Dens} & 
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_15_11_25_ssvep_40-crop.pdf} &
\includegraphics[scale=0.18,draft]{../ssvep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Basilar Tip 2} & 
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_15_48_24_ssvep_50-crop.pdf} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}
\end{tabular}
\caption{Basilar tip, Mid-Basilar, VB Junction, Cervical Ventebral Dens (not for rabbit 10), Basiliar tip. \_Tue\_06\_05\_2014\_15\_48\_24\_ssvep appears to be mislabeled as a 50 Hz trial.}
\end{center}
\end{figure}
\subsubsection{SSVEP 40 Hz (Live Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
& Rabbit 9 & Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Basilar Tip} & 
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40-crop.pdf} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf} \\
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsubsection{SSVEP 40 Hz (Dead Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1.7cm}Unspecified} & 
\includegraphics[scale=0.30]{../ssvep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}
\end{tabular}
\caption{Only measured for rabbit 10. Unspecified location.}
\end{center}
\end{figure}
\subsection{SSVEP 50 Hz}
\clearpage
\subsubsection{SSVEP 50 Hz (Experiment)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
& Rabbit 9 & Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Basilar Tip 1} & 
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_11_16_01_ssvep_50-crop.pdf} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_12_09_32_ssvep_50-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Mid-Basilar} & 
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_14_03_09_ssvep_50-crop.pdf} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_14_21_40_ssvep_50-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}VB Junction} & 
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_14_43_48_ssvep_50-crop.pdf} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_16_04_56_ssvep_50-crop.pdf} \\
\rotatebox{90}{\hspace{0.2cm}Cervical Ventebral Dens} & 
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_15_12_40_ssvep_50-crop.pdf} &
\includegraphics[scale=0.18,draft]{../ssvep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Basilar Tip 2} & 
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_15_49_35_ssvep_40-crop.pdf} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_16_40_58_ssvep_50-crop.pdf}
\end{tabular}
\caption{Basilar tip, Mid-Basilar, VB Junction, Cervical Ventebral Dens (not for rabbit 10), Basiliar tip. \_Tue\_06\_05\_2014\_16\_38\_47\_ssvep appears to be mislabeled as a 40 Hz trial.}
\end{center}
\end{figure}
\subsubsection{SSVEP 50 Hz (Live Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
& Rabbit 9 & Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Basilar Tip} & 
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_11_24_15_ssvep_50-crop.pdf} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_12_14_36_ssvep_ctr_50-crop.pdf} \\
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsubsection{SSVEP 50 Hz (Dead Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1.7cm}Unspecified} & 
\includegraphics[scale=0.30]{../ssvep/matlab_data/_Thu_15_05_2014_17_20_11_ssvep_50-crop.pdf}
\end{tabular}
\caption{Only measured for rabbit 10. Unspecified location}
\end{center}
\end{figure}
\section{SSAEP}
\subsection{SSAEP 12 Hz}
\subsubsection{SSAEP 12 Hz (Experiment)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
& Rabbit 9 & Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Basilar Tip 1} & 
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_11_31_23_ssaep_12-crop.pdf} &
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_12_28_28_ssaep_12-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Mid-Basilar} & 
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_14_08_46_ssaep_12-crop.pdf} &
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_14_24_26_ssaep_12-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}VB Junction} & 
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_14_50_29_ssaep_12-crop.pdf} &
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_16_07_59_ssaep_12-crop.pdf} \\
\rotatebox{90}{\hspace{0.2cm}Cervical Ventebral Dens} & 
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_15_18_04_ssaep_12-crop.pdf} &
\includegraphics[scale=0.18,draft]{../ssvep/matlab_data/_Tue_06_05_2014_11_13_41_ssvep_10-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Basilar Tip 2} & 
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_15_55_07_ssaep_12-crop.pdf} &
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_16_54_15_ssaep_12-crop.pdf}
\end{tabular}
\caption{Basilar tip, Mid-Basilar, VB Junction, Cervical Ventebral Dens (not for rabbit 10), Basiliar tip.}
\end{center}
\end{figure}
\subsubsection{SSAEP 12 Hz (Live Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
& Rabbit 9 & Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Basilar Tip} & 
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_11_39_46_ssaep_12-crop.pdf} &
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_12_23_40_ssaep_ctr_12-crop.pdf} \\
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsubsection{SSAEP 12 Hz (Dead Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1.7cm}Unspecified} & 
\includegraphics[scale=0.30]{../ssaep/matlab_data/_Thu_15_05_2014_17_08_12_ssaep_12-crop.pdf} &
\end{tabular}
\caption{Only measured for rabbit 10. Unspecified location}
\end{center}
\end{figure}
\subsection{SSAEP 42 Hz}
\subsubsection{SSAEP 42 Hz (Experiment)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
& Rabbit 9 & Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Basilar Tip 1} & 
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_11_36_06_ssaep_42-crop.pdf} &
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_12_29_48_ssaep_42-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Mid-Basilar} & 
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_14_09_59_ssaep_42-crop.pdf} &
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_14_25_41_ssaep_42-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}VB Junction} & 
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_14_51_59_ssaep_42-crop.pdf} &
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_16_10_09_ssaep_42-crop.pdf} \\
\rotatebox{90}{\hspace{0.2cm}Cervical Ventebral Dens} & 
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_15_19_16_ssaep_42-crop.pdf} &
\includegraphics[scale=0.18,draft]{../ssvep/matlab_data/_Tue_06_05_2014_11_13_41_ssvep_10-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Basilar Tip 2} & 
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_15_56_42_ssaep_42-crop.pdf} &
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_16_56_24_ssaep_42-crop.pdf}
\end{tabular}
\caption{Basilar tip, Mid-Basilar, VB Junction, Cervical Ventebral Dens (not for rabbit 10), Basiliar tip.}
\end{center}
\end{figure}
\subsubsection{SSAEP 42 Hz (Live Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
& Rabbit 9 & Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Basilar Tip} & 
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_11_41_03_ssaep_42-crop.pdf} &
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_12_24_55_ssaep_ctr_42-crop.pdf} \\
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsubsection{SSAEP 42 Hz (Dead Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1.7cm}Unspecified} & 
\includegraphics[scale=0.30]{../ssaep/matlab_data/_Thu_15_05_2014_17_10_30_ssaep_42-crop.pdf}
\end{tabular}
\caption{Only measured for rabbit 10. Unspecified location}
\end{center}
\end{figure}
\subsection{SSAEP 86 Hz}
\subsubsection{SSAEP 86 Hz (Experiment)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
& Rabbit 9 & Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Basilar Tip 1} & 
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf} &
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Mid-Basilar} & 
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_14_11_09_ssaep_86-crop.pdf} &
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}VB Junction} & 
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_14_53_21_ssaep_86-crop.pdf} &
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{0.2cm}Cervical Ventebral Dens} & 
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_15_20_29_ssaep_86-crop.pdf} &
\includegraphics[scale=0.18,draft]{../ssvep/matlab_data/_Tue_06_05_2014_11_13_41_ssvep_10-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Basilar Tip 2} & 
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_15_57_52_ssaep_86-crop.pdf} &
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}
\end{tabular}
\caption{Basilar tip, Mid-Basilar, VB Junction, Cervical Ventebral Dens (not for rabbit 10), Basiliar tip.}
\end{center}
\end{figure}
\subsubsection{SSAEP 86 Hz (Live Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
& Rabbit 9 & Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Basilar Tip} & 
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86-crop.pdf} &
\includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf} \\
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsubsection{SSAEP 86 Hz (Dead Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1.7cm}Unspecified} & 
\includegraphics[scale=0.30]{../ssaep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}
\end{tabular}
\caption{Only measured for rabbit 10. Unspecified location}
\end{center}
\end{figure}
\end{document}

### 2014-07-24 analysis/figures/snr_tip.tex
Figure layout latex added

\documentclass[]{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{float}
\usepackage{graphicx}
\usepackage{hyperref}

\pagestyle{plain}

\begin{document}
\tableofcontents
\section{SSVEP}
\subsection{SSVEP 10 Hz}
\clearpage
\subsubsection{SSVEP 10 Hz (Experiment)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 9 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_11_13_41_ssvep_10-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Hub} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_12_03_34_ssvep_10-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Ag/AgCl} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_12_29_43_ssvep_10-crop.pdf} \\
\rotatebox{90}{\hspace{0.2cm}Guidewire @ 10cm from catheter tip} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_13_17_59_ssvep_10-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip} & \includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_12_07_13_ssvep_10-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Coil}            & \includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_13_20_12_ssvep_10-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsubsection{SSVEP 10 Hz (Live Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 9 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_11_21_50_ssvep_10-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Hub} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_12_11_10_ssvep_10-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Ag/AgCl} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_12_22_36_ssvep_10-crop.pdf} \\
\rotatebox{90}{\hspace{0.2cm}Guidewire @ 10cm from catheter tip} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_13_25_33_ssvep_10-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip} & \includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_12_12_15_ssvep_ctr_10-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Coil}            & \includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_13_25_05_ssvep_ctr_10-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsubsection{SSVEP 10 Hz (Dead Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}???} & \includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_17_15_37_ssvep_10-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsection{SSVEP 40 Hz}
\subsubsection{SSVEP 40 Hz (Experiment)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 9 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Hub} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_12_04_50_ssvep_40-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Ag/AgCl} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_12_30_51_ssvep_40-crop.pdf} \\
\rotatebox{90}{\hspace{0.2cm}Guidewire @ 10cm from catheter tip} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_13_19_10_ssvep_40-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip} & \includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Coil}            & \includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_13_21_25_ssvep_40-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsubsection{SSVEP 40 Hz (Live Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 9 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Hub} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_12_12_21_ssvep_40-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Ag/AgCl} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_12_23_46_ssvep_40-crop.pdf} \\
\rotatebox{90}{\hspace{0.2cm}Guidewire @ 10cm from catheter tip} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_13_26_44_ssvep_40-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip} & \includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Coil}            & \includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_13_26_16_ssvep_ctr_40-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsubsection{SSVEP 40 Hz (Dead Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}???} & \includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsection{SSVEP 50 Hz}
\subsubsection{SSVEP 50 Hz (Experiment)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 9 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_11_16_01_ssvep_50-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Hub} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_12_05_58_ssvep_50-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Ag/AgCl} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_12_32_00_ssvep_50-crop.pdf} \\
\rotatebox{90}{\hspace{0.2cm}Guidewire @ 10cm from catheter tip} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_13_20_19_ssvep_50-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip} & \includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_12_09_32_ssvep_50-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Coil}            & \includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_13_22_37_ssvep_50-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsubsection{SSVEP 50 Hz (Live Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 9 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_11_24_15_ssvep_50-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Hub} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_12_13_29_ssvep_50-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Ag/AgCl} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_12_24_55_ssvep_50-crop.pdf} \\
\rotatebox{90}{\hspace{0.2cm}Guidewire @ 10cm from catheter tip} &
\includegraphics[scale=0.18]{../ssvep/matlab_data/_Tue_06_05_2014_13_27_53_ssvep_50-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip} & \includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_12_14_36_ssvep_ctr_50-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Coil}            & \includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_13_27_27_ssvep_ctr_50-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsubsection{SSVEP 50 Hz (Dead Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}???} & \includegraphics[scale=0.18]{../ssvep/matlab_data/_Thu_15_05_2014_17_20_11_ssvep_50-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\section{SSAEP}
\subsection{SSAEP 12 Hz}
\subsubsection{SSAEP 12 Hz (Experiment)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 9 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip}                      & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_11_31_23_ssaep_12-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Hub}                      & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_11_55_37_ssaep_12-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Ag/AgCl}                              & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_12_38_56_ssaep_12-crop.pdf} \\
\rotatebox{90}{\hspace{0.2cm}Guidewire @ 10cm from catheter tip} & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_13_03_56_ssaep_12-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip} & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_12_28_28_ssaep_12-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Coil}            & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_13_35_22_ssaep_12-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsubsection{SSAEP 12 Hz (Live Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 9 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip}                      & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_11_39_46_ssaep_12-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Hub}                      & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_11_51_43_ssaep_12-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Ag/AgCl}                              & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_12_43_40_ssaep_12-crop.pdf} \\
\rotatebox{90}{\hspace{0.2cm}Guidewire @ 10cm from catheter tip} & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_13_09_08_ssaep_12-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip} & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_12_23_40_ssaep_ctr_12-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Coil}            & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_13_40_19_ssaep_ctr_12-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsubsection{SSAEP 12 Hz (Dead Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}???} & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_17_08_12_ssaep_12-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsection{SSAEP 42 Hz}
\subsubsection{SSAEP 42 Hz (Experiment)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 9 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip}                      & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_11_36_06_ssaep_42-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Hub}                      & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_11_56_47_ssaep_42-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Ag/AgCl}                              & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_12_40_15_ssaep_42-crop.pdf} \\
\rotatebox{90}{\hspace{0.2cm}Guidewire @ 10cm from catheter tip} & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_13_06_20_ssaep_42-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip} & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_12_29_48_ssaep_42-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Coil}            & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_13_36_42_ssaep_42-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsubsection{SSAEP 42 Hz (Live Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 9 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip}                      & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_11_41_03_ssaep_42-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Hub}                      & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_11_52_54_ssaep_42-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Ag/AgCl}                              & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_12_44_55_ssaep_42-crop.pdf} \\
\rotatebox{90}{\hspace{0.2cm}Guidewire @ 10cm from catheter tip} & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_13_10_18_ssaep_42-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip} & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_12_24_55_ssaep_ctr_42-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Coil}            & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_13_41_32_ssaep_ctr_42-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsubsection{SSAEP 42 Hz (Dead Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}???} & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_17_10_30_ssaep_42-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsection{SSAEP 86 Hz}
\subsubsection{SSAEP 86 Hz (Experiment)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 9 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip}                      & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Hub}                      & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_11_58_00_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Ag/AgCl}                              & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_12_41_28_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{0.2cm}Guidewire @ 10cm from catheter tip} & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_13_07_35_ssaep_86-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip} & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Coil}            & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_13_38_08_ssaep_86-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsubsection{SSAEP 86 Hz (Live Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 9 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip}                      & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Hub}                      & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_11_54_01_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Ag/AgCl}                              & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_12_46_06_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{0.2cm}Guidewire @ 10cm from catheter tip} & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Tue_06_05_2014_13_12_42_ssaep_86-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}Guidewire @ Tip} & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Coil}            & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_13_42_44_ssaep_ctr_86-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\subsubsection{SSAEP 86 Hz (Dead Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
& Rabbit 10 \\
\rotatebox{90}{\hspace{1cm}???} & \includegraphics[scale=0.18]{../ssaep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}
\end{tabular}
\caption{Basilar tip.}
\end{center}
\end{figure}
\end{document}

### 2014-07-24 analysis/figures/vep.tex
Figure layout latex added

\documentclass[]{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}

\pagestyle{plain}

\begin{document}

\tableofcontents

\section{Rabbit 9}
\subsection{Rabbit 9 (Experiment)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
Rabbit 9 & Early & Late \\
\rotatebox{90}{\hspace{0.0cm}Basilar Tip, wire@tip} & \includegraphics[scale=0.2]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf} & \includegraphics[scale=0.2]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep__late-crop.pdf} \\
%\rotatebox{90}{\hspace{0cm}Basilar Tip, guidewire@hub} & \includegraphics[scale=0.2]{../vep/matlab_data/_Tue_06_05_2014_12_07_06_vep_-crop.pdf} & \includegraphics[scale=0.2]{../vep/matlab_data/_Tue_06_05_2014_12_07_06_vep__late-crop.pdf} \\
%\rotatebox{90}{\hspace{0cm}Basilar Tip, Ag/AgCl}   & \includegraphics[scale=0.2]{../vep/matlab_data/_Tue_06_05_2014_12_33_09_vep_-crop.pdf} & \includegraphics[scale=0.2]{../vep/matlab_data/_Tue_06_05_2014_12_33_09_vep__late-crop.pdf} \\
\rotatebox{90}{\hspace{0cm}Basilar Tip, wire@10cm}& \includegraphics[scale=0.2]{../vep/matlab_data/_Tue_06_05_2014_13_21_31_vep_-crop.pdf} & \includegraphics[scale=0.2]{../vep/matlab_data/_Tue_06_05_2014_13_21_31_vep__late-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Mid-Basilar}                & \includegraphics[scale=0.2]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep_-crop.pdf} & \includegraphics[scale=0.2]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep__late-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}VB junction}                & \includegraphics[scale=0.2]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep_-crop.pdf} & \includegraphics[scale=0.2]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep__late-crop.pdf} \\
\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens}    & \includegraphics[scale=0.2]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep_-crop.pdf} & \includegraphics[scale=0.2]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep__late-crop.pdf} \\
\rotatebox{90}{\hspace{1cm}Basilar Tip}                & \includegraphics[scale=0.2]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep_-crop.pdf} & \includegraphics[scale=0.2]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep__late-crop.pdf} 
\end{tabular}
\caption{Rabbit 9 Experiment. TODO: write down data analysis conditions (filter - high, low, notch - parameters)}
\end{center}
\end{figure}

\subsection{Rabbit 9 (Live Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
Rabbit 9 & Early & Late \\
\rotatebox{90}{\hspace{0cm}Basilar Tip, guidewire@tip} & \includegraphics[scale=0.23]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep_-crop.pdf} & \includegraphics[scale=0.23]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep__late-crop.pdf} \\
\rotatebox{90}{\hspace{0cm}Basilar Tip, guidewire@hub} & \includegraphics[scale=0.23]{../vep/matlab_data/_Tue_06_05_2014_12_14_37_vep_-crop.pdf} & \includegraphics[scale=0.23]{../vep/matlab_data/_Tue_06_05_2014_12_14_37_vep__late-crop.pdf} \\
\rotatebox{90}{\hspace{0cm}Basilar Tip, Ag/AgCl}       & \includegraphics[scale=0.23]{../vep/matlab_data/_Tue_06_05_2014_12_26_04_vep_-crop.pdf} & \includegraphics[scale=0.23]{../vep/matlab_data/_Tue_06_05_2014_12_26_04_vep__late-crop.pdf} \\
\rotatebox{90}{\hspace{0cm}Basilar Tip, guidewire@10cm}& \includegraphics[scale=0.23]{../vep/matlab_data/_Tue_06_05_2014_13_30_15_vep_-crop.pdf} & \includegraphics[scale=0.23]{../vep/matlab_data/_Tue_06_05_2014_13_30_15_vep__late-crop.pdf} 
\end{tabular}
\caption{Rabbit 9 Live Control. TODO: write down data analysis conditions (filter - high, low, notch - parameters)}
\end{center}
\end{figure}

\section{Rabbit 10}
\subsection{Rabbit 10 (Experiment)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
Rabbit 10 & Early & Late \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip, guidewire} & \includegraphics[scale=0.23]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf} & \includegraphics[scale=0.23]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__late-crop.pdf} \\ % Position: Basilar Tip, Electrode: Guidewire
\rotatebox{90}{\hspace{0.5cm}Basilar Tip, coil} & \includegraphics[scale=0.23]{../vep/matlab_data/_Thu_15_05_2014_13_13_47_vep_-crop.pdf} & \includegraphics[scale=0.23]{../vep/matlab_data/_Thu_15_05_2014_13_13_47_vep__late-crop.pdf} \\ % Position: Basilar Tip, Electrode: Coil
\rotatebox{90}{\hspace{1cm}Mid-Basilar} & \includegraphics[scale=0.23]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf} & \includegraphics[scale=0.23]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__late-crop.pdf} \\ % Position: Mid-Basilar, Electrode: X-pedion 10 guidewire
\rotatebox{90}{\hspace{1cm}Vertebro-basilar} & \includegraphics[scale=0.23]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf} & \includegraphics[scale=0.23]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep__late-crop.pdf} \\ % Position: Vertebro-basilar (VB) Junction, Electrode: X-pedion 10 guidewire
%\includegraphics[scale=0.23]{../vep/matlab_data/_Thu_15_05_2014_16_32_25_vep_-crop.pdf} \\ % Position: Basilar Tip, Electrode: X-pedion 10 guidewire
%\includegraphics[scale=0.23]{../vep/matlab_data/_Thu_15_05_2014_16_43_27_vep_-crop.pdf} \\ % Position: Basilar Tip, Electrode: X-pedion 10 guidewire
\rotatebox{90}{\hspace{1cm}Basilar Tip} & \includegraphics[scale=0.23]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf} & \includegraphics[scale=0.23]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep__late-crop.pdf} \\ % Position: Basilar Tip, Electrode: X-pedion 10 guidewire
\end{tabular}
\caption{Rabbit 10. TODO: write down data analysis conditions (filter - high, low, notch - parameters)}
\end{center}
\end{figure}

\subsection{Rabbit 10 (Live Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
Rabbit 10 & Early & Late \\
\rotatebox{90}{\hspace{0cm}Basilar Tip, guidewire@tip} & \includegraphics[scale=0.23]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf} & \includegraphics[scale=0.23]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_late-crop.pdf} \\
\rotatebox{90}{\hspace{0.6cm}Basilar Tip, coil}          & \includegraphics[scale=0.23]{../vep/matlab_data/_Thu_15_05_2014_13_28_55_vep_ctr-crop.pdf} & \includegraphics[scale=0.23]{../vep/matlab_data/_Thu_15_05_2014_13_28_55_vep_ctr_late-crop.pdf} 
\end{tabular}
\caption{Rabbit 10 Live Control. TODO: write down data analysis conditions (filter - high, low, notch - parameters)}
\end{center}
\end{figure}

\subsection{Rabbit 10 (Dead Control)}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
Rabbit 10 & Early & Late \\
\rotatebox{90}{\hspace{1cm}Unknown} & \includegraphics[scale=0.23]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf} & \includegraphics[scale=0.23]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep__late-crop.pdf}
\end{tabular}
\caption{Rabbit 10 Dead Control. TODO: write down data analysis conditions (filter - high, low, notch - parameters)}
\end{center}
\end{figure}
%PSD is computed with overlapping window -- how does this affect results?
%fourier transform vs power spectral density
%options for computing in matlab
%why does overlap produce better curves, peaks where you expect them to be
%
%two interpretations of snr
% - noise is just power
% - noise is variance/std of power
%
%mark off multiples of 60 Hz
%
%\section{PSD vs. DFT}
%\subsection{PSD}
%http://en.wikipedia.org/wiki/Welch's\_method
%http://en.wikipedia.org/wiki/Bartlett\%27s\_method
%http://en.wikipedia.org/wiki/Periodogram
%
%\begin{align*}
%\frac{T}{2}a &= \sum f(t)\cos(kt)
%\frac{T}{2}b &= \sum f(t)\sin(kt)
%r &= \sqrt{a^2 + b^2}
%\end{align*}
%
%\subsection{FFT}
%\begin{align*}
%X_k &= \sum_{n=0}^{N-1}x_ne^{-i2\pi k\frac{n}{N}} = c+di \\
%&= \sum_{n=0}^{N-1}x_n\left(\cos(2\pi k\frac{n}{N}) + i\sin(2\pi k\frac{n}{N})\right)
%r &= |X_k| = \sqrt{c^2+d^2}
%\end{align*}

\end{document}

### 2014-07-24 analysis/figures/figures.tex
Figure layout

\documentclass[]{article}

\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}

\pagestyle{plain}

% scale:
% 0.161
% 0.126
% 0.126
\begin{document}
\begin{figure}[H]
\begin{center}
\includegraphics{brain.pdf} \\
\vspace{0.5cm}
\begin{tabular}{cccc}
& VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf} &
\includegraphics[scale=0.126]{../ssvep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf} &
\includegraphics[scale=0.126]{../ssaep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf} &
\includegraphics[scale=0.126]{../ssvep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf} &
\includegraphics[scale=0.126]{../ssaep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf} &
\includegraphics[scale=0.126]{../ssvep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf} &
\includegraphics[scale=0.126]{../ssaep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf} &
\includegraphics[scale=0.126]{../ssvep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf} &
\includegraphics[scale=0.126]{../ssaep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}
\end{tabular}
\caption{Rabbit 10 experimental responses.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf} &
\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40-crop.pdf} &
\includegraphics[scale=0.126]{../ssaep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}
\end{tabular}
\caption{Rabbit 10 live control.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\includegraphics{brain.pdf} \\
\vspace{0.5cm}
\begin{tabular}{cccc}
& VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf} &
\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf} &
\includegraphics[scale=0.126]{../ssaep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep_-crop.pdf} &
\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_14_02_01_ssvep_40-crop.pdf} &
\includegraphics[scale=0.126]{../ssaep/matlab_data/_Tue_06_05_2014_14_11_09_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep_-crop.pdf} &
\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_14_41_46_ssvep_40-crop.pdf} &
\includegraphics[scale=0.126]{../ssaep/matlab_data/_Tue_06_05_2014_14_53_21_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep_-crop.pdf} &
\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_15_11_25_ssvep_40-crop.pdf} &
\includegraphics[scale=0.126]{../ssaep/matlab_data/_Tue_06_05_2014_15_20_29_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep_-crop.pdf} &
\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_15_48_24_ssvep_50-crop.pdf} &
\includegraphics[scale=0.126]{../ssaep/matlab_data/_Tue_06_05_2014_15_57_52_ssaep_86-crop.pdf}
\end{tabular}
\caption{Rabbit 9 experimental responses.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep_-crop.pdf} &
\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40-crop.pdf} &
\includegraphics[scale=0.126]{../ssaep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86-crop.pdf}
\end{tabular}
\caption{Rabbit 9 live control.}
\end{center}
\end{figure}

\end{document}

### 2014-07-25 analysis/figures/figures_combined.tex
VEP On/Off in one figure, SSVEP/SSAEP in another

\documentclass[]{article}

\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}

\pagestyle{plain}

% scale:
% 0.161
% 0.126
% 0.126

% 0.161
% 0.126
% 0.126
\begin{document}
%\begin{minipage}{6in}
%\centering
%\raisebox{-0.5\height}{\includegraphics[height=0.75in]{brain.pdf}}
%\hspace*{.2in}
%\raisebox{-0.5\height}{\includegraphics[height=0.3in]{brain.pdf}}
%\end{minipage}

\begin{figure}[H]
\begin{center}
\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
\hspace{0.2cm}
\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
\vspace{0.5cm}
\begin{tabular}{cccc}
& VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf} &
\includegraphics[scale=0.161]{../ssvep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf} &
\includegraphics[scale=0.161]{../ssaep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf} &
\includegraphics[scale=0.161]{../ssvep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf} &
\includegraphics[scale=0.161]{../ssaep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf} &
\includegraphics[scale=0.161]{../ssvep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf} &
\includegraphics[scale=0.161]{../ssaep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf} &
\includegraphics[scale=0.161]{../ssvep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf} &
\includegraphics[scale=0.161]{../ssaep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}
\end{tabular}
\caption{Rabbit 10 experimental responses.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf} &
\includegraphics[scale=0.161]{../ssvep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf} &
\includegraphics[scale=0.161]{../ssaep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}
\end{tabular}
\caption{Rabbit 10 live control.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
\hspace{0.2cm}
\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
\vspace{0.5cm}
\begin{tabular}{cccc}
& VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf} &
\includegraphics[scale=0.161]{../ssvep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf} &
\includegraphics[scale=0.161]{../ssaep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep_-crop.pdf} &
\includegraphics[scale=0.161]{../ssvep/matlab_data/_Tue_06_05_2014_14_02_01_ssvep_40-crop.pdf} &
\includegraphics[scale=0.161]{../ssaep/matlab_data/_Tue_06_05_2014_14_11_09_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep_-crop.pdf} &
\includegraphics[scale=0.161]{../ssvep/matlab_data/_Tue_06_05_2014_14_41_46_ssvep_40-crop.pdf} &
\includegraphics[scale=0.161]{../ssaep/matlab_data/_Tue_06_05_2014_14_53_21_ssaep_86-crop.pdf} \\
%\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
%\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep_-crop.pdf} &
%\includegraphics[scale=0.161]{../ssvep/matlab_data/_Tue_06_05_2014_15_11_25_ssvep_40-crop.pdf} &
%\includegraphics[scale=0.161]{../ssaep/matlab_data/_Tue_06_05_2014_15_20_29_ssaep_86-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep_-crop.pdf} &
\includegraphics[scale=0.161]{../ssvep/matlab_data/_Tue_06_05_2014_15_48_24_ssvep_50-crop.pdf} &
\includegraphics[scale=0.161]{../ssaep/matlab_data/_Tue_06_05_2014_15_57_52_ssaep_86-crop.pdf}
\end{tabular}
\caption{Rabbit 9 experimental responses.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep_-crop.pdf} &
\includegraphics[scale=0.161]{../ssvep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40-crop.pdf} &
\includegraphics[scale=0.161]{../ssaep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86-crop.pdf}
\end{tabular}
\caption{Rabbit 9 live control.}
\end{center}
\end{figure}

\end{document}

### 2014-07-27 analysis/figures/vep_all.tex
Latex for all VEP curves

\documentclass[]{article}

\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}

\pagestyle{plain}

% scale:
% 0.161
% 0.126
% 0.126

% 0.161
% 0.126
% 0.126
\begin{document}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
%& VEP On Response \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__all.png} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__all.png} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep__all.png} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep__all.png}
\end{tabular}
\caption{Rabbit 10 experimental VEP.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{c}
%VEP On Response & VEP Off Response \\
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_all.png}
\end{tabular}
\caption{Rabbit 10 live control VEP.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
%& VEP On Response \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep__all.png} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep__all.png} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep__all.png} \\
\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep__all.png} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep__all.png}
\end{tabular}
\caption{Rabbit 9 experimental responses.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{c}
%VEP On Response & VEP Off Response \\
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep__all.png}
\end{tabular}
\caption{Rabbit 9 live control.}
\end{center}
\end{figure}
\end{document}

### 2014-07-30 analysis/qrs/main.m
Code to plot qrs complex

@@ -1,0 +1,190 @@
+clear;
+close all;
+
+addpath('../utilities');
+
+%% Constants
+channelNames_VEP = {'Disconnected','Endo','Mid head','Disconnected','Right Eye','Right Leg','Back Head','Left Eye','Bottom Precordial','Top Precordial'};
+maxNumberOfChannels = 10;
+digitalinCh = 65;
+channelToPlot = [2,3,5,7,8];
+%channelToPlot = [2];
+fs = 9600;
+
+CM = [hex2dec('e9'), hex2dec('00'), hex2dec('3a');
+      hex2dec('ff'), hex2dec('ba'), hex2dec('00');
+      hex2dec('40'), hex2dec('40'), hex2dec('ff');
+      hex2dec('58'), hex2dec('e0'), hex2dec('00');
+      hex2dec('b0'), hex2dec('00'), hex2dec('b0')];
+
+CM = CM/256;
+
+
+%% Filters
+hp = fdesign.highpass('Fst,Fp,Ast,Ap',(2.0),(10.0),90,1,fs);
+hpf = design(hp, 'butter');
+
+lp = fdesign.lowpass('Fp,Fst,Ap,Ast',(220.0),(256.0),1,90,fs);
+lpf = design(lp, 'butter');
+
+n60 = fdesign.notch('N,F0,BW,Ap',6,60,20,2,fs);
+n120 = fdesign.notch('N,F0,Q,Ap',6,120,10,1,fs);
+n180 = fdesign.notch('N,F0,Q,Ap',6,180,10,1,fs);
+nf60 = design(n60);
+nf120 = design(n120);
+nf180 = design(n180);
+
+for rabbit_ID = {'9rabbit_may_6_2014', '10rabbit_may_15_2014'}
+    rabbit_ID = rabbit_ID{1};
+    fprintf('rabbit_ID: %s\n', rabbit_ID);
+
+    switch rabbit_ID
+        case '9rabbit_may_6_2014'
+            vep_indices = [10 2 10 11 12 13 3];
+            ssvep_indices = [5 29 32 38 8];
+            ssaep_indices = [8 32 35 41 11];
+        case '10rabbit_may_15_2014'
+            vep_indices = [4 10 12 15 5];
+            ssvep_indices = [11 23 32 35 14];
+            ssaep_indices = [15 24 33 36 12];
+    end
+
+    pathname_comments = ['../../../../data/easter/' rabbit_ID '/neuro/neuro_experiment_log.txt'];
+
+    fid = fopen(pathname_comments);
[…]

### 2014-07-30 analysis/qrs/qrs_plot.m
Fixed centering issues

@@ -61,7 +61,7 @@ function [] = qrs_plot(chData, cardiacData, name, color, f1, f2, f3, f4, f5)
         scatter(1:numel(dt), dt / 9600 * 1000, 36, color);
         xlabel('Interval Number');
         ylabel('Interval Length (ms)');
-        title('Time Between R Peaks');
+        title('Time Between Complexes');
         xlim([0 numel(dt)]);
         ylim([150 300]);
     
@@ -87,12 +87,16 @@ function [] = qrs_plot(chData, cardiacData, name, color, f1, f2, f3, f4, f5)
     assert(all(r_peak < finish));
 
     dt = finish - start;
+    max_before = max(r_peak - start);
+    max_after = max(finish - r_peak);
+    median_before = median(r_peak - start);
+    median_after = median(finish - r_peak);
 
     %% Gather and align the channel data
     %padded = nan(numel(r_peak), max(dt));
-    padded = zeros(numel(r_peak), max(dt));
+    padded = zeros(numel(r_peak), max_before + max_after);
     for i = 1:numel(r_peak)
-        padded(i, 1:(finish(i)-start(i))) = chData(start(i):(finish(i)-1));
+        padded(i, (start(i):(finish(i)-1)) - r_peak(i) + max_before + 1) = chData(start(i):(finish(i)-1));
     end
 
     %% Check that every column/row has a non-nan value
@@ -111,16 +115,17 @@ function [] = qrs_plot(chData, cardiacData, name, color, f1, f2, f3, f4, f5)
         %% Plot Mean and Confidence Interval
         figure(f4);
         hold on;
-        plot((1:numel(qrs)) / 9600, qrs, 'color', color, 'linewidth', 2);
+        plot(((1:numel(qrs)) - max_before) / 9600, qrs, 'color', color, 'linewidth', 2);
         confMean = bootci(100, @nanmean, padded);
-        plot((1:numel(qrs)) / 9600, confMean(1,:),'--','color',color,'linewidth',2);
-        plot((1:numel(qrs)) / 9600, confMean(2,:),'--','color',color,'linewidth',2);
+        plot(((1:numel(qrs)) - max_before) / 9600, confMean(1,:),'--','color',color,'linewidth',2);
+        plot(((1:numel(qrs)) - max_before) / 9600, confMean(2,:),'--','color',color,'linewidth',2);
     
         xlabel('Time (seconds)');
[…]

### 2014-07-30 analysis/qrs/main.m
Moved save outside (skip repeated saves)

@@ -179,9 +179,30 @@ for rabbit_ID = {'9rabbit_may_6_2014', '10rabbit_may_15_2014'}
 
             end
 
-            qrs_plot(0.2 * cardiacData, cardiacData, name, 'black', f1, f2, f3, f4, f5);
+            qrs_plot(0.15 * cardiacData, cardiacData, name, 'black', f1, f2, f3, f4, f5);
 
             ansdkasnd
+
+            %saveas(f1, ['matlab_data/' name '_' int2str(channel) '_r_peak.fig']);
+            saveas(f1, ['matlab_data/' name '_r_peak.fig']);
+
+            %saveas(f1, ['matlab_data/' name '_' int2str(channel) '_dt.fig']);
+            %save2pdf(['matlab_data/' name '_' int2str(channel) '_dt.pdf'], f2, 1200);
+            saveas(f2, ['matlab_data/' name '_dt.fig']);
+            save2pdf(['matlab_data/' name '_dt.pdf'], f2, 1200);
+
+            %saveas(f1, ['matlab_data/' name '_' int2str(channel) '_dt.fig']);
+            %save2pdf(['matlab_data/' name '_' int2str(channel) '_dt.pdf'], f3, 1200);
+            saveas(f3, ['matlab_data/' name '_dt.fig']);
+            save2pdf(['matlab_data/' name '_dt.pdf'], f3, 1200);
+
+            %save2pdf(['matlab_data/' name '_' int2str(channel) '_qrs.pdf'], f4, 1200);
+            save2pdf(['matlab_data/' name '_qrs.pdf'], f4, 1200);
+
+
+            %save2pdf(['matlab_data/' name '_' int2str(channel) '_qrs_all.pdf'], f3, 1200);
+            save2pdf(['matlab_data/' name '_qrs_all.pdf'], f5, 1200);
+
             close all;
 
         end

### 2014-07-30 analysis/qrs/qrs_plot.m

@@ -23,9 +23,6 @@ function [] = qrs_plot(chData, cardiacData, name, color, f1, f2, f3, f4, f5)
         ylabel('$\mu V$', 'interpreter', 'LaTeX');
         title('Detected R Wave');
         xlim([0 numel(cardiacData) / 9600]);
-    
-        %saveas(f1, ['matlab_data/' name '_' int2str(channel) '_r_peak.fig']);
-        saveas(f1, ['matlab_data/' name '_r_peak.fig']);
     end
 
     if (nargin >= 6 && f2 ~= 0)
@@ -45,11 +42,6 @@ function [] = qrs_plot(chData, cardiacData, name, color, f1, f2, f3, f4, f5)
         %figure(f1);
         %xlim(locs(b) / 9600 + [-0.4 0.4]);
         %locs(b + (-1:1)) / 9600 * 1000
-    
-        %saveas(f1, ['matlab_data/' name '_' int2str(channel) '_dt.fig']);
-        %save2pdf(['matlab_data/' name '_' int2str(channel) '_dt.pdf'], f2, 1200);
-        saveas(f2, ['matlab_data/' name '_dt.fig']);
-        save2pdf(['matlab_data/' name '_dt.pdf'], f2, 1200);
     end
 
     %% Compute interval (include first, exclude last)
@@ -69,11 +61,6 @@ function [] = qrs_plot(chData, cardiacData, name, color, f1, f2, f3, f4, f5)
         %figure(f1);
         %xlim(locs(b) / 9600 + [-0.4 0.4]);
         %locs(b + (-1:1)) / 9600 * 1000
-    
-        %saveas(f1, ['matlab_data/' name '_' int2str(channel) '_dt.fig']);
-        %save2pdf(['matlab_data/' name '_' int2str(channel) '_dt.pdf'], f3, 1200);
-        saveas(f3, ['matlab_data/' name '_dt.fig']);
-        save2pdf(['matlab_data/' name '_dt.pdf'], f3, 1200);
     end
 
     %% Compute start, R peak, end, and length of each interval
@@ -128,9 +115,6 @@ function [] = qrs_plot(chData, cardiacData, name, color, f1, f2, f3, f4, f5)
         ylim([-120 120]);
         set(findall(f4,'type','text'),'fontSize',40,'fontWeight','normal', 'color', [0,0,0]);
         set(gca,'FontSize',40);
-    
[…]

### 2014-07-30 analysis/qrs/main.m
Plot cardiac as first.

@@ -161,6 +161,8 @@ for rabbit_ID = {'9rabbit_may_6_2014', '10rabbit_may_15_2014'}
             f4 = figure('units', 'pixels', 'outerposition', [0 0 1366 768]);
             f5 = figure('units', 'pixels', 'outerposition', [0 0 1366 768]);
 
+            qrs_plot(0.125 * cardiacData, cardiacData, name, 'black', f1, f2, f3, f4, f5);
+
             for ii=1:length(channelToPlot)
                 fprintf('ii: %d, %d\n', ii, channelToPlot(ii));
 
@@ -178,8 +180,6 @@ for rabbit_ID = {'9rabbit_may_6_2014', '10rabbit_may_15_2014'}
                 qrs_plot(chData, cardiacData, name, CM(ii, :), 0, 0, 0, f4, f5);
 
             end
-
-            qrs_plot(0.15 * cardiacData, cardiacData, name, 'black', f1, f2, f3, f4, f5);
 
             ansdkasnd
 

### 2014-07-30 analysis/qrs/main.m
Minor changes to improve runtime

@@ -145,7 +145,7 @@ for rabbit_ID = {'9rabbit_may_6_2014', '10rabbit_may_15_2014'}
             dataColumnDig = fread(fid, Inf, 'single', 4*64);
             cleanDigitalIn = (dataColumnDig>0);
 
-            cardiacData = data{find(strcmp(data, 'Bottom Precordial')), 2};
+            cardiacData = data{strcmp(data, 'Bottom Precordial'), 2};
 
             cardiacData = filtfilt(nf60.sosMatrix, nf60.ScaleValues, cardiacData);
             cardiacData = filtfilt(nf120.sosMatrix, nf120.ScaleValues, cardiacData);
@@ -161,6 +161,8 @@ for rabbit_ID = {'9rabbit_may_6_2014', '10rabbit_may_15_2014'}
             f4 = figure('units', 'pixels', 'outerposition', [0 0 1366 768]);
             f5 = figure('units', 'pixels', 'outerposition', [0 0 1366 768]);
 
+            figure(f4);
+            plot([0 0], [-120 120], 'color', 'black', 'linewidth', 4);
             qrs_plot(0.125 * cardiacData, cardiacData, name, 'black', f1, f2, f3, f4, f5);
 
             for ii=1:length(channelToPlot)

### 2014-07-30 analysis/qrs/qrs_plot.m

@@ -4,7 +4,7 @@ function [] = qrs_plot(chData, cardiacData, name, color, f1, f2, f3, f4, f5)
     % cardiacData probably has to be unfiltered to work
     assert(all(size(chData) == size(cardiacData)));
     %tic
-    [pks,locs]=findpeaks(cardiacData,'minpeakdistance', round(0.18 * 9600));
+    [~,locs]=findpeaks(cardiacData,'minpeakdistance', round(0.18 * 9600));
     %toc
     %locs = locs(2:(end-1));
 
@@ -73,7 +73,7 @@ function [] = qrs_plot(chData, cardiacData, name, color, f1, f2, f3, f4, f5)
     assert(all(start < r_peak));
     assert(all(r_peak < finish));
 
-    dt = finish - start;
+    %dt = finish - start;
     max_before = max(r_peak - start);
     max_after = max(finish - r_peak);
     median_before = median(r_peak - start);
@@ -92,8 +92,8 @@ function [] = qrs_plot(chData, cardiacData, name, color, f1, f2, f3, f4, f5)
 
     %% Remove trials that have extreme values
     invalid = any(abs(padded) > 1e3, 2); % for some reason after applying hpf/lpf/nf, first and last area have extreme values
-    num_invalid = sum(invalid)
-    assert(sum(invalid) < 15);
+    num_invalid = sum(invalid);
+    assert(num_invalid < 15);
     padded = padded(~invalid, :);
 
     qrs = nanmean(padded, 1)';

### 2014-07-30 analysis/qrs/main.m
Remove duplicated run and allow code to continue

@@ -40,7 +40,7 @@ for rabbit_ID = {'9rabbit_may_6_2014', '10rabbit_may_15_2014'}
 
     switch rabbit_ID
         case '9rabbit_may_6_2014'
-            vep_indices = [10 2 10 11 12 13 3];
+            vep_indices = [2 10 11 12 13 3];
             ssvep_indices = [5 29 32 38 8];
             ssaep_indices = [8 32 35 41 11];
         case '10rabbit_may_15_2014'
@@ -182,8 +182,6 @@ for rabbit_ID = {'9rabbit_may_6_2014', '10rabbit_may_15_2014'}
                 qrs_plot(chData, cardiacData, name, CM(ii, :), 0, 0, 0, f4, f5);
 
             end
-
-            ansdkasnd
 
             %saveas(f1, ['matlab_data/' name '_' int2str(channel) '_r_peak.fig']);
             saveas(f1, ['matlab_data/' name '_r_peak.fig']);

### 2014-07-30 analysis/figures/figures.tex
Added baseline and dead control

@@
 % 0.126
+
+% 0.161
+% 0.126
+% 0.126
 \begin{document}
+%\begin{minipage}{6in}
+%\centering
+%\raisebox{-0.5\height}{\includegraphics[height=0.75in]{brain.pdf}}
+%\hspace*{.2in}
+%\raisebox{-0.5\height}{\includegraphics[height=0.3in]{brain.pdf}}
+%\end{minipage}
+
 \begin{figure}[H]
 \begin{center}
-\includegraphics{brain.pdf} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
+\hspace{0.2cm}
+\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
 \vspace{0.5cm}
-\begin{tabular}{cccc}
-& VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
+\begin{tabular}{ccc}
+& VEP On Response & VEP Off Response \\
 \rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
 \includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf} \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__off-crop.pdf} \\
 \rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
 \includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf} \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__off-crop.pdf} \\
 \rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
 \includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf} \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep__off-crop.pdf} \\
 \rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
 \includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep__off-crop.pdf}
+\end{tabular}
+\caption{Rabbit 10 experimental VEP.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{cc}
+VEP On Response & VEP Off Response \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf} &
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_off-crop.pdf}
+\end{tabular}
+\caption{Rabbit 10 live control VEP.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{cc}
+VEP On Response & VEP Off Response \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_.pdf} &
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep__off.pdf}
+\end{tabular}
+\caption{Rabbit 10 dead control VEP.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{cc}
+VEP On Response & VEP Off Response \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_09_55_41_vep_.pdf}
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_09_55_41_vep__off.pdf} &
+\end{tabular}
+\caption{Rabbit 10 baseline VEP.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
+\hspace{0.2cm}
+\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
+\vspace{0.5cm}
+\begin{tabular}{ccc}
+& SSVEP 40 Hz & SSAEP 86 Hz \\
+\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
+\includegraphics[scale=0.161]{../ssvep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf} &
+\includegraphics[scale=0.161]{../ssaep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf} \\
+\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
+\includegraphics[scale=0.161]{../ssvep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf} &
+\includegraphics[scale=0.161]{../ssaep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf} \\
+\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
+\includegraphics[scale=0.161]{../ssvep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf} &
+\includegraphics[scale=0.161]{../ssaep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf} \\
+\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
+\includegraphics[scale=0.161]{../ssvep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf} &
+\includegraphics[scale=0.161]{../ssaep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}
 \end{tabular}
@@
 \begin{tabular}{cccc}
-VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
-\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}
+SSVEP 40 Hz & SSAEP 86 Hz \\
+\includegraphics[scale=0.161]{../ssvep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf} &
+\includegraphics[scale=0.161]{../ssaep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}
 \end{tabular}
@@
 \begin{center}
-\includegraphics{brain.pdf} \\
+\begin{tabular}{cccc}
+SSVEP 40 Hz & SSAEP 86 Hz \\
+\includegraphics[scale=0.161]{../ssvep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40.pdf} &
+\includegraphics[scale=0.161]{../ssaep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86.pdf}
+\end{tabular}
+\caption{Rabbit 10 dead control.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{cccc}
+SSVEP 40 Hz & SSAEP 86 Hz \\
+\includegraphics[scale=0.161]{../ssvep/matlab_data/_Thu_15_05_2014_09_52_53_ssvep_40.pdf} &
+\includegraphics[scale=0.161]{../ssaep/matlab_data/_Thu_15_05_2014_10_04_16_ssaep_86.pdf}
+\end{tabular}
+\caption{Rabbit 10 baseline.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
+\hspace{0.2cm}
+\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
 \vspace{0.5cm}
-\begin{tabular}{cccc}
-& VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
+\begin{tabular}{ccc}
+& VEP On Response & VEP Off Response \\
 \rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
 \includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf} \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep__off-crop.pdf} \\
 \rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
 \includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep_-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_14_02_01_ssvep_40-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Tue_06_05_2014_14_11_09_ssaep_86-crop.pdf} \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep__off-crop.pdf} \\
 \rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
 \includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep_-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_14_41_46_ssvep_40-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Tue_06_05_2014_14_53_21_ssaep_86-crop.pdf} \\
-\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
-\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep_-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_15_11_25_ssvep_40-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Tue_06_05_2014_15_20_29_ssaep_86-crop.pdf} \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep__off-crop.pdf} \\
+%\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
+%\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep_-crop.pdf} &
+%\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep__off-crop.pdf} \\
 \rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
 \includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep_-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_15_48_24_ssvep_50-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Tue_06_05_2014_15_57_52_ssaep_86-crop.pdf}
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep__off-crop.pdf}
 \end{tabular}
@@
 \begin{center}
-\begin{tabular}{cccc}
-VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
+\begin{tabular}{cc}
+VEP On Response & VEP Off Response \\
 \includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep_-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86-crop.pdf}
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep__off-crop.pdf}
+\end{tabular}
+\caption{Rabbit 9 live control VEP.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{cc}
+VEP On Response & VEP Off Response \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_09_55_56_vep_3m.pdf}
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_09_55_56_vep_3m_off.pdf} &
+\end{tabular}
+\caption{Rabbit 9 baseline VEP.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
+\hspace{0.2cm}
+\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
+\vspace{0.5cm}
+\begin{tabular}{ccc}
+& SSVEP 40 Hz & SSAEP 86 Hz \\
+\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
+\includegraphics[scale=0.161]{../ssvep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf} &
+\includegraphics[scale=0.161]{../ssaep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf} \\
+\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
+\includegraphics[scale=0.161]{../ssvep/matlab_data/_Tue_06_05_2014_14_02_01_ssvep_40-crop.pdf} &
+\includegraphics[scale=0.161]{../ssaep/matlab_data/_Tue_06_05_2014_14_11_09_ssaep_86-crop.pdf} \\
+\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
+\includegraphics[scale=0.161]{../ssvep/matlab_data/_Tue_06_05_2014_14_41_46_ssvep_40-crop.pdf} &
+\includegraphics[scale=0.161]{../ssaep/matlab_data/_Tue_06_05_2014_14_53_21_ssaep_86-crop.pdf} \\
+%\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
+%\includegraphics[scale=0.161]{../ssvep/matlab_data/_Tue_06_05_2014_15_11_25_ssvep_40-crop.pdf} &
+%\includegraphics[scale=0.161]{../ssaep/matlab_data/_Tue_06_05_2014_15_20_29_ssaep_86-crop.pdf} \\
+\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
+\includegraphics[scale=0.161]{../ssvep/matlab_data/_Tue_06_05_2014_15_48_24_ssvep_50-crop.pdf} &
+\includegraphics[scale=0.161]{../ssaep/matlab_data/_Tue_06_05_2014_15_57_52_ssaep_86-crop.pdf}
+\end{tabular}
+\caption{Rabbit 9 experimental responses.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{cc}
+SSVEP 40 Hz & SSAEP 86 Hz \\
+\includegraphics[scale=0.161]{../ssvep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40-crop.pdf} &
+\includegraphics[scale=0.161]{../ssaep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86-crop.pdf}
 \end{tabular}
@@
 
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{cc}
+SSVEP 40 Hz & SSAEP 86 Hz \\
+\includegraphics[scale=0.161]{../ssvep/matlab_data/_Tue_06_05_2014_09_52_56_ssvep_40-crop.pdf} &
+\includegraphics[scale=0.161]{../ssaep/matlab_data/_Tue_06_05_2014_10_08_48_ssaep_86.pdf}
+\end{tabular}
+\caption{Rabbit 9 baseline.}
+\end{center}
+\end{figure}
+
 \end{document}

### 2014-08-04 analysis/figures/paper_figures.tex
Original paper figures.

\documentclass[]{article}

\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}

\pagestyle{plain}

% scale:
% 0.161
% 0.126
% 0.126

% 0.161
% 0.126
% 0.126
\begin{document}
%\begin{minipage}{6in}
%\centering
%\raisebox{-0.5\height}{\includegraphics[height=0.75in]{brain.pdf}}
%\hspace*{.2in}
%\raisebox{-0.5\height}{\includegraphics[height=0.3in]{brain.pdf}}
%\end{minipage}

\begin{figure}[H]
\begin{center}
\raisebox{-0.5\height}{\includegraphics[scale=0.2]{brain.pdf}}
\hspace{0.2cm}
\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
\vspace{0.5cm}
\begin{tabular}{ccc}
& VEP On Response & VEP Off Response \\
\raisebox{-0.5\height}{\rotatebox{90}{Basilar Tip}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__off.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{Mid-Basilar}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__off.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{Vertebro-basilar}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep__off.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{Basilar Tip}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep__off.pdf}}
\vspace{0.2cm} \\
\hline
% TODO add space
\raisebox{-0.5\height}{\rotatebox{90}{Live Control}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_off.pdf}}
\end{tabular}
\caption{Rabbit 10 VEP.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{ccc}
& SSVEP 40 Hz & SSAEP 86 Hz \\
\raisebox{-0.5\height}{\rotatebox{90}{Basilar Tip}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{Mid-Basilar}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{Vertebro-basilar}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{Basilar Tip}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86.pdf}}
\vspace{0.2cm} \\
\hline
% TODO add space
\raisebox{-0.5\height}{\rotatebox{90}{Live Control}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86.pdf}}
\end{tabular}
\caption{Rabbit 10 experimental responses.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
& VEP & SSVEP 40 Hz & SSAEP 86 Hz \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_11_57_42_vep__qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40_qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86_qrs-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40_qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86_qrs-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_15_54_54_vep__qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40_qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86_qrs-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_47_47_vep__qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40_qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86_qrs-crop.pdf}
\end{tabular}
\caption{Rabbit 10 experimental responses. Cardiac activity is multiplied by 0.125.}
\end{center}
\end{figure}

%\begin{figure}[H]
%\begin{center}
%\begin{tabular}{cccc}
%& VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
%\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_17_10_vep__qrs-crop.pdf} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40_qrs-crop.pdf} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86_qrs-crop.pdf} \\
%\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_04_18_vep__qrs-crop.pdf} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_02_01_ssvep_40_qrs-crop.pdf} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_11_09_ssaep_86_qrs-crop.pdf} \\
%\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_44_57_vep__qrs-crop.pdf} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_41_46_ssvep_40_qrs-crop.pdf} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_53_21_ssaep_86_qrs-crop.pdf} \\
%%\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
%%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_13_50_vep__qrs-crop.pdf} &
%%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_11_25_ssvep_40_qrs-crop.pdf} &
%%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_20_29_ssaep_86_qrs-crop.pdf} \\
%\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_50_43_vep__qrs-crop.pdf} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_48_24_ssvep_50_qrs-crop.pdf} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_57_52_ssaep_86_qrs-crop.pdf}
%\end{tabular}
%\caption{Rabbit 9 experimental responses. Cardiac activity is multiplied by 0.125.}
%\end{center}
%\end{figure}

\end{document}

### 2014-08-04 analysis/figures/paper_figures.tex
Placeholder captions

@@
 
-% scale:
-% 0.161
-% 0.126
-% 0.126
-
-% 0.161
-% 0.126
-% 0.126
 \begin{document}
-%\begin{minipage}{6in}
-%\centering
-%\raisebox{-0.5\height}{\includegraphics[height=0.75in]{brain.pdf}}
-%\hspace*{.2in}
-%\raisebox{-0.5\height}{\includegraphics[height=0.3in]{brain.pdf}}
-%\end{minipage}
 
@@
 \begin{center}
-\raisebox{-0.5\height}{\includegraphics[scale=0.2]{brain.pdf}}
-\hspace{0.2cm}
-\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
-\vspace{0.5cm}
-\begin{tabular}{ccc}
-& VEP On Response & VEP Off Response \\
-\raisebox{-0.5\height}{\rotatebox{90}{Basilar Tip}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__off.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{Mid-Basilar}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__off.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{Vertebro-basilar}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep__off.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{Basilar Tip}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep__off.pdf}}
-\vspace{0.2cm} \\
-\hline
-% TODO add space
-\raisebox{-0.5\height}{\rotatebox{90}{Live Control}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_off.pdf}}
-\end{tabular}
-\caption{Rabbit 10 VEP.}
+\caption{Surgical approach, anatomy imaging.}
 \end{center}
@@
 \begin{center}
-\begin{tabular}{ccc}
-& SSVEP 40 Hz & SSAEP 86 Hz \\
-\raisebox{-0.5\height}{\rotatebox{90}{Basilar Tip}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{Mid-Basilar}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{Vertebro-basilar}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{Basilar Tip}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86.pdf}}
-\vspace{0.2cm} \\
-\hline
-% TODO add space
-\raisebox{-0.5\height}{\rotatebox{90}{Live Control}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86.pdf}}
-\end{tabular}
-\caption{Rabbit 10 experimental responses.}
+\caption{At Basilar Tip.}
 \end{center}
@@
 \begin{center}
-\begin{tabular}{cccc}
-& VEP & SSVEP 40 Hz & SSAEP 86 Hz \\
-\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
-\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_11_57_42_vep__qrs-crop.pdf} &
-\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40_qrs-crop.pdf} &
-\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86_qrs-crop.pdf} \\
-\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
-\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__qrs-crop.pdf} &
-\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40_qrs-crop.pdf} &
-\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86_qrs-crop.pdf} \\
-\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
-\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_15_54_54_vep__qrs-crop.pdf} &
-\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40_qrs-crop.pdf} &
-\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86_qrs-crop.pdf} \\
-\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
-\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_47_47_vep__qrs-crop.pdf} &
-\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40_qrs-crop.pdf} &
-\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86_qrs-crop.pdf}
-\end{tabular}
-\caption{Rabbit 10 experimental responses. Cardiac activity is multiplied by 0.125.}
+\caption{Rabbit 10 position dependence.}
 \end{center}
@@
 
-%\begin{figure}[H]
-%\begin{center}
-%\begin{tabular}{cccc}
-%& VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
-%\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
-%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_17_10_vep__qrs-crop.pdf} &
-%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40_qrs-crop.pdf} &
-%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86_qrs-crop.pdf} \\
-%\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
-%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_04_18_vep__qrs-crop.pdf} &
-%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_02_01_ssvep_40_qrs-crop.pdf} &
-%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_11_09_ssaep_86_qrs-crop.pdf} \\
-%\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
-%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_44_57_vep__qrs-crop.pdf} &
-%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_41_46_ssvep_40_qrs-crop.pdf} &
-%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_53_21_ssaep_86_qrs-crop.pdf} \\
-%%\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
-%%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_13_50_vep__qrs-crop.pdf} &
-%%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_11_25_ssvep_40_qrs-crop.pdf} &
-%%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_20_29_ssaep_86_qrs-crop.pdf} \\
-%\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
-%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_50_43_vep__qrs-crop.pdf} &
-%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_48_24_ssvep_50_qrs-crop.pdf} &
-%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_57_52_ssaep_86_qrs-crop.pdf}
-%\end{tabular}
-%\caption{Rabbit 9 experimental responses. Cardiac activity is multiplied by 0.125.}
-%\end{center}
-%\end{figure}
+\begin{figure}[H]
+\begin{center}
+\caption{Impedence characterization.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\caption{Cardiac contamination and cleaning.}
+\end{center}
+\end{figure}
 

### 2014-08-05 analysis/figures/paper_figures.tex
Partially completed paper figures.

@@
 \usepackage[margin=1.0in]{geometry}
+%\usepackage[paperwidth=5.5in, paperheight=8.5in]{geometry}
 \usepackage{graphicx}
@@
 \begin{center}
+\includegraphics[scale=1.0]{surgical_methods.pdf}
 \caption{Surgical approach, anatomy imaging.}
@@
 \begin{center}
+\begin{tabular}{cccc}
+& VEP & SSAEP 86 Hz & SSVEP 40 Hz \\
+\raisebox{-0.5\height}{\rotatebox{90}{Rabbit 8}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_24_04_2014_12_55_56_vep_-crop.pdf}} &
+&
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_24_04_2014_12_59_49_ssvep_.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{Rabbit 9}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{Rabbit 10}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}}
+\end{tabular}
 \caption{At Basilar Tip.}
@@
 
+\setcounter{figure}{1}
+
 \begin{figure}[H]
 \begin{center}
+\begin{tabular}{ccc}
+& Rabbit 10 & Rabbit 9 \\
+\raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}}
+\end{tabular}
+\caption{At Basilar Tip.}
+\end{center}
+\end{figure}
+
+\setlength{\tabcolsep}{2pt}
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{ccccc|cc}
+& Basilar Tip & Mid-Basilar & VB Junction & Basilar Tip & Live Control & Dead Control \\
+\raisebox{-0.5\height}{\rotatebox{90}{Resting State}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_15_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_24_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_33_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_36_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_12_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_40_40-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}}
+\end{tabular}
+\caption{Rabbit 10 position dependence.}
+\end{center}
+\end{figure}
+\setlength{\tabcolsep}{6pt}
+
+\setcounter{figure}{2}
+\setlength{\tabcolsep}{2pt}
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{ccccc}
+& Basilar Tip & Mid-Basilar & VB Junction & Basilar Tip \\ %& Live Control & Dead Control \\
+\raisebox{-0.5\height}{\rotatebox{90}{Resting State}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_15_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_24_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_33_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_36_40-crop.pdf}} \\
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_12_40-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_40_40-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf}} \\
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}} \\
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}}
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}}
+\end{tabular}
+\caption{Rabbit 10 position dependence.}
+\end{center}
+\end{figure}
+\setlength{\tabcolsep}{6pt}
+
+\setcounter{figure}{2}
+
+\begin{figure}[H] % Transpose of previous
+\begin{center}
+\begin{tabular}{ccccc}
+& Resting State & VEP & SSVEP 40 Hz & SSAEP 86 Hz \\
+\raisebox{-0.5\height}{\rotatebox{90}{Basilar Tips}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_15_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{Mid-Basilar}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_24_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{VB Junction}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_33_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{Basilar Tip}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_36_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{Live Control}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_12_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{Dead Control}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_40_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}}
+\end{tabular}
 \caption{Rabbit 10 position dependence.}
@@
 \begin{center}
+\begin{tabular}{cc}
+\includegraphics[scale=0.5]{impedance.pdf}
+\end{tabular}
 \caption{Impedence characterization.}
@@
 \begin{center}
+\begin{tabular}{ccc}
+\raisebox{-0.5\height}{contaminated raw trace + cardiac} &
+\raisebox{-0.5\height}{\includegraphics[scale=1.0]{TODO.pdf}} \\
+\raisebox{-0.5\height}{VEP aligned contaminated EKG} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__all_qrs.png}} \\
+\raisebox{-0.5\height}{cardiac aligned avg vep + EKG} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__qrs-crop.pdf}} \\
+\raisebox{-0.5\height}{vep aligned cleaned} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__all.png}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_.pdf}} \\
+\raisebox{-0.5\height}{raw cleaned} &
+\raisebox{-0.5\height}{\includegraphics[scale=1.0]{TODO.pdf}}
+\end{tabular}
 \caption{Cardiac contamination and cleaning.}

### 2014-08-05 analysis/figures/paper_figures.tex
Fix labels for some figures and rearragement

@@
 \includegraphics[scale=1.0]{surgical_methods.pdf}
-\caption{Surgical approach, anatomy imaging.}
+\caption{Surgical approach, anatomy imaging.} % Figure 1
 \end{center}
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{Rabbit 10}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}}
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}}
 \end{tabular}
-\caption{At Basilar Tip.}
+\caption{At Basilar Tip.} % Figure 2
 \end{center}
@@
 \begin{center}
-\begin{tabular}{ccc}
-& Rabbit 10 & Rabbit 9 \\
+\begin{tabular}{cccc}
+& Rabbit 10 & Rabbit 9 & Rabbit 8 \\
 \raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_24_04_2014_12_55_56_vep_-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}}
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_24_04_2014_12_59_49_ssvep_.pdf}}
 \end{tabular}
-\caption{At Basilar Tip.}
+\caption{At Basilar Tip.} % Figure 2
 \end{center}
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}}
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}}
 \end{tabular}
-\caption{Rabbit 10 position dependence.}
+\caption{Rabbit 10 position dependence.} % Figure 3
 \end{center}
@@
 %\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} \\
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}}
 %\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}}
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}}
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}}
 \end{tabular}
-\caption{Rabbit 10 position dependence.}
+\caption{Rabbit 10 position dependence.} % Figure 3
 \end{center}
@@
 \begin{tabular}{ccccc}
-& Resting State & VEP & SSVEP 40 Hz & SSAEP 86 Hz \\
+& Resting State & VEP & SSAEP 86 Hz & SSVEP 40 Hz \\
 \raisebox{-0.5\height}{\rotatebox{90}{Basilar Tips}} &
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{Mid-Basilar}} &
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{VB Junction}} &
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{Basilar Tip}} &
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{Live Control}} &
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{Dead Control}} &
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}}
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}}
 \end{tabular}
-\caption{Rabbit 10 position dependence.}
+\caption{Rabbit 10 position dependence.} % Figure 3
 \end{center}
@@
 \end{tabular}
-\caption{Impedence characterization.}
+\caption{Impedence characterization.} % Figure 4
 \end{center}
@@
 \end{tabular}
-\caption{Cardiac contamination and cleaning.}
+\caption{Cardiac contamination and cleaning.} % Figure 5
 \end{center}

### 2014-08-05 analysis/figures/paper_figures.tex
Using mid-basilar for rabbit 10 figure 2.
Comment out alternative versions of figures

@@
 
-\begin{figure}[H]
-\begin{center}
-\begin{tabular}{cccc}
-& VEP & SSAEP 86 Hz & SSVEP 40 Hz \\
-\raisebox{-0.5\height}{\rotatebox{90}{Rabbit 8}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_24_04_2014_12_55_56_vep_-crop.pdf}} &
-&
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_24_04_2014_12_59_49_ssvep_.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{Rabbit 9}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{Rabbit 10}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}}
-\end{tabular}
-\caption{At Basilar Tip.} % Figure 2
-\end{center}
-\end{figure}
+%\begin{figure}[H]
+%\begin{center}
+%\begin{tabular}{cccc}
+%& VEP & SSAEP 86 Hz & SSVEP 40 Hz \\
+%\raisebox{-0.5\height}{\rotatebox{90}{Rabbit 8}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_24_04_2014_12_55_56_vep_-crop.pdf}} &
+%&
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_24_04_2014_12_59_49_ssvep_.pdf}} \\
+%\raisebox{-0.5\height}{\rotatebox{90}{Rabbit 9}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} \\
+%\raisebox{-0.5\height}{\rotatebox{90}{Rabbit 10}} &
+%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
+%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
+%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}}
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} \\
+%\end{tabular}
+%\caption{At Basilar Tip for rabbit 8 and 9; at mid-basilar for rabbit 10.} % Figure 2
+%\end{center}
+%\end{figure}
 
@@
 \raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} &
@@
 \raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} &
@@
 \end{tabular}
-\caption{At Basilar Tip.} % Figure 2
+\caption{At Basilar Tip for rabbit 8 and 9; at mid-basilar for rabbit 10.} % Figure 2
 \end{center}
@@
 
-\setcounter{figure}{2}
-\setlength{\tabcolsep}{2pt}
-\begin{figure}[H]
-\begin{center}
-\begin{tabular}{ccccc}
-& Basilar Tip & Mid-Basilar & VB Junction & Basilar Tip \\ %& Live Control & Dead Control \\
-\raisebox{-0.5\height}{\rotatebox{90}{Resting State}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_15_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_24_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_33_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_36_40-crop.pdf}} \\
+%\setcounter{figure}{2}
+%\setlength{\tabcolsep}{2pt}
+%\begin{figure}[H]
+%\begin{center}
+%\begin{tabular}{ccccc}
+%& Basilar Tip & Mid-Basilar & VB Junction & Basilar Tip \\ %& Live Control & Dead Control \\
+%\raisebox{-0.5\height}{\rotatebox{90}{Resting State}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_15_40-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_24_40-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_33_40-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_36_40-crop.pdf}} \\
+%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_12_40-crop.pdf}} &
+%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_40_40-crop.pdf}} \\
+%\raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf}} \\
+%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
+%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} \\
+%\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} \\
+%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
+%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}} \\
+%\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}}
+%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
+%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}}
+%\end{tabular}
+%\caption{Rabbit 10 position dependence.} % Figure 3
+%\end{center}
+%\end{figure}
+%\setlength{\tabcolsep}{6pt}
+
+%\setcounter{figure}{2}
+%\begin{figure}[H] % Transpose of previous
+%\begin{center}
+%\begin{tabular}{ccccc}
+%& Resting State & VEP & SSAEP 86 Hz & SSVEP 40 Hz \\
+%\raisebox{-0.5\height}{\rotatebox{90}{Basilar Tips}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_15_40-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} \\
+%\raisebox{-0.5\height}{\rotatebox{90}{Mid-Basilar}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_24_40-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} \\
+%\raisebox{-0.5\height}{\rotatebox{90}{VB Junction}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_33_40-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf}} \\
+%\raisebox{-0.5\height}{\rotatebox{90}{Basilar Tip}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_36_40-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}} \\
+%\raisebox{-0.5\height}{\rotatebox{90}{Live Control}} &
 %\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_12_40-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_40_40-crop.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf}} \\
 %\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} \\
 %\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}}
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} \\
+%\raisebox{-0.5\height}{\rotatebox{90}{Dead Control}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_40_40-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}} &
 %\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}}
-\end{tabular}
-\caption{Rabbit 10 position dependence.} % Figure 3
-\end{center}
-\end{figure}
-\setlength{\tabcolsep}{6pt}
-
-\setcounter{figure}{2}
-
-\begin{figure}[H] % Transpose of previous
-\begin{center}
-\begin{tabular}{ccccc}
-& Resting State & VEP & SSAEP 86 Hz & SSVEP 40 Hz \\
-\raisebox{-0.5\height}{\rotatebox{90}{Basilar Tips}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_15_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{Mid-Basilar}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_24_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{VB Junction}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_33_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{Basilar Tip}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_36_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{Live Control}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_12_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{Dead Control}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_40_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}}
-\end{tabular}
-\caption{Rabbit 10 position dependence.} % Figure 3
-\end{center}
-\end{figure}
+%\end{tabular}
+%\caption{Rabbit 10 position dependence.} % Figure 3
+%\end{center}
+%\end{figure}
 

### 2014-08-05 analysis/figures/paper_figures.tex
Added control version of figure 2.

@@
 \setcounter{figure}{1}
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{cccc}
+& Rabbit 10 & Rabbit 9 & Rabbit 8 \\
+\raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep_-crop.pdf}} \\
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_24_04_2014_12_55_56_vep_-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40-crop.pdf}}
+%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_24_04_2014_12_59_49_ssvep_.pdf}}
+\end{tabular}
+\caption{Live control trials. At Basilar Tip. NOTE: This is a different location for rabbit 10. NOTE: Does not exist for rabbit 8.} % Figure 2
+\end{center}
+\end{figure}
 
+\setcounter{figure}{1}
 \begin{figure}[H]

### 2014-08-06 analysis/figures/paper_figures.tex
Fixed ordering of figures
Forgot to use cropped version of figure
Rabbit 8 figures

--- 2014-08-05 analysis/figures/paper_figures.tex
@@
 \setcounter{figure}{1}
-
 \begin{figure}[H]
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/8rabbit_apr_24_2014_ssaep_ssvep_5_5-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_24_04_2014_12_59_49_ssvep_.pdf}}
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_24_04_2014_12_59_49_ssvep_-crop.pdf}}\\
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/8rabbit_apr_24_2014_ssaep_ssvep_5_5-crop.pdf}} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/8rabbit_apr_24_2014_ssaep_ssvep_26_36-crop.pdf}} \\
 \end{tabular}
-\caption{At Basilar Tip for rabbit 8 and 9; at mid-basilar for rabbit 10.} % Figure 2
+\caption{At Basilar Tip for rabbit 8 and 9; at mid-basilar for rabbit 10. Rabbit 8 ssaep is 42 Hz.} % Figure 2
+\end{center}
+\end{figure}
+
+\setcounter{figure}{1}
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{cccc}
+& Rabbit 10 & Rabbit 9 & Rabbit 8 \\
+\raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_24_04_2014_16_56_55_vep_.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/8rabbit_apr_24_2014_ssaep_ssvep_26_36-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_24_04_2014_16_59_49_ssvep_40-crop.pdf}}
+\end{tabular}
+\caption{Live control trials.
+At Basilar Tip.
+NOTE: This is a different location for rabbit 10.
+NOTE: Does not exist for rabbit 8.
+Rabbit 8 uses Dead control, which is Ag/AgCl.
+Rabbit 8 SSAEP is 42 Hz.} % Figure 2
 \end{center}
@@
 & Basilar Tip & Mid-Basilar & VB Junction & Basilar Tip & Live Control & Dead Control \\
-\raisebox{-0.5\height}{\rotatebox{90}{Resting State}} &
+\raisebox{-0.5\height}{\rotatebox{90}{Resting State (SSAEP)}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_15_40-crop.pdf}} &
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_40_40-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{Resting State (SSVEP)}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_11_38-crop.pdf}} & % basilar tip
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_23_38-crop.pdf}} & % mid-basilar
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_32_38-crop.pdf}} & % vb junction
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_35_38-crop.pdf}} & % basilar tip
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_14_38-crop.pdf}} & % live control
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_38_38-crop.pdf}} \\ % dead control
+\raisebox{-0.5\height}{\rotatebox{90}{Resting PSD (SSAEP)}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_15_40_not_subtracted-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_24_40_not_subtracted-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_33_40_not_subtracted-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_36_40_not_subtracted-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_12_40_not_subtracted-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_40_40_not_subtracted-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{Resting PSD (SSVEP)}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_11_38_not_subtracted-crop.pdf}} & % basilar tip
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_23_38_not_subtracted-crop.pdf}} & % mid-basilar
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_32_38_not_subtracted-crop.pdf}} & % vb junction
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_35_38_not_subtracted-crop.pdf}} & % basilar tip
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_14_38_not_subtracted-crop.pdf}} & % live control
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_38_38_not_subtracted-crop.pdf}} \\ % dead control
 \raisebox{-0.5\height}{\rotatebox{90}{VEP}} &

### 2014-08-06 analysis/figures/paper_figures.tex
Remove rabbit 8

@@
 \begin{center}
-\begin{tabular}{cccc}
-& Rabbit 10 & Rabbit 9 & Rabbit 8 \\
+\begin{tabular}{ccc}
+& Rabbit 10 & Rabbit 9 \\
 \raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_24_04_2014_12_55_56_vep_-crop.pdf}} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/8rabbit_apr_24_2014_ssaep_ssvep_5_5-crop.pdf}} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_24_04_2014_12_59_49_ssvep_-crop.pdf}}\\
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/8rabbit_apr_24_2014_ssaep_ssvep_5_5-crop.pdf}} \\
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/8rabbit_apr_24_2014_ssaep_ssvep_26_36-crop.pdf}} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}}
 \end{tabular}
-\caption{At Basilar Tip for rabbit 8 and 9; at mid-basilar for rabbit 10. Rabbit 8 ssaep is 42 Hz.} % Figure 2
+\caption{At Basilar Tip for rabbit 9; at mid-basilar for rabbit 10.} % Figure 2
 \end{center}
@@
 \begin{center}
-\begin{tabular}{cccc}
-& Rabbit 10 & Rabbit 9 & Rabbit 8 \\
+\begin{tabular}{ccc}
+& Rabbit 10 & Rabbit 9 \\
 \raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_24_04_2014_16_56_55_vep_.pdf}} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep_-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/8rabbit_apr_24_2014_ssaep_ssvep_26_36-crop.pdf}} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_24_04_2014_16_59_49_ssvep_40-crop.pdf}}
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40-crop.pdf}}
 \end{tabular}
-\caption{Live control trials.
-At Basilar Tip.
-NOTE: This is a different location for rabbit 10.
-NOTE: Does not exist for rabbit 8.
-Rabbit 8 uses Dead control, which is Ag/AgCl.
-Rabbit 8 SSAEP is 42 Hz.} % Figure 2
+\caption{Live control trials. At Basilar Tip for rabbit 9, at mid-basilar for rabbit 10.} % Figure 2
 \end{center}

### 2014-08-06 analysis/figures/paper_figures.tex
Merged figure 2 experiment and live control (previously supplementary) into one figure

@@
 \begin{center}
-\begin{tabular}{ccc}
-& Rabbit 10 & Rabbit 9 \\
+\begin{tabular}{ccc|cc}
+& Rabbit 10 & Rabbit 9 & Rabbit 10 Control & Rabbit 9 Control \\
 \raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep_-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}}
-\end{tabular}
-\caption{At Basilar Tip for rabbit 9; at mid-basilar for rabbit 10.} % Figure 2
-\end{center}
-\end{figure}
-
-\setcounter{figure}{1}
-\begin{figure}[H]
-\begin{center}
-\begin{tabular}{ccc}
-& Rabbit 10 & Rabbit 9 \\
-\raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep_-crop.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86-crop.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
@@
 \end{tabular}
-\caption{Live control trials. At Basilar Tip for rabbit 9, at mid-basilar for rabbit 10.} % Figure 2
+\caption{At Basilar Tip for rabbit 9; at mid-basilar for rabbit 10.} % Figure 2
 \end{center}

### 2014-08-06 analysis/figures/paper_figures.tex
Resting state for rabbit 9

@@
 & Basilar Tip & Mid-Basilar & VB Junction & Basilar Tip & Live Control & Dead Control \\
-\raisebox{-0.5\height}{\rotatebox{90}{Resting State (SSAEP)}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_15_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_24_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_33_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_36_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_12_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_40_40-crop.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{Resting State (SSVEP)}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_11_38-crop.pdf}} & % basilar tip
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_23_38-crop.pdf}} & % mid-basilar
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_32_38-crop.pdf}} & % vb junction
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_35_38-crop.pdf}} & % basilar tip
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_14_38-crop.pdf}} & % live control
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_38_38-crop.pdf}} \\ % dead control
 \raisebox{-0.5\height}{\rotatebox{90}{Resting PSD (SSAEP)}} &
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_38_38_not_subtracted-crop.pdf}} \\ % dead control
+%\raisebox{-0.5\height}{\rotatebox{90}{Resting PSD 9 (SSAEP)}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssaep_8_8_not_subtracted-crop.pdf}} & % basilar tip
+%\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssaep_32_8_not_subtracted-crop.pdf}} & % mid-basilar
+%\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssaep_35_8_not_subtracted-crop.pdf}} & % vb junction
+%\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssaep_41_8_not_subtracted-crop.pdf}} & % basilar tip
+%\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssaep_11_8_not_subtracted-crop.pdf}} & % live control
+%\\
+\raisebox{-0.5\height}{\rotatebox{90}{Resting PSD 9 (SSVEP)}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssvep_5_5_not_subtracted-crop.pdf}} & % basilar tip
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssvep_29_5_not_subtracted-crop.pdf}} & % mid-basilar
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssvep_32_5_not_subtracted-crop.pdf}} & % vb junction
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssvep_38_5_not_subtracted-crop.pdf}} & % basilar tip
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssvep_8_5_not_subtracted-crop.pdf}} & % live control
+\\
 \raisebox{-0.5\height}{\rotatebox{90}{VEP}} &

### 2014-08-06 analysis/vep/plot_all_vep.m
plot_all_vep is now a function

@@ -17,18 +17,27 @@
 %	
 %	The analysis code assumes a fixed sampling rate of 9600 Hz and digital input channel # of 65 (both designated in arduino_vep.m)
 
+function plot_all_vep(rabbit_ID, publication_quality, trials_list)
+
+addpath('../config');
+addpath('../utilities');
 
 %///////////////////////////////////////////////
 % START BLOCK: Hardcoded variables
 %///////////////////////////////////////////////
+%rabbit_ID = '1rabbit_dec_10_2012';
+%rabbit_ID = '2rabbit_jan_23_2013';
+%rabbit_ID = '4rabbit_feb_5_2014';
+%rabbit_ID = '5rabbit_mar_4_2014';
 %rabbit_ID = '6rabbit_apr_11_2014';                                         %'7rabbit_apr_15_2014' corresponds to the experiment performed 4/15/14
 %rabbit_ID = '7rabbit_apr_15_2014';                                         %'7rabbit_apr_15_2014' corresponds to the experiment performed 4/15/14
 %rabbit_ID = '8rabbit_apr_24_2014';
 %rabbit_ID = '9rabbit_may_6_2014';
-rabbit_ID = '10rabbit_may_15_2014';
+%rabbit_ID = '10rabbit_may_15_2014';
 
-publication_quality = 3;                                                   % generate the high quality figures with confidence intervals. this is much slower than having it set to zero
+%publication_quality = 3;                                                   % generate the high quality figures with confidence intervals. this is much slower than having it set to zero
                                                                            % 0:, 1:with confidence intervals , 2:without confidence intervals, 3: use dashed lines instead of transparent ares for confidence areas
+% TODO: for some reason, publication quality 1 (shaded confidence intervals) does not save properly to pdf or eps
 
 decimate_factor = 10;                                                      % decimate the data to speed up plotting (decimate_factor = 1 is no decimation; 10 is reasonable)
                                                                            %(this Matlab function implements proper downsampling using anti-aliasing, with decimate.m).
@@ -141,9 +150,33 @@ for i = 1:length(S)
   assert(strcmp(S_second, header_second));
 end
 
-for i=1:length(S),				%for each data file in the directory
+if (nargin < 2)
+    publication_quality = 2;
+end
+
+if (nargin < 3)
+    trials_list = 1:numel(S);
+end
+
+
+% rabbit10
[…]

### 2014-08-06 analysis/utilities/clean_name.m
Function to clean formatting of file names

@@ -1,0 +1,10 @@
+function [ name ] = clean_name(name)
+
+name(name == '.') = '_';
+while any(name == '%')
+    index = find(name == '%', 1);
+    name = [name(1:(index-1)) '_' name((index+3):end)];
+end
+
+end
+

### 2014-08-06 analysis/vep/plot_all_vep.m
Use functions instead of copy pasted code in plot_all_vep

@@ -46,7 +46,7 @@ decimate_factor = 10;                                                      % dec
 maxNumberOfChannels = 10;                                                  %# of consecutive analog input channels, starting with channel 1, to extract from the project easter binary files
                                                                            %(which contain 64 analog channels and the digital in channel (channel 65)
 
-digitalinCh = 65;                                                          %designate the digital input channel, which is used to record
+digitalInCh = 65;                                                          %designate the digital input channel, which is used to record
                                                                            %the LED state to align EEG data with onset or offset to generate VEP graphs 
 
 original_sampling_rate_in_Hz = 9600;                                       % data is acquired with the g.Tech g.HiAmp at 9600 Hz. this is fixed for convenience. at higher rates, the 
@@ -66,89 +66,20 @@ pathname_comments = ['../../../../data/easter/' rabbit_ID '/neuro/neuro_experime
 
 pathname_matdata = ['../../../../data/easter/' rabbit_ID '/neuro/matlab_data/vep/'];
 
-%Channel labels during VEP for all rabbits (5,6,7, etc.)
-switch rabbit_ID
-    case {'7rabbit_apr_15_2014', '8rabbit_apr_24_2014', '9rabbit_may_6_2014', '10rabbit_may_15_2014'}
-        channelNames_VEP = {'Disconnected','Endo','Mid head','Disconnected','Right Eye','Right Leg','Back Head','Left Eye','Bottom Precordial','Top Precordial'};
-        plot_only_neuro_and_endo_channels = 0;                             % choose to plot only neuro and endo channels, excluding disconnected or precordial channels
-        gtechGND = 'Nose';
-        earth = 'Left Leg';
-    case '6rabbit_apr_11_2014'
-        channelNames_VEP = {'Disconnected','Endo','Mid head','Disconnected','Right Eye','Right Leg','Back Head','Left Eye','Bottom Precordial','Top Precordial'};
-    case '5rabbit_apr_15_2014'
-%        channelNames_VEP = 
-end
+[ channelNames, gtechGND, earth ] = rabbit_information(rabbit_ID);
 %///////////////////////////////////////////////
 % END BLOCK: Hardcoded variables
 %///////////////////////////////////////////////
 
 
 
[…]

### 2014-08-06 analysis/vep/plot_all_vep.m
Don't print output.

@@ -109,7 +109,7 @@ for i = trials_list
     filename = S{i};
     fprintf('filename: %s,\t%d / %d\n', filename, i, length(S));
 
-    [ data, cleanDigitalIn ] = load_data([pathname filename], maxNumberOfChannels, digitalInCh, channelNames)
+    [ data, cleanDigitalIn ] = load_data([pathname filename], maxNumberOfChannels, digitalInCh, channelNames);
 
     if publication_quality > 0
         run('publish_vep_v2.m');

### 2014-08-06 analysis/vep/plot_all_vep.m
Stop printing output

@@ -73,7 +73,7 @@ pathname_matdata = ['../../../../data/easter/' rabbit_ID '/neuro/matlab_data/vep
 
 
 
-[ S, allData ] = get_information(pathname, pathname_comments, 'VEP')
+[ S, allData ] = get_information(pathname, pathname_comments, 'VEP');
 
 %////////////////////////////////////////////////////////////////////////////////////////
 % START BLOCK: Extract Data from Project Easter Binary Files to Prep for

### 2014-08-06 analysis/figures/paper_figures.tex
Remove commented out text and resting state

@@
 
-%\begin{figure}[H]
-%\begin{center}
-%\begin{tabular}{cccc}
-%& VEP & SSAEP 86 Hz & SSVEP 40 Hz \\
-%\raisebox{-0.5\height}{\rotatebox{90}{Rabbit 8}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_24_04_2014_12_55_56_vep_-crop.pdf}} &
-%&
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_24_04_2014_12_59_49_ssvep_.pdf}} \\
-%\raisebox{-0.5\height}{\rotatebox{90}{Rabbit 9}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} \\
-%\raisebox{-0.5\height}{\rotatebox{90}{Rabbit 10}} &
-%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
-%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
-%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}}
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} \\
-%\end{tabular}
-%\caption{At Basilar Tip for rabbit 8 and 9; at mid-basilar for rabbit 10.} % Figure 2
-%\end{center}
-%\end{figure}
-
 \setcounter{figure}{1}
@@
 \raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
@@
 \raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
@@
 \raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
@@
 & Basilar Tip & Mid-Basilar & VB Junction & Basilar Tip & Live Control & Dead Control \\
-\raisebox{-0.5\height}{\rotatebox{90}{Resting PSD (SSAEP)}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_15_40_not_subtracted-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_24_40_not_subtracted-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_33_40_not_subtracted-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_36_40_not_subtracted-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_12_40_not_subtracted-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_40_40_not_subtracted-crop.pdf}} \\
-\raisebox{-0.5\height}{\rotatebox{90}{Resting PSD (SSVEP)}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_11_38_not_subtracted-crop.pdf}} & % basilar tip
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_23_38_not_subtracted-crop.pdf}} & % mid-basilar
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_32_38_not_subtracted-crop.pdf}} & % vb junction
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_35_38_not_subtracted-crop.pdf}} & % basilar tip
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_14_38_not_subtracted-crop.pdf}} & % live control
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_38_38_not_subtracted-crop.pdf}} \\ % dead control
-%\raisebox{-0.5\height}{\rotatebox{90}{Resting PSD 9 (SSAEP)}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssaep_8_8_not_subtracted-crop.pdf}} & % basilar tip
-%\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssaep_32_8_not_subtracted-crop.pdf}} & % mid-basilar
-%\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssaep_35_8_not_subtracted-crop.pdf}} & % vb junction
-%\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssaep_41_8_not_subtracted-crop.pdf}} & % basilar tip
-%\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssaep_11_8_not_subtracted-crop.pdf}} & % live control
-%\\
-\raisebox{-0.5\height}{\rotatebox{90}{Resting PSD 9 (SSVEP)}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssvep_5_5_not_subtracted-crop.pdf}} & % basilar tip
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssvep_29_5_not_subtracted-crop.pdf}} & % mid-basilar
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssvep_32_5_not_subtracted-crop.pdf}} & % vb junction
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssvep_38_5_not_subtracted-crop.pdf}} & % basilar tip
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssvep_8_5_not_subtracted-crop.pdf}} & % live control
-\\
 \raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
@@
 \setlength{\tabcolsep}{6pt}
-
-%\setcounter{figure}{2}
-%\setlength{\tabcolsep}{2pt}
-%\begin{figure}[H]
-%\begin{center}
-%\begin{tabular}{ccccc}
-%& Basilar Tip & Mid-Basilar & VB Junction & Basilar Tip \\ %& Live Control & Dead Control \\
-%\raisebox{-0.5\height}{\rotatebox{90}{Resting State}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_15_40-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_24_40-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_33_40-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_36_40-crop.pdf}} \\
-%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_12_40-crop.pdf}} &
-%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_40_40-crop.pdf}} \\
-%\raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf}} \\
-%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
-%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} \\
-%\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} \\
-%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
-%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}} \\
-%\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}}
-%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
-%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}}
-%\end{tabular}
-%\caption{Rabbit 10 position dependence.} % Figure 3
-%\end{center}
-%\end{figure}
-%\setlength{\tabcolsep}{6pt}
-
-%\setcounter{figure}{2}
-%\begin{figure}[H] % Transpose of previous
-%\begin{center}
-%\begin{tabular}{ccccc}
-%& Resting State & VEP & SSAEP 86 Hz & SSVEP 40 Hz \\
-%\raisebox{-0.5\height}{\rotatebox{90}{Basilar Tips}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_15_40-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} \\
-%\raisebox{-0.5\height}{\rotatebox{90}{Mid-Basilar}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_24_40-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} \\
-%\raisebox{-0.5\height}{\rotatebox{90}{VB Junction}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_33_40-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf}} \\
-%\raisebox{-0.5\height}{\rotatebox{90}{Basilar Tip}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_36_40-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}} \\
-%\raisebox{-0.5\height}{\rotatebox{90}{Live Control}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_12_40-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} \\
-%\raisebox{-0.5\height}{\rotatebox{90}{Dead Control}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_40_40-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}} &
-%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}}
-%\end{tabular}
-%\caption{Rabbit 10 position dependence.} % Figure 3
-%\end{center}
-%\end{figure}
 

### 2014-08-06 analysis/vep/plot_all_vep.m
Make publish_vep_v2 a function

@@ -89,38 +89,34 @@ if (nargin < 3)
     trials_list = 1:numel(S);
 end
 
+filters = get_filters(original_sampling_rate_in_Hz, true, true, true, true, true);
+cardiac_filters = get_filters(original_sampling_rate_in_Hz, true, false, false, false, false);
 
-% rabbit10
-%for i=1:length(S),				%for each data file in the directory
-%for i=1:length(S),				%for each data file in the directory
+preEventPlot_sec = 0.05;                                                    %time in seconds to extend plot prior to event time (marked as time zero)
+postEventPlot_sec = 0.1;
 
-%for i = [2 10 11 13 3] % rabbit 9
-%for i = [12] % rabbit 9
-%for i = [2 10 11 12 13 3] % rabbit 9
-%for i = [2 10 11] % rabbit 9
-%for i = [12 13 3] % rabbit 9
-%for i = [4 10 12 15 5] % rabbit 10
-%for i = [10]
-%for i = [1] % rabbit 9/10 baseline
-%for i = length(S)
-%for i = 10 % mid-basilar (happens to be same for rabbit 9 and 10
-%for i = 11
+channelToPlot = [2,3,5,7,8];
+%CM = [hex2dec('e9'), hex2dec('00'), hex2dec('3a'); hex2dec('ff'), hex2dec('ba'),hex2dec('00'); hex2dec('18'),hex2dec('26'),hex2dec('b0'); hex2dec('58'),hex2dec('e0'), hex2dec('00'); hex2dec('00'),hex2dec('00'),hex2dec('00')];
+CM = [hex2dec('e9'), hex2dec('00'), hex2dec('3a');
+      hex2dec('ff'), hex2dec('ba'), hex2dec('00');
+      hex2dec('40'), hex2dec('40'), hex2dec('ff');
+      hex2dec('58'), hex2dec('e0'), hex2dec('00');
+      hex2dec('b0'), hex2dec('00'), hex2dec('b0')];
+
+CM = CM/256;
+
+
 for i = trials_list
     filename = S{i};
     fprintf('filename: %s,\t%d / %d\n', filename, i, length(S));
 
     [ data, cleanDigitalIn ] = load_data([pathname filename], maxNumberOfChannels, digitalInCh, channelNames);
 
-    if publication_quality > 0
-        run('publish_vep_v2.m');
-        %run('publish_vep_off_v2.m');
-        %run('publish_vep_all.m');
-        %run('publish_fano.m');
-    else
[…]

### 2014-08-06 analysis/vep/publish_vep_v2.m

@@ -14,318 +14,140 @@
 %run('../utilities/loaddata.m');		%populates the variable names pathname, filename, and data
 %//////////////////////////////////
 
+function [] = publish_vep_v2(data, cleanDigitalIn, fs, publication_quality, filters, cardiac_filters, preEventPlot_sec, postEventPlot_sec, comment, name, channelToPlot, CM, OnOff)
 
 %///// hardcoded values that you should keep unchanged
-
-fs = original_sampling_rate_in_Hz;
                                                                            %digital input channel convention is low is LED OFF, high is LED ON; verified for VEP aruino recording code with 5rabbit, 6rabbit, 7rabbit, etc.
 LED_ON_edge = 1;                                                           %LED turns on with rising edge of digital in channel (diff = 1)
 LED_OFF_edge = -1;                                                         %LED turns off with falling edge of digital in channel (diff = -1)
-
 
 %////////////////////////////////////////////////////////////////////
 %///// hardcoded analysis options: VEP onset and offset
 %////////////////////////////////////////////////////////////////////
 
-% OPTION 1 /////// Choose how much time you would like to plot pre- and post- event onset                                                                            
-preEventPlot_sec = 0.1;                                                    %time in seconds to extend plot prior to event time (marked as time zero)
-postEventPlot_sec = 1/0.8942;                                               %time in seconds to extend plot following event time (marked as time zero). 0.9 Hz was frequency of light onset in VEP controlled by Arduino 
-
-
-% OPTION 2 /////// Choose which filters you want to use in the analysis                                                                            
-use_lpf = 1;                                                               %0 or 1; use the lowpass filter hardcoded in the lines below
-use_hpf = 0;                                                               %0 or 1; use the highpass filter hardcoded in the lines below
-use_nf_60_120_180 = 1;                                                     %0 or 1; use the 60, 120, and 180 Hz notch filters
-
-
-% OPTION 3 /////// Choose desired properties of the lowpass, highpass, and notch filter options
[…]

### 2014-08-07 analysis/figures/paper_figures.tex
VEP off now shown, and leftmost plot has labels.

@@
 & Rabbit 10 & Rabbit 9 & Rabbit 10 Control & Rabbit 9 Control \\
-\raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\rotatebox{90}{VEP On}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__labelled-crop.pdf}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} &
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep_-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{VEP Off}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__off_labelled-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep__off-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_off-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep__off-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86_labelled-crop.pdf}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} &
@@
 \raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40_labelled-crop.pdf}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} &
@@
 & Basilar Tip & Mid-Basilar & VB Junction & Basilar Tip & Live Control & Dead Control \\
-\raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\rotatebox{90}{VEP On}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__labelled-crop.pdf}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
@@
 \raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{VEP Off}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__off_labelled-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__off-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep__off-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep__off-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_off-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep__off-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86_labelled-crop.pdf}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
@@
 \raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40_labelled-crop.pdf}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &

### 2014-08-07 analysis/ssavep/plot_all_ssavep.m
Format changes to figures.

@@ -86,15 +86,10 @@ end
 %////////////////////////////////////////////////////////////////////////////////////////
 windlengthSeconds = 2;
 noverlapPercent = 0.25;%windlength * 0.25; % number overlap percent
-channelToPlot = [2,3,5,7,8];
-filters = [];
-CM = [hex2dec('e9'), hex2dec('00'), hex2dec('3a');
-      hex2dec('ff'), hex2dec('ba'), hex2dec('00');
-      hex2dec('40'), hex2dec('40'), hex2dec('ff');
-      hex2dec('58'), hex2dec('e0'), hex2dec('00');
-      hex2dec('b0'), hex2dec('00'), hex2dec('b0')];
-CM = CM/256;
 
+[ channelToPlot, CM ] = plot_settings();
+
+filters = get_filters(original_sampling_rate_in_Hz, true, false, false, false, false);
 
 
 for i = trials_list
@@ -104,6 +99,14 @@ for i = trials_list
 
     [ data, cleanDigitalIn ] = load_data([pathname filename], maxNumberOfChannels, digitalInCh, channelNames);
 
-    publish_ssavep(data, original_sampling_rate_in_Hz, windlengthSeconds, noverlapPercent, cleanDigitalIn, channelToPlot, filters, CM, ssavep, filename, allData(i), publication_quality, S{i})
+    %figure;
+    %hold on;
+    %chData = data{2, 2};
+    %%chData = run_filters(chData, filters);
+    %plot((1:numel(chData))/9600, chData);
+    %yl = ylim;
+    %plot((1:numel(chData))/9600, (cleanDigitalIn * 0.8 + 0.1) * (yl(2) - yl(1)) + yl(1));
+
+    publish_ssavep(data, original_sampling_rate_in_Hz, windlengthSeconds, noverlapPercent, cleanDigitalIn, channelToPlot, filters, CM, ssavep, filename, allData(i), publication_quality, clean_name(S{i}));
 end
 

### 2014-08-07 analysis/ssavep/publish_ssavep.m

@@ -7,12 +7,18 @@ windlength = windlengthSeconds * fs;
 %noverlapPercent = 0.25;%windlength * 0.25; % number overlap percent
 noverlap = windlength * noverlapPercent; % number overlap (timesteps)
 
-time_axis = (0:length(cleanDigitalIn)-1)*1.0/fs;
+threshold = 4; % Threshold for 60 Hz harmonics
+
+time_axis = (0:numel(cleanDigitalIn)-1)*1.0/fs;
 %figure;plot(time_axis,dataColumnDig);
 
 t1 = diff(cleanDigitalIn); % -1: experiment turns off, 0: no change, 1: experiment turns on
 t2 = find(t1 == 1); % first time when led turns on (experiment starts)
 t3 = find(t1 == -1); % last time when led turns off (experiment ends)
+
+if isempty(t3)
+    t3 = length(cleanDigitalIn);
+end
 
 cutLengthB = t2; %fs * cutSecondsBegining;
 cutLengthE = t3; %fs * cutSecondsEnd;
@@ -24,9 +30,6 @@ assert(cutLengthB < cutLengthE);
 
 %channelToPlot = [2,3,5,7,8];
 channels_plotted = [];
-
-hp = fdesign.highpass('Fst,Fp,Ast,Ap',(2.0),(10.0),90,1,fs);             %highpass filter; passband 90 Hz, stopband 105 Hz, 1dB passband ripple, 90 dB stopband attenuation, sampling frequency fs, butterworth 
-hpf = design(hp, 'butter');
 
 % choose the colormap for the plots
 %CM = [hex2dec('00'), hex2dec('00'), hex2dec('00');
@@ -57,7 +60,16 @@ legends = [];
 % draw the figure with white background and full screen
 %fgh = figure('Color',[1 1 1],'units','normalized','outerposition',[0 0 1 1]);
 %fgh = figure('Color',[1 1 1],'units','pixels','outerposition',[0 0 1366 768]);
-fgh = figure('Color',[1 1 1],'units','pixels','outerposition',[0 0 1366 768], 'visible', 'off');
+%fgh = figure('Color',[1 1 1],'units','pixels','outerposition',[0 0 1400 1100], 'visible', 'off');
[…]

### 2014-08-07 analysis/figures/paper_figures.tex
Layout figures

--- 2014-08-06 analysis/figures/paper_figures.tex
@@
 
-\usepackage[margin=1.0in]{geometry}
+\usepackage[margin=0.5in]{geometry}
 %\usepackage[paperwidth=5.5in, paperheight=8.5in]{geometry}
@@
 \usepackage{hyperref}
+\usepackage{multirow}
 
@@
 
+%% Rabbit 10 = Subject 1
+%% Rabbit 9 = Subject 2
 \begin{figure}[H]
@@
 
-\setcounter{figure}{1}
+\setlength{\tabcolsep}{2pt}
 \begin{figure}[H]
 \begin{center}
-\begin{tabular}{ccc|cc}
-& Rabbit 10 & Rabbit 9 & Rabbit 10 Control & Rabbit 9 Control \\
-\raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep_-crop.pdf}} \\
+\begin{tabular}{c|cc|cc}
+& \multicolumn{2}{c|}{Experiment} & \multicolumn{2}{c}{Control} \\
+& Subject 1 & Subject 2 & Subject 1 & Subject 2 \\
+\hline
+\raisebox{-0.5\height}{\rotatebox{90}{VEP On}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__labelled-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep_-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{VEP Off}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__off_labelled-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep__off-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_off-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep__off-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86-crop.pdf}} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86_labelled-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40-crop.pdf}}
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40_labelled-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40-crop.pdf}}
 \end{tabular}
-\caption{At Basilar Tip for rabbit 9; at mid-basilar for rabbit 10.} % Figure 2
+\caption{Performance of the electrodes at the optimal location for the endovascular location compared with the performance on the live control trials.
+The SSAEP and SSVEP experimental trials for Subject 1 are shown for the mid-basilar location.
+All other performances are shown at the basilar tip position.
+In each of the experiments, all experimental trials elicited a much larger response than the control experiments, which indicates that true non-artifactual responses were recorded.
+In addition, the endovascular electrode achieved superior signals compared to the scalp electrodes for the VEP and SSAEP experiments.}
+% Figure 2
 \end{center}
 \end{figure}
+\setlength{\tabcolsep}{6pt}
 
@@
 \begin{center}
-\begin{tabular}{ccccc|cc}
-& Basilar Tip & Mid-Basilar & VB Junction & Basilar Tip & Live Control & Dead Control \\
-\raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} \\
+\begin{tabular}{c|cccc|cc}
+         & \multicolumn{4}{c|}{Experiment}                       & \multicolumn{2}{c}{Control} \\
+         &             &             &             &             & Live         & Dead \\
+\hline
+Location & Basilar Tip & Mid-Basilar & VB Junction & Basilar Tip & Basilar Tip  & Basilar Tip \\
+Time     & 11:57:42    & 14:13:26    & 15:54:54    & 16:47:47    & 12:15:47     & 17:22:22 \\
+\hline
+\raisebox{-0.5\height}{\rotatebox{90}{VEP On}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__labelled-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} \\
+\raisebox{-0.5\height}{\rotatebox{90}{VEP Off}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__off_labelled-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__off-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep__off-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep__off-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_off-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep__off-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86_labelled-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}} \\
 \raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}}
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40_labelled-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}}
 \end{tabular}
-\caption{Rabbit 10 position dependence.} % Figure 3
+\caption{Demonstration of position dependence for Subject 1.
+The performance of the endovascular electrode varies as its location is changed.
+The performance is consistent between the two basilar tip trials.
+}
+% Figure 3
 \end{center}
@@
 
+%\begin{figure}[H]
+%\begin{center}
+%\begin{tabular}{cc}
+%\multirow{2}{*}{
+%\begin{tabular}{ccc}
+%Raw Trace & VEP Aligned & \\
+%\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__start-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__cardiac_labelled-crop.pdf}} &
+%\\
+%\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__end-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__labelled-crop.pdf}} &
+%\end{tabular}} &
+%\raisebox{-0.5\height}{cardiac aligned avg vep + EKG} \\
+%& \raisebox{-0.5\height}{\includegraphics[scale=0.32]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__qrs-crop.pdf}} \\
+%%\raisebox{-0.5\height}{contaminated raw trace + cardiac} &
+%%\raisebox{-0.5\height}{VEP aligned contaminated EKG} &
+%%\raisebox{-0.5\height}{vep aligned cleaned} &
+%%\raisebox{-0.5\height}{raw cleaned} &
+%%\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__end-crop.pdf}}
+%\end{tabular}
+
+%\begin{figure}[H]
+%\begin{center}
+%\begin{tabular}{cccc}
+%& Raw Trace & VEP Aligned & cardiac aligned avg vep + EKG \\
+%\raisebox{-0.5\height}{\rotatebox{90}{Contaminated}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__start-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__cardiac_labelled-crop.pdf}} &
+%\raisebox{-0.5\height}{\multirow{2}{*}{\includegraphics[scale=0.64]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__qrs-crop.pdf}}} \\
+%\raisebox{-0.5\height}{\rotatebox{90}{Cleaned}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__end-crop.pdf}} &
+%\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__labelled-crop.pdf}} &
+%\end{tabular}
+
 \begin{figure}[H]
 \begin{center}
-\begin{tabular}{ccc}
-\raisebox{-0.5\height}{contaminated raw trace + cardiac} &
-\raisebox{-0.5\height}{\includegraphics[scale=1.0]{TODO.pdf}} \\
-\raisebox{-0.5\height}{VEP aligned contaminated EKG} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__all_qrs.png}} \\
-\raisebox{-0.5\height}{cardiac aligned avg vep + EKG} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__qrs-crop.pdf}} \\
-\raisebox{-0.5\height}{vep aligned cleaned} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__all.png}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_.pdf}} \\
-\raisebox{-0.5\height}{raw cleaned} &
-\raisebox{-0.5\height}{\includegraphics[scale=1.0]{TODO.pdf}}
+\begin{tabular}{c|cc|c}
+\raisebox{-0.5\height}{\multirow{3}{*}{
+\begin{tabular}{c}
+Cardiac-Aligned  Measurements \vspace{0.7cm} \\
+\includegraphics[scale=0.64]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__qrs-crop.pdf}
 \end{tabular}
-\caption{Cardiac contamination and cleaning.} % Figure 5
+}} &
+Raw Trace & VEP-Aligned \\
+\hline
+&
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__start-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__cardiac_labelled-crop.pdf}} &
+\rotatebox{180}{\raisebox{-0.5\height}{\rotatebox{90}{Contaminated}}} \\
+&
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__end-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__labelled-crop.pdf}} &
+\rotatebox{180}{\raisebox{-0.5\height}{\rotatebox{90}{Cleaned}}}
+\end{tabular}
+
+\caption{Cardiac contamination and cleaning. 1076 trials for qrs mean} % Figure 5
 \end{center}
@@
 
+%% VEP 
+%filename: _Tue_06.05.2014_11%3A17%3A10_vep_,    2 / 13
+%Number of Trials: 153
+%Number of Trials: 153
+%filename: _Thu_15.05.2014_11%3A57%3A42_vep_,    4 / 16
+%Number of Trials: 205
+%Number of Trials: 206
+%filename: _Thu_15.05.2014_14%3A13%3A26_vep_,    10 / 16
+%Number of Trials: 192
+%Number of Trials: 191
+%filename: _Thu_15.05.2014_15%3A54%3A54_vep_,    12 / 16
+%Number of Trials: 208
+%Number of Trials: 208
+%filename: _Thu_15.05.2014_16%3A47%3A47_vep_,    15 / 16
+%Number of Trials: 208
+%Number of Trials: 208
+%filename: _Thu_15.05.2014_12%3A15%3A47_vep_ctr, 5 / 16
+%Number of Trials: 208
+%Number of Trials: 208
+%filename: _Thu_15.05.2014_17%3A22%3A22_vep_,    16 / 16
+%Number of Trials: 208
+%Number of Trials: 208
+%filename: _Tue_06.05.2014_11%3A25%3A22_vep_,    3 / 13
+%Number of Trials: 153
+%Number of Trials: 153
+%filename: _Thu_15.05.2014_14%3A13%3A26_vep_,    10 / 16
+%Number of Trials: 192
+%Number of Trials: 191
+
+%% SSAVEP
+%filename: _Thu_15.05.2014_12%3A08%3A22_ssvep_40,    11 / 39
+%Experiment: 320640 584434
+%Baseline: 9600 301440
+%filename: _Thu_15.05.2014_12%3A31%3A02_ssaep_86,    15 / 40
+%Experiment: 307603 585728
+%Baseline: 9600 288403
+%filename: _Tue_06.05.2014_11%3A14%3A51_ssvep_40,    5 / 39
+%Experiment: 320045 583839
+%Baseline: 9600 300845
+%filename: _Tue_06.05.2014_11%3A37%3A22_ssaep_86,    8 / 41
+%Experiment: 70740 585728
+%Baseline: 9600 51540
+%filename: _Tue_06.05.2014_11%3A23%3A01_ssvep_40,    8 / 39
+%Experiment: 317488 581282
+%Baseline: 9600 298288
+%filename: _Tue_06.05.2014_11%3A42%3A15_ssaep_86,    11 / 41
+%Experiment: 94848 585856
+%Baseline: 9600 75648
+%filename: _Thu_15.05.2014_12%3A13%3A26_ssvep_ctr_40,    14 / 39
+%Experiment: 328552 592346
+%Baseline: 9600 309352
+%filename: _Thu_15.05.2014_12%3A26%3A26_ssaep_ctr_86,    12 / 40
+%Experiment: 305364 585856
+%Baseline: 9600 286164
+%filename: _Thu_15.05.2014_09%3A52%3A53_ssvep_40,    2 / 39
+%Experiment: 328875 592669
+%Baseline: 9600 309675
+%filename: _Thu_15.05.2014_12%3A08%3A22_ssvep_40,    11 / 39
+%Experiment: 320640 584434
+%Baseline: 9600 301440
+%filename: _Thu_15.05.2014_14%3A20%3A24_ssvep_40,    23 / 39
+%Experiment: 323398 587192
+%Experiment: 371398 587192
+%Baseline: 9600 304198
+%filename: _Thu_15.05.2014_16%3A02%3A44_ssvep_40,    32 / 39
+%Experiment: 609145 1156050
+%Baseline: 9600 589945
+%filename: _Thu_15.05.2014_16%3A38%3A47_ssvep_40,    35 / 39
+%Experiment: 611121 1158026
+%Baseline: 9600 591921
+%filename: _Thu_15.05.2014_12%3A13%3A26_ssvep_ctr_40,    14 / 39
+%Experiment: 328552 592346
+%Baseline: 9600 309352
+%filename: _Thu_15.05.2014_17%3A18%3A01_ssvep_40,    38 / 39
+%Experiment: 606919 1153824
+%Baseline: 9600 587719
+%filename: _Thu_15.05.2014_10%3A04%3A16_ssaep_86,    3 / 40
+%Experiment: 303843 585856
+%Baseline: 9600 284643
+%filename: _Thu_15.05.2014_12%3A31%3A02_ssaep_86,    15 / 40
+%Experiment: 307603 585728
+%Baseline: 9600 288403
+%filename: _Thu_15.05.2014_14%3A26%3A54_ssaep_86,    24 / 40
+%Experiment: 301020 585728
+%Baseline: 9600 281820
+%filename: _Thu_15.05.2014_16%3A12%3A19_ssaep_86,    33 / 40
+%Experiment: 593190 1161856
+%Baseline: 9600 573990
+%filename: _Thu_15.05.2014_16%3A58%3A34_ssaep_86,    36 / 40
+%Experiment: 595230 1161728
+%Baseline: 9600 576030
+%filename: _Thu_15.05.2014_12%3A26%3A26_ssaep_ctr_86,    12 / 40
+%Experiment: 305364 585856
+%Baseline: 9600 286164
+%filename: _Thu_15.05.2014_17%3A12%3A38_ssaep_86,    40 / 40
+%Experiment: 595109 1161728
+%Baseline: 9600 575909
+
 \end{document}

### 2014-08-07 analysis/qrs/qrs_figure.m

@@ -1,0 +1,94 @@
+clear;
+close all;
+
+addpath('../utilities');
+
+rabbit_ID = '10rabbit_may_15_2014';
+experiment = 'vep';
+index = 10;
+
+%% Constants
+[ channelNames, gtechGND, earth ] = rabbit_information(rabbit_ID);
+[ maxNumberOfChannels, digitalInCh, original_sampling_rate_in_Hz ] = constants();
+[ channelToPlot, CM ] = plot_settings();
+
+%% Filters
+filters = get_filters(original_sampling_rate_in_Hz, true, false, false, false, false);
+cardiac_filters = get_filters(original_sampling_rate_in_Hz, true, false, false, false, false);
+
+pathname_comments = ['../../../../data/easter/' rabbit_ID '/neuro/neuro_experiment_log.txt'];
+
+pathname = ['../../../../data/easter/' rabbit_ID '/neuro/binary_data/' experiment '/'];
+pathname_matdata = ['../../../../data/easter/' rabbit_ID '/neuro/matlab_data/' experiment '/'];
+
+[ S, allData ] = get_information(pathname, pathname_comments, upper(experiment));
+
+filename = S{index};
+
+% Clean name format
+name = clean_name(S{index});
+
+%% Load data
+[ data, cleanDigitalIn ] = load_data([pathname filename], maxNumberOfChannels, digitalInCh, channelNames);
+
+cardiacData = data{strcmp(data, 'Bottom Precordial'), 2};
+cardiacData = run_filters(cardiacData, cardiac_filters);
+
+% draw the figure with white background and fixed size (in pixels)
+width = 275;   % width of figure (just plot itself, not labels)
+height = 225;  % height of figure (just plot itself, not labels)
+margins = 100; % extra space for labels
+position = [0 0 (width + 2 * margins) (height + 2 * margins)];
+
+% Open invisible screen for figure
+f1 = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'on'); axes('units', 'pixel', 'position', [margins margins width height]);
+f2 = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'on'); axes('units', 'pixel', 'position', [margins margins width height]);
[…]

### 2014-08-07 analysis/figures/baseline_spectral_content.tex
Adding a bunch of layouts

\documentclass[]{article}

\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}

\pagestyle{plain}

\begin{document}

\begin{figure}[H]
\begin{center}
\raisebox{-0.5\height}{\includegraphics[scale=0.2]{brain.pdf}}
\hspace{0.2cm}
\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
\vspace{0.5cm}
\begin{tabular}{ccc}
& SSVEP 40 Hz & SSAEP 86 Hz \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40_baseline.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86_baseline.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40_baseline.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86_baseline.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40_baseline.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86_baseline.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40_baseline.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86_baseline.pdf}
\end{tabular}
\caption{Rabbit 10 experimental responses - spectral content during baseline.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
SSVEP 40 Hz & SSAEP 86 Hz \\
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40_baseline.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86_baseline.pdf}
\end{tabular}
\caption{Rabbit 10 live control - spectral content during baseline.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
SSVEP 40 Hz & SSAEP 86 Hz \\
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40_baseline.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86_baseline.pdf}
\end{tabular}
\caption{Rabbit 10 dead control - spectral content during baseline.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
SSVEP 40 Hz & SSAEP 86 Hz \\
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_09_52_53_ssvep_40_baseline.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_10_04_16_ssaep_86_baseline.pdf}
\end{tabular}
\caption{Rabbit 10 baseline - spectral content during baseline.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\raisebox{-0.5\height}{\includegraphics[scale=0.2]{brain.pdf}}
\hspace{0.2cm}
\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
\vspace{0.5cm}
\begin{tabular}{ccc}
& SSVEP 40 Hz & SSAEP 86 Hz \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40_baseline.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86_baseline.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_14_02_01_ssvep_40_baseline.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_14_11_09_ssaep_86_baseline.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_14_41_46_ssvep_40_baseline.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_14_53_21_ssaep_86_baseline.pdf} \\
%\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
%\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_15_11_25_ssvep_40_baseline.pdf} &
%\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_15_20_29_ssaep_86_baseline.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_15_48_24_ssvep_50_baseline.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_15_57_52_ssaep_86_baseline.pdf}
\end{tabular}
\caption{Rabbit 9 experimental responses - spectral content during baseline.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
SSVEP 40 Hz & SSAEP 86 Hz \\
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40_baseline.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86_baseline.pdf}
\end{tabular}
\caption{Rabbit 9 live control - spectral content during baseline.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
SSVEP 40 Hz & SSAEP 86 Hz \\
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_09_52_56_ssvep_40_baseline.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_10_08_48_ssaep_86_baseline.pdf}
\end{tabular}
\caption{Rabbit 9 baseline - spectral content during baseline.}
\end{center}
\end{figure}

\end{document}

### 2014-08-07 analysis/figures/diff_r_peak.tex
Adding a bunch of layouts

\documentclass[]{article}

\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}

\pagestyle{plain}

\begin{document}
%\begin{minipage}{6in}
%\centering
%\raisebox{-0.5\height}{\includegraphics[height=0.75in]{brain.pdf}}
%\hspace*{.2in}
%\raisebox{-0.5\height}{\includegraphics[height=0.3in]{brain.pdf}}
%\end{minipage}

\begin{figure}[H]
\begin{center}
\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
\hspace{0.2cm}
\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
\vspace{0.5cm}
\begin{tabular}{cccc}
& VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_11_57_42_vep__dt-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40_dt-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86_dt-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__dt-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40_dt-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86_dt-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_15_54_54_vep__dt-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40_dt-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86_dt-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_47_47_vep__dt-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40_dt-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86_dt-crop.pdf}
\end{tabular}
\caption{Rabbit 10 experimental responses.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_dt-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40_dt-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86_dt-crop.pdf}
\end{tabular}
\caption{Rabbit 10 live control.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
& VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_17_10_vep__dt-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40_dt-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86_dt-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_04_18_vep__dt-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_02_01_ssvep_40_dt-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_11_09_ssaep_86_dt-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_44_57_vep__dt-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_41_46_ssvep_40_dt-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_53_21_ssaep_86_dt-crop.pdf} \\
%\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_13_50_vep__dt-crop.pdf} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_11_25_ssvep_40_dt-crop.pdf} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_20_29_ssaep_86_dt-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_50_43_vep__dt-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_48_24_ssvep_50_dt-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_57_52_ssaep_86_dt-crop.pdf}
\end{tabular}
\caption{Rabbit 9 experimental responses.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_25_22_vep__dt-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40_dt-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86_dt-crop.pdf}
\end{tabular}
\caption{Rabbit 9 live control.}
\end{center}
\end{figure}

\end{document}

### 2014-08-07 analysis/figures/difference.tex
Adding a bunch of layouts

--- 2014-08-07 analysis/figures/baseline_spectral_content.tex
@@
 & SSVEP 40 Hz & SSAEP 86 Hz \\
-\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40_baseline.pdf} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86_baseline.pdf} \\
-\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40_baseline.pdf} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86_baseline.pdf} \\
-\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40_baseline.pdf} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86_baseline.pdf} \\
-\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40_baseline.pdf} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86_baseline.pdf}
+\rotatebox{90}{\hspace{1.0cm}Rabbit 10} &
+\includegraphics[scale=0.200]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_15_12.pdf} &
+\includegraphics[scale=0.200]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_11_8.pdf} \\
+\rotatebox{90}{\hspace{1.0cm}Rabbit 9} &
+\includegraphics[scale=0.200]{../ssavep/matlab_data/9rabbit_may_6_2014_ssvep_8_11.pdf} &
+\includegraphics[scale=0.200]{../ssavep/matlab_data/9rabbit_may_6_2014_ssaep_14_17.pdf}
 \end{tabular}
-\caption{Rabbit 10 experimental responses - spectral content during baseline.}
-\end{center}
-\end{figure}
-
-\begin{figure}[H]
-\begin{center}
-\begin{tabular}{cccc}
-SSVEP 40 Hz & SSAEP 86 Hz \\
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40_baseline.pdf} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86_baseline.pdf}
-\end{tabular}
-\caption{Rabbit 10 live control - spectral content during baseline.}
-\end{center}
-\end{figure}
-
-\begin{figure}[H]
-\begin{center}
-\begin{tabular}{cccc}
-SSVEP 40 Hz & SSAEP 86 Hz \\
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40_baseline.pdf} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86_baseline.pdf}
-\end{tabular}
-\caption{Rabbit 10 dead control - spectral content during baseline.}
-\end{center}
-\end{figure}
-
-\begin{figure}[H]
-\begin{center}
-\begin{tabular}{cccc}
-SSVEP 40 Hz & SSAEP 86 Hz \\
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_09_52_53_ssvep_40_baseline.pdf} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_10_04_16_ssaep_86_baseline.pdf}
-\end{tabular}
-\caption{Rabbit 10 baseline - spectral content during baseline.}
-\end{center}
-\end{figure}
-
-\begin{figure}[H]
-\begin{center}
-\raisebox{-0.5\height}{\includegraphics[scale=0.2]{brain.pdf}}
-\hspace{0.2cm}
-\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
-\vspace{0.5cm}
-\begin{tabular}{ccc}
-& SSVEP 40 Hz & SSAEP 86 Hz \\
-\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40_baseline.pdf} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86_baseline.pdf} \\
-\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_14_02_01_ssvep_40_baseline.pdf} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_14_11_09_ssaep_86_baseline.pdf} \\
-\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_14_41_46_ssvep_40_baseline.pdf} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_14_53_21_ssaep_86_baseline.pdf} \\
-%\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
-%\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_15_11_25_ssvep_40_baseline.pdf} &
-%\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_15_20_29_ssaep_86_baseline.pdf} \\
-\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_15_48_24_ssvep_50_baseline.pdf} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_15_57_52_ssaep_86_baseline.pdf}
-\end{tabular}
-\caption{Rabbit 9 experimental responses - spectral content during baseline.}
-\end{center}
-\end{figure}
-
-\begin{figure}[H]
-\begin{center}
-\begin{tabular}{cc}
-SSVEP 40 Hz & SSAEP 86 Hz \\
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40_baseline.pdf} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86_baseline.pdf}
-\end{tabular}
-\caption{Rabbit 9 live control - spectral content during baseline.}
-\end{center}
-\end{figure}
-
-\begin{figure}[H]
-\begin{center}
-\begin{tabular}{cc}
-SSVEP 40 Hz & SSAEP 86 Hz \\
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_09_52_56_ssvep_40_baseline.pdf} &
-\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_10_08_48_ssaep_86_baseline.pdf}
-\end{tabular}
-\caption{Rabbit 9 baseline - spectral content during baseline.}
+\caption{}
 \end{center}

### 2014-08-07 analysis/figures/experimental_spectral_content.tex
Adding a bunch of layouts

\documentclass[]{article}

\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}

\pagestyle{plain}

\begin{document}

\begin{figure}[H]
\begin{center}
\raisebox{-0.5\height}{\includegraphics[scale=0.2]{brain.pdf}}
\hspace{0.2cm}
\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
\vspace{0.5cm}
\begin{tabular}{ccc}
& SSVEP 40 Hz & SSAEP 86 Hz \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40_experimental.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86_experimental.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40_experimental.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86_experimental.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40_experimental.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86_experimental.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40_experimental.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86_experimental.pdf}
\end{tabular}
\caption{Rabbit 10 experimental responses - spectral content during experimental.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
SSVEP 40 Hz & SSAEP 86 Hz \\
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40_experimental.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86_experimental.pdf}
\end{tabular}
\caption{Rabbit 10 live control - spectral content during experimental.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
SSVEP 40 Hz & SSAEP 86 Hz \\
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40_experimental.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86_experimental.pdf}
\end{tabular}
\caption{Rabbit 10 dead control - spectral content during experimental.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
SSVEP 40 Hz & SSAEP 86 Hz \\
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_09_52_53_ssvep_40_experimental.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_10_04_16_ssaep_86_experimental.pdf}
\end{tabular}
\caption{Rabbit 10 baseline - spectral content during experimental.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\raisebox{-0.5\height}{\includegraphics[scale=0.2]{brain.pdf}}
\hspace{0.2cm}
\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
\vspace{0.5cm}
\begin{tabular}{ccc}
& SSVEP 40 Hz & SSAEP 86 Hz \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40_experimental.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86_experimental.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_14_02_01_ssvep_40_experimental.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_14_11_09_ssaep_86_experimental.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_14_41_46_ssvep_40_experimental.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_14_53_21_ssaep_86_experimental.pdf} \\
%\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
%\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_15_11_25_ssvep_40_experimental.pdf} &
%\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_15_20_29_ssaep_86_experimental.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_15_48_24_ssvep_50_experimental.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_15_57_52_ssaep_86_experimental.pdf}
\end{tabular}
\caption{Rabbit 9 experimental responses - spectral content during experimental.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
SSVEP 40 Hz & SSAEP 86 Hz \\
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40_experimental.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86_experimental.pdf}
\end{tabular}
\caption{Rabbit 9 live control - spectral content during experimental.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
SSVEP 40 Hz & SSAEP 86 Hz \\
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_09_52_56_ssvep_40_experimental.pdf} &
\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_10_08_48_ssaep_86_experimental.pdf}
\end{tabular}
\caption{Rabbit 9 baseline - spectral content during experimental.}
\end{center}
\end{figure}

\end{document}

### 2014-08-07 analysis/figures/fano.tex
Adding a bunch of layouts

\documentclass[]{article}

\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}

\pagestyle{plain}

\begin{document}

\begin{figure}[H]
\begin{center}
\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
\hspace{0.2cm}
\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
\vspace{0.5cm}
\begin{tabular}{ccc}
%& VEP On Response & VEP Off Response \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__fano-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__fano_late-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__fano-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__fano_late-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep__fano-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep__fano_late-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep__fano-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep__fano_late-crop.pdf} \\
\end{tabular}
\caption{Rabbit 10 experimental VEP.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
%VEP On Response & VEP Off Response \\
%\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_fano-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_fano_late-crop.pdf} \\
\end{tabular}
\caption{Rabbit 10 live control VEP.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
\hspace{0.2cm}
\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
\vspace{0.5cm}
\begin{tabular}{ccc}
%& VEP On Response & VEP Off Response \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep__fano-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep__fano_late-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep__fano-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep__fano_late-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep__fano-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep__fano_late-crop.pdf} \\
%\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
%\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep__fano-crop.pdf} &
%\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep__fano_late-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep__fano-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep__fano_late-crop.pdf}
\end{tabular}
\caption{Rabbit 9 experimental responses.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
%VEP On Response & VEP Off Response \\
%\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep_-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep__fano-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep__fano_late-crop.pdf}
\end{tabular}
\caption{Rabbit 9 live control.}
\end{center}
\end{figure}

\end{document}

### 2014-08-07 analysis/figures/figures.tex
Adding a bunch of layouts

--- 2014-07-24 analysis/figures/figures.tex
@@
 % 0.126
+
+% 0.161
+% 0.126
+% 0.126
 \begin{document}
+%\begin{minipage}{6in}
+%\centering
+%\raisebox{-0.5\height}{\includegraphics[height=0.75in]{brain.pdf}}
+%\hspace*{.2in}
+%\raisebox{-0.5\height}{\includegraphics[height=0.3in]{brain.pdf}}
+%\end{minipage}
+
 \begin{figure}[H]
 \begin{center}
-\includegraphics{brain.pdf} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.2]{brain.pdf}}
+\hspace{0.2cm}
+\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
 \vspace{0.5cm}
-\begin{tabular}{cccc}
-& VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
+\begin{tabular}{ccc}
+& VEP On Response & VEP Off Response \\
 \rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
-\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf} \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_.pdf} &
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__off.pdf} \\
 \rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
-\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf} \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_.pdf} &
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__off.pdf} \\
 \rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
-\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf} \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_.pdf} &
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep__off.pdf} \\
 \rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
-\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_.pdf} &
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep__off.pdf}
+\end{tabular}
+\caption{Rabbit 10 experimental VEP.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{cc}
+VEP On Response & VEP Off Response \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr.pdf} &
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_off.pdf}
+\end{tabular}
+\caption{Rabbit 10 live control VEP.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{cc}
+VEP On Response & VEP Off Response \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_.pdf} &
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep__off.pdf}
+\end{tabular}
+\caption{Rabbit 10 dead control VEP.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{cc}
+VEP On Response & VEP Off Response \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_09_55_41_vep_.pdf}
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_09_55_41_vep__off.pdf} &
+\end{tabular}
+\caption{Rabbit 10 baseline VEP.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\raisebox{-0.5\height}{\includegraphics[scale=0.2]{brain.pdf}}
+\hspace{0.2cm}
+\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
+\vspace{0.5cm}
+\begin{tabular}{ccc}
+& SSVEP 40 Hz & SSAEP 86 Hz \\
+\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40.pdf} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86.pdf} \\
+\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40.pdf} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86.pdf} \\
+\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40.pdf} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86.pdf} \\
+\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40.pdf} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86.pdf}
 \end{tabular}
@@
 \begin{tabular}{cccc}
-VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
-\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}
+SSVEP 40 Hz & SSAEP 86 Hz \\
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40.pdf} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86.pdf}
 \end{tabular}
@@
 \begin{center}
-\includegraphics{brain.pdf} \\
+\begin{tabular}{cccc}
+SSVEP 40 Hz & SSAEP 86 Hz \\
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40.pdf} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86.pdf}
+\end{tabular}
+\caption{Rabbit 10 dead control.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{cccc}
+SSVEP 40 Hz & SSAEP 86 Hz \\
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_09_52_53_ssvep_40.pdf} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Thu_15_05_2014_10_04_16_ssaep_86.pdf}
+\end{tabular}
+\caption{Rabbit 10 baseline.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\raisebox{-0.5\height}{\includegraphics[scale=0.2]{brain.pdf}}
+\hspace{0.2cm}
+\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
 \vspace{0.5cm}
-\begin{tabular}{cccc}
-& VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
+\begin{tabular}{ccc}
+& VEP On Response & VEP Off Response \\
 \rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
-\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf} \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_.pdf} &
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep__off.pdf} \\
 \rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
-\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep_-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_14_02_01_ssvep_40-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Tue_06_05_2014_14_11_09_ssaep_86-crop.pdf} \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep_.pdf} &
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep__off.pdf} \\
 \rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
-\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep_-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_14_41_46_ssvep_40-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Tue_06_05_2014_14_53_21_ssaep_86-crop.pdf} \\
-\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
-\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep_-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_15_11_25_ssvep_40-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Tue_06_05_2014_15_20_29_ssaep_86-crop.pdf} \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep_.pdf} &
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep__off.pdf} \\
+%\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
+%\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep_.pdf} &
+%\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep__off.pdf} \\
 \rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
-\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep_-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_15_48_24_ssvep_50-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Tue_06_05_2014_15_57_52_ssaep_86-crop.pdf}
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep_.pdf} &
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep__off.pdf}
 \end{tabular}
@@
 \begin{center}
-\begin{tabular}{cccc}
-VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
-\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep_-crop.pdf} &
-\includegraphics[scale=0.126]{../ssvep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40-crop.pdf} &
-\includegraphics[scale=0.126]{../ssaep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86-crop.pdf}
+\begin{tabular}{cc}
+VEP On Response & VEP Off Response \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep_.pdf} &
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep__off.pdf}
+\end{tabular}
+\caption{Rabbit 9 live control VEP.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{cc}
+VEP On Response & VEP Off Response \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_09_55_56_vep_3m.pdf}
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_09_55_56_vep_3m_off.pdf} &
+\end{tabular}
+\caption{Rabbit 9 baseline VEP.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\raisebox{-0.5\height}{\includegraphics[scale=0.2]{brain.pdf}}
+\hspace{0.2cm}
+\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
+\vspace{0.5cm}
+\begin{tabular}{ccc}
+& SSVEP 40 Hz & SSAEP 86 Hz \\
+\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40.pdf} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86.pdf} \\
+\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_14_02_01_ssvep_40.pdf} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_14_11_09_ssaep_86.pdf} \\
+\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_14_41_46_ssvep_40.pdf} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_14_53_21_ssaep_86.pdf} \\
+%\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
+%\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_15_11_25_ssvep_40.pdf} &
+%\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_15_20_29_ssaep_86.pdf} \\
+\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_15_48_24_ssvep_50.pdf} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_15_57_52_ssaep_86.pdf}
+\end{tabular}
+\caption{Rabbit 9 experimental responses.}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{cc}
+SSVEP 40 Hz & SSAEP 86 Hz \\
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40.pdf} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86.pdf}
 \end{tabular}
@@
 
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{cc}
+SSVEP 40 Hz & SSAEP 86 Hz \\
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_09_52_56_ssvep_40.pdf} &
+\includegraphics[scale=0.161]{../ssavep/matlab_data/_Tue_06_05_2014_10_08_48_ssaep_86.pdf}
+\end{tabular}
+\caption{Rabbit 9 baseline.}
+\end{center}
+\end{figure}
+
 \end{document}

### 2014-08-07 analysis/figures/figures_other.tex
Adding a bunch of layouts

\documentclass[]{article}

\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{array}

\pagestyle{plain}

\begin{document}
%\begin{minipage}{6in}
%\centering
%\raisebox{-0.5\height}{\includegraphics[height=0.75in]{brain.pdf}}
%\hspace*{.2in}
%\raisebox{-0.5\height}{\includegraphics[height=0.3in]{brain.pdf}}
%\end{minipage}

\begin{figure}[H]
\begin{center}
\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
\hspace{0.2cm}
\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
\vspace{0.5cm}
\begin{tabular}{m{5cm}m{20cm}}
VEP, Distal Basilar Artery, recording from guidewire against a Ag/AgCl reference &
\includegraphics[scale=0.250]{../vep/matlab_data/_Fri_11_04_2014_15_25_33_vep_.pdf} \\
VEP, Distal Basilar Artery, recording from guidewire &
\includegraphics[scale=0.250]{../vep/matlab_data/_Fri_11_04_2014_15_33_56_vep_.pdf} \\
VEP Dead Control &
\includegraphics[scale=0.250]{../vep/matlab_data/_Fri_11_04_2014_17_00_46_vep_.pdf} \\
\end{tabular}
\caption{Rabbit 6 VEP.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
\hspace{0.2cm}
\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
\vspace{0.5cm}
\begin{tabular}{m{5cm}m{20cm}}
%SSVEP 40 Hz, no signal on anything &
%\includegraphics[scale=0.250]{../ssvep/matlab_data/_Fri_11_04_2014_15_27_09_ssvep_.pdf} \\
SSVEP 40 Hz, distal basilar artery, recording from guidewire &
\includegraphics[scale=0.250]{../ssvep/matlab_data/_Fri_11_04_2014_15_35_24_ssvep_.pdf} \\
SSVEP 12 Hz, distal basilar artery, recording from guidewire &
\includegraphics[scale=0.250]{../ssvep/matlab_data/_Fri_11_04_2014_15_42_09_ssvep_.pdf} \\
SSVEP 12 Hz Dead Control &
\includegraphics[scale=0.250]{../ssvep/matlab_data/_Fri_11_04_2014_17_02_31_ssvep_.pdf} \\
SSVEP 40 Hz Dead Control &
\includegraphics[scale=0.250]{../ssvep/matlab_data/_Fri_11_04_2014_17_03_23_ssvep_.pdf} \\
\end{tabular}
\caption{Rabbit 6 SSVEP.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
\hspace{0.2cm}
\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
\vspace{0.5cm}
\begin{tabular}{m{5cm}m{20cm}}
VEP, angled glide catheter (ag/agcl) in abdominal descending aorta &
\includegraphics[scale=0.250]{../vep/matlab_data/_Tue_15_04_2014_15_45_35_vep_.pdf} \\
SSVEP 40 Hz, angled glide catheter (ag/agcl) in abdominal descending aorta &
\includegraphics[scale=0.250]{../ssvep/matlab_data/_Tue_15_04_2014_15_48_37_ssvep_40_.pdf} \\
SSVEP 12 Hz, angled glide catheter (ag/agcl) in abdominal descending aorta &
\includegraphics[scale=0.250]{../ssvep/matlab_data/_Tue_15_04_2014_15_49_46_ssvep_12.pdf}
\end{tabular}
\caption{Rabbit 7.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
%\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
%\hspace{0.2cm}
%\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
%\vspace{0.5cm}
\begin{tabular}{m{5cm}m{20cm}}
VEP, Baseline Brain Recordings - no catheter in the rabbit - endo not hooked up &
\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_10_24_11_vep_.pdf} \\
VEP right eye, X-pedion wire through echelon-10, basilar tip (via left vert); wire projects slightly beyond the catheter (documented on imaging) &
\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_12_55_56_vep_.pdf} \\
12:55:56 - VEP right eye, 3 minutes, GND: nose -X-pedion wire through echelon-10, basilar tip (via left vert); wire projects slightly beyond the catheter (documented on imaging) &
\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_12_55_56_vep_.pdf} \\
13:13:22 - VEP  right eye - 3 min -echelon-10, basilar tip (via left vert), Ag/AgCl electrode &
\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_13_13_22_vep_.pdf} \\
13:31:48 - VEP right eye - 5 min -echelon-10, basilar tip (via left vert), Ag/AgCl electrode &
\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_13_31_48_vep_5min.pdf} \\
13:47:15 - VEP right eye - 3 minutes- X-pedion wire through echelon-10, wire is just at hub of catheter; catheter remains at basilar tip &
\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_13_47_15_vep_.pdf} \\
\end{tabular}
\caption{Rabbit 8 VEP.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
%\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
%\hspace{0.2cm}
%\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
%\vspace{0.5cm}
\begin{tabular}{m{5cm}m{20cm}}
14:03:52 - VEP, 3 min GND: Nose- X-pedion wire, 100 cm (half-length), through echelon 10. Specifically: wire is 100 cm into the catheter (total length of wire is 200cm; hub of sidearm reaches 100cm from proximal end of wire) &
\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_14_03_52_vep_.pdf} \\
14:20:45 - VEP, 3 min, GND: Nose -X-pedion wire, hub of sidearm reaches 47.3 cm from proximal end of wire (calculated so that wire is 10 cm from catheter tip (assuming 162.7 cm total catheter length: 150cm catheter shaft plus hub material that we measured by hand, plus the length of the sidearm) &
\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_14_20_45_vep_3min.pdf} \\
14:43:08 - VEP, 3, min - lights in room are ON - X-pedion wire, repositioned just beyond tip of Echelon catheter at tip of basilar, confirmed with imaging; ALL ELECTRONICS ON, 4 PERSONNEL MOVING AND TALKING IN ROOM &
\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_14_43_08_vep_.pdf} \\
14:46:54 - VEP, 3, min - lights in room are OFF - X-pedion wire, repositioned just beyond tip of Echelon catheter at tip of basilar, confirmed with imaging; ALL ELECTRONICS ON, 4 PERSONNEL MOVING AND TALKING IN ROOM &
\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_14_46_54_vep_.pdf} \\
15:05:50 - VEP, 3 min - ELECTRONICS OFF (unchanged position X-pedion wire, repositioned just beyond tip of Echelon catheter at tip of basilar,) &
\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_15_05_50_vep_.pdf}
\end{tabular}
\caption{Rabbit 8 VEP (continued).}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
%\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
%\hspace{0.2cm}
%\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
%\vspace{0.5cm}
\begin{tabular}{m{5cm}m{20cm}}
SSVEP, 12 Hz, Baseline Brain Recordings - no catheter in the rabbit - endo not hooked up &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_10_36_32_ssvep_.pdf} \\
11:58:44 - SSVEP 12 Hz, GND: Nose - Left Vert - angled glidecath @ osteum of left vert; recording from Ag/AgCl; GND: Nose &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_11_58_44_ssvep_.pdf} \\
SSVEP 12 Hz, X-pedion wire through echelon-10, basilar tip (via left vert); wire projects slightly beyond the catheter (documented on imaging) &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_13_00_49_ssvep_.pdf} \\
13:23:31 - SSVEP 12 Hz, GND: Nose -echelon-10, basilar tip (via left vert), Ag/AgCl electrode &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_13_23_31_ssvep_.pdf} \\
13:52:55 - SSVEP right eye 10 Hz, GND: Nose- X-pedion wire through echelon-10, wire is just at hub of catheter; catheter remains at basilar tip &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_13_52_55_ssvep_12hz.pdf} \\
14:07:37 - SSVEP, 12 Hz, GND: Nose- X-pedion wire, 100 cm (half-length), through echelon 10. Specifically: wire is 100 cm into the catheter (total length of wire is 200cm; hub of sidearm reaches 100cm from proximal end of wire) &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_14_07_37_ssvep_12hz.pdf} \\
%14:26:57 - SSVEP 12 Hz, GND: Nose -X-pedion wire, hub of sidearm reaches 47.3 cm from proximal end of wire (calculated so that wire is 10 cm from catheter tip (assuming 162.7 cm total catheter length: 150cm catheter shaft plus hub material that we measured by hand, plus the length of the sidearm) &
%14:50:43 - SSVEP - 12 Hz, GND: Nose  - lights in room are OFF - X-pedion wire, repositioned just beyond tip of Echelon catheter at tip of basilar, confirmed with imaging; ALL ELECTRONICS ON, 4 PERSONNEL MOVING AND TALKING IN ROOM &
15:12:45 - SSVEP, 12 Hz - ELECTRONICS OFF (unchanged position X-pedion wire, repositioned just beyond tip of Echelon catheter at tip of basilar,) &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_15_12_45_ssvep_12.pdf} \\
15:50:45 - SSVEP, 12 Hz - Xpedion-10 still at basilar tip,  echelon-10 pulled back to C2 level (test intended to look at effect of having more exposed wire) &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_15_50_45_ssvep_12.pdf}
\end{tabular}
\caption{Rabbit 8 SSVEP 12 Hz.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
%\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
%\hspace{0.2cm}
%\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
%\vspace{0.5cm}
\begin{tabular}{m{5cm}m{20cm}}
SSVEP, 40.8333 Hz, Baseline Brain Recordings - no catheter in the rabbit - endo not hooked up &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_10_26_41_ssvep_.pdf} \\
12:03:18 - SSVEP 40 Hz, GND: Nose - Left Vert - angled glidecath @ osteum of left vert; recording from Ag/AgCl; GND: Nose &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_12_03_18_ssvep_.pdf} \\
12:59:49 - SSVEP 40 Hz, GND: Nose -X-pedion wire through echelon-10, basilar tip (via left vert); wire projects slightly beyond the catheter (documented on imaging) &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_12_59_49_ssvep_.pdf} \\
13:24:22 - SSVEP 40 Hz, GND: Nose -echelon-10, basilar tip (via left vert), Ag/AgCl electrode &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_13_24_22_ssvep_.pdf} \\
13:52:00 - SSVEP right eye 40 Hz, GND: Nose- X-pedion wire through echelon-10, wire is just at hub of catheter; catheter remains at basilar tip &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_13_52_00_ssvep_40hz.pdf} \\
14:08:34 - SSVEP, 42 Hz, GND: Nose- X-pedion wire, 100 cm (half-length), through echelon 10. Specifically: wire is 100 cm into the catheter (total length of wire is 200cm; hub of sidearm reaches 100cm from proximal end of wire) &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_14_08_34_ssvep_40.pdf} \\
%14:25:50 - SSVEP 40 Hz, GND: Nose -X-pedion wire, hub of sidearm reaches 47.3 cm from proximal end of wire (calculated so that wire is 10 cm from catheter tip (assuming 162.7 cm total catheter length: 150cm catheter shaft plus hub material that we measured by hand, plus the length of the sidearm) &
%14:52:20 - SSVEP, 40 Hz, GND: Nose - lights in room are OFF - X-pedion wire, repositioned just beyond tip of Echelon catheter at tip of basilar, confirmed with imaging; ALL ELECTRONICS ON, 4 PERSONNEL MOVING AND TALKING IN ROOM &
15:11:55 - SSVEP, 40 Hz - ELECTRONICS OFF (unchanged position X-pedion wire, repositioned just beyond tip of Echelon catheter at tip of basilar,) &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_15_11_55_ssvep_40.pdf} \\
15:51:40 - SSVEP, 40 Hz - Xpedion-10 still at basilar tip,  echelon-10 pulled back to C2 level (test intended to look at effect of having more exposed wire) &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_15_51_40_ssvep_40.pdf} \\
\end{tabular}
\caption{Rabbit 8 SSVEP 40 Hz.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
%\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
%\hspace{0.2cm}
%\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
%\vspace{0.5cm}
\begin{tabular}{m{5cm}m{20cm}}
16:14:30 - SSVEP, 40 Hz - Xpedion wire, just beyond echelon-10 catheter, both located at C2 level &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_16_14_30_ssvep_40.pdf} \\
16:38:01 - SSVEP, 40 Hz - Terumo 4Fr, Right cervical common carotid artery near C2 level, recording from Ag/AgCl &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_16_38_01_ssvep_40.pdf} \\
16:59:49 - SSVEP, 40Hz - DEAD ANIMAL CONTROLS - endo is Ag/AgCl Terumo 4 Fr, Right cervical common carotid artery near C2 level (same position as previous), recording from Ag/AgCl &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_16_59_49_ssvep_40.pdf}
\end{tabular}
\caption{Rabbit 8 SSVEP 40 Hz (continued).}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
%\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
%\hspace{0.2cm}
%\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
%\vspace{0.5cm}
\begin{tabular}{m{5cm}m{20cm}}
SSVEP 51 Hz, X-pedion wire through echelon-10, basilar tip (via left vert); wire projects slightly beyond the catheter (documented on imaging) &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_13_01_58_ssvep_.pdf} \\
13:25:11 - SSVEP 51 Hz, GND: Nose -echelon-10, basilar tip (via left vert), Ag/AgCl electrode &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_13_25_11_ssvep_.pdf} \\
13:51:09 - SSVEP right eye 51 Hz, GND: Nose- X-pedion wire through echelon-10, wire is just at hub of catheter; catheter remains at basilar tip &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_13_51_09_ssvep_.pdf} \\
14:09:23 - SSVEP, 51 Hz, GND: Nose- X-pedion wire, 100 cm (half-length), through echelon 10. Specifically: wire is 100 cm into the catheter (total length of wire is 200cm; hub of sidearm reaches 100cm from proximal end of wire) &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_14_09_23_ssvep_.pdf} \\
14:24:53 - SSVEP, 50 Hz, GND: Nose -X-pedion wire, hub of sidearm reaches 47.3 cm from proximal end of wire (calculated so that wire is 10 cm from catheter tip (assuming 162.7 cm total catheter length: 150cm catheter shaft plus hub material that we measured by hand, plus the length of the sidearm) &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_14_24_53_ssvep_50.pdf} \\
%14:53:22 - SSVEP, 51 Hz, GND: Nose - lights in room are OFF - X-pedion wire, repositioned just beyond tip of Echelon catheter at tip of basilar, confirmed with imaging; ALL ELECTRONICS ON, 4 PERSONNEL MOVING AND TALKING IN ROOM &
15:11:00 - SSVEP, 51 Hz - ELECTRONICS OFF (unchanged position X-pedion wire, repositioned just beyond tip of Echelon catheter at tip of basilar,) &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_15_11_00_ssvep_50.pdf} \\
15:52:32 - SSVEP, 50 Hz - Xpedion-10 still at basilar tip,  echelon-10 pulled back to C2 level (test intended to look at effect of having more exposed wire) &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_15_52_32_ssvep_50.pdf} \\
\end{tabular}
\caption{Rabbit 8 SSVEP 50 Hz.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{m{5cm}m{20cm}}
16:13:39 - SSVEP, 50 Hz - Xpedion wire, just beyond echelon-10 catheter, both located at C2 level &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_16_13_39_ssvep_50.pdf} \\
16:15:20 - SSVEP, 10 Hz - Xpedion wire, just beyond echelon-10 catheter, both located at C2 level &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_16_15_20_ssvep_10.pdf} \\
16:37:09 - SSVEP, 10 Hz - Terumo 4Fr, Right cervical common carotid artery near C2 level, recording from Ag/AgCl &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_16_37_09_ssvep_10.pdf} \\
16:38:52 - SSVEP, 50 Hz - Terumo 4Fr, Right cervical common carotid artery near C2 level, recording from Ag/AgCl &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_16_38_52_ssvep_50.pdf} \\
16:58:54 - SSVEP, 50 Hz - DEAD ANIMAL CONTROLS - endo is Ag/AgCl Terumo 4 Fr, Right cervical common carotid artery near C2 level (same position as previous), recording from Ag/AgCl &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_16_58_54_ssvep_50.pdf} \\
17:00:39 - SSVEP, 10 Hz - DEAD ANIMAL CONTROLS - endo is Ag/AgCl Terumo 4 Fr, Right cervical common carotid artery near C2 level (same position as previous), recording from Ag/AgCl &
\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_17_00_39_ssvep_10.pdf} 
\end{tabular}
\caption{Rabbit 8 SSVEP 50 Hz (continued).}
\end{center}
\end{figure}

\end{document}

### 2014-08-07 analysis/figures/mid_basilar.tex
Adding a bunch of layouts

--- 2014-08-07 analysis/figures/figures_other.tex
@@
 \usepackage{hyperref}
-\usepackage{array}
 
@@
 \begin{document}
-%\begin{minipage}{6in}
-%\centering
-%\raisebox{-0.5\height}{\includegraphics[height=0.75in]{brain.pdf}}
-%\hspace*{.2in}
-%\raisebox{-0.5\height}{\includegraphics[height=0.3in]{brain.pdf}}
-%\end{minipage}
 
@@
 \begin{center}
-\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
-\hspace{0.2cm}
-\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
-\vspace{0.5cm}
-\begin{tabular}{m{5cm}m{20cm}}
-VEP, Distal Basilar Artery, recording from guidewire against a Ag/AgCl reference &
-\includegraphics[scale=0.250]{../vep/matlab_data/_Fri_11_04_2014_15_25_33_vep_.pdf} \\
-VEP, Distal Basilar Artery, recording from guidewire &
-\includegraphics[scale=0.250]{../vep/matlab_data/_Fri_11_04_2014_15_33_56_vep_.pdf} \\
-VEP Dead Control &
-\includegraphics[scale=0.250]{../vep/matlab_data/_Fri_11_04_2014_17_00_46_vep_.pdf} \\
-\end{tabular}
-\caption{Rabbit 6 VEP.}
+\includegraphics[scale=0.3]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__aligned_full.png}
+\caption{Rabbit 10 mid-basilar aligned VEP data.}
 \end{center}
@@
 \begin{center}
-\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
-\hspace{0.2cm}
-\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
-\vspace{0.5cm}
-\begin{tabular}{m{5cm}m{20cm}}
-%SSVEP 40 Hz, no signal on anything &
-%\includegraphics[scale=0.250]{../ssvep/matlab_data/_Fri_11_04_2014_15_27_09_ssvep_.pdf} \\
-SSVEP 40 Hz, distal basilar artery, recording from guidewire &
-\includegraphics[scale=0.250]{../ssvep/matlab_data/_Fri_11_04_2014_15_35_24_ssvep_.pdf} \\
-SSVEP 12 Hz, distal basilar artery, recording from guidewire &
-\includegraphics[scale=0.250]{../ssvep/matlab_data/_Fri_11_04_2014_15_42_09_ssvep_.pdf} \\
-SSVEP 12 Hz Dead Control &
-\includegraphics[scale=0.250]{../ssvep/matlab_data/_Fri_11_04_2014_17_02_31_ssvep_.pdf} \\
-SSVEP 40 Hz Dead Control &
-\includegraphics[scale=0.250]{../ssvep/matlab_data/_Fri_11_04_2014_17_03_23_ssvep_.pdf} \\
-\end{tabular}
-\caption{Rabbit 6 SSVEP.}
+\includegraphics[scale=0.3]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep__aligned_full.png}
+\caption{Rabbit 9 mid-basilar aligned VEP data.}
 \end{center}
@@
 
-\begin{figure}[H]
-\begin{center}
-\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
-\hspace{0.2cm}
-\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
-\vspace{0.5cm}
-\begin{tabular}{m{5cm}m{20cm}}
-VEP, angled glide catheter (ag/agcl) in abdominal descending aorta &
-\includegraphics[scale=0.250]{../vep/matlab_data/_Tue_15_04_2014_15_45_35_vep_.pdf} \\
-SSVEP 40 Hz, angled glide catheter (ag/agcl) in abdominal descending aorta &
-\includegraphics[scale=0.250]{../ssvep/matlab_data/_Tue_15_04_2014_15_48_37_ssvep_40_.pdf} \\
-SSVEP 12 Hz, angled glide catheter (ag/agcl) in abdominal descending aorta &
-\includegraphics[scale=0.250]{../ssvep/matlab_data/_Tue_15_04_2014_15_49_46_ssvep_12.pdf}
-\end{tabular}
-\caption{Rabbit 7.}
-\end{center}
-\end{figure}
-
-\begin{figure}[H]
-\begin{center}
-%\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
-%\hspace{0.2cm}
-%\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
-%\vspace{0.5cm}
-\begin{tabular}{m{5cm}m{20cm}}
-VEP, Baseline Brain Recordings - no catheter in the rabbit - endo not hooked up &
-\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_10_24_11_vep_.pdf} \\
-VEP right eye, X-pedion wire through echelon-10, basilar tip (via left vert); wire projects slightly beyond the catheter (documented on imaging) &
-\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_12_55_56_vep_.pdf} \\
-12:55:56 - VEP right eye, 3 minutes, GND: nose -X-pedion wire through echelon-10, basilar tip (via left vert); wire projects slightly beyond the catheter (documented on imaging) &
-\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_12_55_56_vep_.pdf} \\
-13:13:22 - VEP  right eye - 3 min -echelon-10, basilar tip (via left vert), Ag/AgCl electrode &
-\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_13_13_22_vep_.pdf} \\
-13:31:48 - VEP right eye - 5 min -echelon-10, basilar tip (via left vert), Ag/AgCl electrode &
-\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_13_31_48_vep_5min.pdf} \\
-13:47:15 - VEP right eye - 3 minutes- X-pedion wire through echelon-10, wire is just at hub of catheter; catheter remains at basilar tip &
-\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_13_47_15_vep_.pdf} \\
-\end{tabular}
-\caption{Rabbit 8 VEP.}
-\end{center}
-\end{figure}
-
-\begin{figure}[H]
-\begin{center}
-%\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
-%\hspace{0.2cm}
-%\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
-%\vspace{0.5cm}
-\begin{tabular}{m{5cm}m{20cm}}
-14:03:52 - VEP, 3 min GND: Nose- X-pedion wire, 100 cm (half-length), through echelon 10.
-Specifically: wire is 100 cm into the catheter (total length of wire is 200cm; hub of sidearm reaches 100cm from proximal end of wire) &
-\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_14_03_52_vep_.pdf} \\
-14:20:45 - VEP, 3 min, GND: Nose -X-pedion wire, hub of sidearm reaches 47.3 cm from proximal end of wire (calculated so that wire is 10 cm from catheter tip (assuming 162.7 cm total catheter length: 150cm catheter shaft plus hub material that we measured by hand, plus the length of the sidearm) &
-\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_14_20_45_vep_3min.pdf} \\
-14:43:08 - VEP, 3, min - lights in room are ON - X-pedion wire, repositioned just beyond tip of Echelon catheter at tip of basilar, confirmed with imaging; ALL ELECTRONICS ON, 4 PERSONNEL MOVING AND TALKING IN ROOM &
-\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_14_43_08_vep_.pdf} \\
-14:46:54 - VEP, 3, min - lights in room are OFF - X-pedion wire, repositioned just beyond tip of Echelon catheter at tip of basilar, confirmed with imaging; ALL ELECTRONICS ON, 4 PERSONNEL MOVING AND TALKING IN ROOM &
-\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_14_46_54_vep_.pdf} \\
-15:05:50 - VEP, 3 min - ELECTRONICS OFF (unchanged position X-pedion wire, repositioned just beyond tip of Echelon catheter at tip of basilar,) &
-\includegraphics[scale=0.150]{../vep/matlab_data/_Thu_24_04_2014_15_05_50_vep_.pdf}
-\end{tabular}
-\caption{Rabbit 8 VEP (continued).}
-\end{center}
-\end{figure}
-
-\begin{figure}[H]
-\begin{center}
-%\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
-%\hspace{0.2cm}
-%\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
-%\vspace{0.5cm}
-\begin{tabular}{m{5cm}m{20cm}}
-SSVEP, 12 Hz, Baseline Brain Recordings - no catheter in the rabbit - endo not hooked up &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_10_36_32_ssvep_.pdf} \\
-11:58:44 - SSVEP 12 Hz, GND: Nose - Left Vert - angled glidecath @ osteum of left vert; recording from Ag/AgCl; GND: Nose &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_11_58_44_ssvep_.pdf} \\
-SSVEP 12 Hz, X-pedion wire through echelon-10, basilar tip (via left vert); wire projects slightly beyond the catheter (documented on imaging) &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_13_00_49_ssvep_.pdf} \\
-13:23:31 - SSVEP 12 Hz, GND: Nose -echelon-10, basilar tip (via left vert), Ag/AgCl electrode &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_13_23_31_ssvep_.pdf} \\
-13:52:55 - SSVEP right eye 10 Hz, GND: Nose- X-pedion wire through echelon-10, wire is just at hub of catheter; catheter remains at basilar tip &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_13_52_55_ssvep_12hz.pdf} \\
-14:07:37 - SSVEP, 12 Hz, GND: Nose- X-pedion wire, 100 cm (half-length), through echelon 10.
-Specifically: wire is 100 cm into the catheter (total length of wire is 200cm; hub of sidearm reaches 100cm from proximal end of wire) &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_14_07_37_ssvep_12hz.pdf} \\
-%14:26:57 - SSVEP 12 Hz, GND: Nose -X-pedion wire, hub of sidearm reaches 47.3 cm from proximal end of wire (calculated so that wire is 10 cm from catheter tip (assuming 162.7 cm total catheter length: 150cm catheter shaft plus hub material that we measured by hand, plus the length of the sidearm) &
-%14:50:43 - SSVEP - 12 Hz, GND: Nose  - lights in room are OFF - X-pedion wire, repositioned just beyond tip of Echelon catheter at tip of basilar, confirmed with imaging; ALL ELECTRONICS ON, 4 PERSONNEL MOVING AND TALKING IN ROOM &
-15:12:45 - SSVEP, 12 Hz - ELECTRONICS OFF (unchanged position X-pedion wire, repositioned just beyond tip of Echelon catheter at tip of basilar,) &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_15_12_45_ssvep_12.pdf} \\
-15:50:45 - SSVEP, 12 Hz - Xpedion-10 still at basilar tip,  echelon-10 pulled back to C2 level (test intended to look at effect of having more exposed wire) &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_15_50_45_ssvep_12.pdf}
-\end{tabular}
-\caption{Rabbit 8 SSVEP 12 Hz.}
-\end{center}
-\end{figure}
-
-\begin{figure}[H]
-\begin{center}
-%\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
-%\hspace{0.2cm}
-%\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
-%\vspace{0.5cm}
-\begin{tabular}{m{5cm}m{20cm}}
-SSVEP, 40.8333 Hz, Baseline Brain Recordings - no catheter in the rabbit - endo not hooked up &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_10_26_41_ssvep_.pdf} \\
-12:03:18 - SSVEP 40 Hz, GND: Nose - Left Vert - angled glidecath @ osteum of left vert; recording from Ag/AgCl; GND: Nose &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_12_03_18_ssvep_.pdf} \\
-12:59:49 - SSVEP 40 Hz, GND: Nose -X-pedion wire through echelon-10, basilar tip (via left vert); wire projects slightly beyond the catheter (documented on imaging) &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_12_59_49_ssvep_.pdf} \\
-13:24:22 - SSVEP 40 Hz, GND: Nose -echelon-10, basilar tip (via left vert), Ag/AgCl electrode &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_13_24_22_ssvep_.pdf} \\
-13:52:00 - SSVEP right eye 40 Hz, GND: Nose- X-pedion wire through echelon-10, wire is just at hub of catheter; catheter remains at basilar tip &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_13_52_00_ssvep_40hz.pdf} \\
-14:08:34 - SSVEP, 42 Hz, GND: Nose- X-pedion wire, 100 cm (half-length), through echelon 10.
-Specifically: wire is 100 cm into the catheter (total length of wire is 200cm; hub of sidearm reaches 100cm from proximal end of wire) &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_14_08_34_ssvep_40.pdf} \\
-%14:25:50 - SSVEP 40 Hz, GND: Nose -X-pedion wire, hub of sidearm reaches 47.3 cm from proximal end of wire (calculated so that wire is 10 cm from catheter tip (assuming 162.7 cm total catheter length: 150cm catheter shaft plus hub material that we measured by hand, plus the length of the sidearm) &
-%14:52:20 - SSVEP, 40 Hz, GND: Nose - lights in room are OFF - X-pedion wire, repositioned just beyond tip of Echelon catheter at tip of basilar, confirmed with imaging; ALL ELECTRONICS ON, 4 PERSONNEL MOVING AND TALKING IN ROOM &
-15:11:55 - SSVEP, 40 Hz - ELECTRONICS OFF (unchanged position X-pedion wire, repositioned just beyond tip of Echelon catheter at tip of basilar,) &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_15_11_55_ssvep_40.pdf} \\
-15:51:40 - SSVEP, 40 Hz - Xpedion-10 still at basilar tip,  echelon-10 pulled back to C2 level (test intended to look at effect of having more exposed wire) &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_15_51_40_ssvep_40.pdf} \\
-\end{tabular}
-\caption{Rabbit 8 SSVEP 40 Hz.}
-\end{center}
-\end{figure}
-
-\begin{figure}[H]
-\begin{center}
-%\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
-%\hspace{0.2cm}
-%\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
-%\vspace{0.5cm}
-\begin{tabular}{m{5cm}m{20cm}}
-16:14:30 - SSVEP, 40 Hz - Xpedion wire, just beyond echelon-10 catheter, both located at C2 level &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_16_14_30_ssvep_40.pdf} \\
-16:38:01 - SSVEP, 40 Hz - Terumo 4Fr, Right cervical common carotid artery near C2 level, recording from Ag/AgCl &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_16_38_01_ssvep_40.pdf} \\
-16:59:49 - SSVEP, 40Hz - DEAD ANIMAL CONTROLS - endo is Ag/AgCl Terumo 4 Fr, Right cervical common carotid artery near C2 level (same position as previous), recording from Ag/AgCl &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_16_59_49_ssvep_40.pdf}
-\end{tabular}
-\caption{Rabbit 8 SSVEP 40 Hz (continued).}
-\end{center}
-\end{figure}
-
-\begin{figure}[H]
-\begin{center}
-%\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
-%\hspace{0.2cm}
-%\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
-%\vspace{0.5cm}
-\begin{tabular}{m{5cm}m{20cm}}
-SSVEP 51 Hz, X-pedion wire through echelon-10, basilar tip (via left vert); wire projects slightly beyond the catheter (documented on imaging) &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_13_01_58_ssvep_.pdf} \\
-13:25:11 - SSVEP 51 Hz, GND: Nose -echelon-10, basilar tip (via left vert), Ag/AgCl electrode &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_13_25_11_ssvep_.pdf} \\
-13:51:09 - SSVEP right eye 51 Hz, GND: Nose- X-pedion wire through echelon-10, wire is just at hub of catheter; catheter remains at basilar tip &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_13_51_09_ssvep_.pdf} \\
-14:09:23 - SSVEP, 51 Hz, GND: Nose- X-pedion wire, 100 cm (half-length), through echelon 10.
-Specifically: wire is 100 cm into the catheter (total length of wire is 200cm; hub of sidearm reaches 100cm from proximal end of wire) &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_14_09_23_ssvep_.pdf} \\
-14:24:53 - SSVEP, 50 Hz, GND: Nose -X-pedion wire, hub of sidearm reaches 47.3 cm from proximal end of wire (calculated so that wire is 10 cm from catheter tip (assuming 162.7 cm total catheter length: 150cm catheter shaft plus hub material that we measured by hand, plus the length of the sidearm) &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_14_24_53_ssvep_50.pdf} \\
-%14:53:22 - SSVEP, 51 Hz, GND: Nose - lights in room are OFF - X-pedion wire, repositioned just beyond tip of Echelon catheter at tip of basilar, confirmed with imaging; ALL ELECTRONICS ON, 4 PERSONNEL MOVING AND TALKING IN ROOM &
-15:11:00 - SSVEP, 51 Hz - ELECTRONICS OFF (unchanged position X-pedion wire, repositioned just beyond tip of Echelon catheter at tip of basilar,) &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_15_11_00_ssvep_50.pdf} \\
-15:52:32 - SSVEP, 50 Hz - Xpedion-10 still at basilar tip,  echelon-10 pulled back to C2 level (test intended to look at effect of having more exposed wire) &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_15_52_32_ssvep_50.pdf} \\
-\end{tabular}
-\caption{Rabbit 8 SSVEP 50 Hz.}
-\end{center}
-\end{figure}
-
-\begin{figure}[H]
-\begin{center}
-\begin{tabular}{m{5cm}m{20cm}}
-16:13:39 - SSVEP, 50 Hz - Xpedion wire, just beyond echelon-10 catheter, both located at C2 level &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_16_13_39_ssvep_50.pdf} \\
-16:15:20 - SSVEP, 10 Hz - Xpedion wire, just beyond echelon-10 catheter, both located at C2 level &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_16_15_20_ssvep_10.pdf} \\
-16:37:09 - SSVEP, 10 Hz - Terumo 4Fr, Right cervical common carotid artery near C2 level, recording from Ag/AgCl &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_16_37_09_ssvep_10.pdf} \\
-16:38:52 - SSVEP, 50 Hz - Terumo 4Fr, Right cervical common carotid artery near C2 level, recording from Ag/AgCl &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_16_38_52_ssvep_50.pdf} \\
-16:58:54 - SSVEP, 50 Hz - DEAD ANIMAL CONTROLS - endo is Ag/AgCl Terumo 4 Fr, Right cervical common carotid artery near C2 level (same position as previous), recording from Ag/AgCl &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_16_58_54_ssvep_50.pdf} \\
-17:00:39 - SSVEP, 10 Hz - DEAD ANIMAL CONTROLS - endo is Ag/AgCl Terumo 4 Fr, Right cervical common carotid artery near C2 level (same position as previous), recording from Ag/AgCl &
-\includegraphics[scale=0.150]{../ssvep/matlab_data/_Thu_24_04_2014_17_00_39_ssvep_10.pdf} 
-\end{tabular}
-\caption{Rabbit 8 SSVEP 50 Hz (continued).}
-\end{center}
-\end{figure}
+The maximum voltage in the first 0.4 seconds is aligned.
 

### 2014-08-07 analysis/figures/qrs.tex
Adding a bunch of layouts

\documentclass[]{article}

\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}

\pagestyle{plain}

\begin{document}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
& Endo & Bottom Precordial & Top Precordial \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_2_qrs-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_9_qrs-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_10_qrs-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep_2_qrs-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep_9_qrs-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep_10_qrs-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep_2_qrs-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep_9_qrs-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep_10_qrs-crop.pdf} \\
\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep_2_qrs-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep_9_qrs-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep_10_qrs-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep_2_qrs-crop.pdf} & 
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep_9_qrs-crop.pdf} & 
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep_10_qrs-crop.pdf}
\end{tabular}
\caption{Rabbit 9 hand-selected intervals that show qrs complex.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
& Endo & Bottom Precordial & Top Precordial \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_2_qrs-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_9_qrs-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_10_qrs-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_2_qrs-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_9_qrs-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_10_qrs-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_2_qrs-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_9_qrs-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_10_qrs-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_2_qrs-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_9_qrs-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_10_qrs-crop.pdf}
\end{tabular}
\caption{Rabbit 10 hand-selected intervals that show qrs complex.}
\end{center}
\end{figure}

\end{document}

### 2014-08-07 analysis/figures/qrs_shape.tex
Adding a bunch of layouts

\documentclass[]{article}

\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}

\pagestyle{plain}

\begin{document}
%\begin{minipage}{6in}
%\centering
%\raisebox{-0.5\height}{\includegraphics[height=0.75in]{brain.pdf}}
%\hspace*{.2in}
%\raisebox{-0.5\height}{\includegraphics[height=0.3in]{brain.pdf}}
%\end{minipage}

\begin{figure}[H]
\begin{center}
\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
\hspace{0.2cm}
\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend2.pdf}} \\
\vspace{0.5cm}
\begin{tabular}{cccc}
& VEP & SSVEP 40 Hz & SSAEP 86 Hz \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_11_57_42_vep__qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40_qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86_qrs-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40_qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86_qrs-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_15_54_54_vep__qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40_qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86_qrs-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_47_47_vep__qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40_qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86_qrs-crop.pdf}
\end{tabular}
\caption{Rabbit 10 experimental responses. Cardiac activity is multiplied by 0.125.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
VEP & SSVEP 40 Hz & SSAEP 86 Hz \\
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40_qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86_qrs-crop.pdf}
\end{tabular}
\caption{Rabbit 10 live control. Cardiac activity is multiplied by 0.125.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
& VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_17_10_vep__qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40_qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86_qrs-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_04_18_vep__qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_02_01_ssvep_40_qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_11_09_ssaep_86_qrs-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_44_57_vep__qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_41_46_ssvep_40_qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_53_21_ssaep_86_qrs-crop.pdf} \\
%\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_13_50_vep__qrs-crop.pdf} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_11_25_ssvep_40_qrs-crop.pdf} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_20_29_ssaep_86_qrs-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_50_43_vep__qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_48_24_ssvep_50_qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_57_52_ssaep_86_qrs-crop.pdf}
\end{tabular}
\caption{Rabbit 9 experimental responses. Cardiac activity is multiplied by 0.125.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_25_22_vep__qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40_qrs-crop.pdf} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86_qrs-crop.pdf}
\end{tabular}
\caption{Rabbit 9 live control. Cardiac activity is multiplied by 0.125.}
\end{center}
\end{figure}

\end{document}

### 2014-08-07 analysis/figures/qrs_shape_all.tex
Adding a bunch of layouts

\documentclass[]{article}

\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}

\pagestyle{plain}

% scale:
% 0.150
% 0.126
% 0.126

% 0.150
% 0.126
% 0.126
\begin{document}
%\begin{minipage}{6in}
%\centering
%\raisebox{-0.5\height}{\includegraphics[height=0.75in]{brain.png}}
%\hspace*{.2in}
%\raisebox{-0.5\height}{\includegraphics[height=0.3in]{brain.png}}
%\end{minipage}

\begin{figure}[H]
\begin{center}
\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
\hspace{0.2cm}
\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend2.pdf}} \\
\vspace{0.5cm}
\begin{tabular}{cccc}
& VEP & SSVEP 40 Hz & SSAEP 86 Hz \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_11_57_42_vep__qrs_all-crop.png} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40_qrs_all-crop.png} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86_qrs_all-crop.png} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__qrs_all-crop.png} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40_qrs_all-crop.png} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86_qrs_all-crop.png} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_15_54_54_vep__qrs_all-crop.png} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40_qrs_all-crop.png} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86_qrs_all-crop.png} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_47_47_vep__qrs_all-crop.png} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40_qrs_all-crop.png} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86_qrs_all-crop.png}
\end{tabular}
\caption{Rabbit 10 experimental responses. Cardiac activity is multiplied by 0.125.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
VEP & SSVEP 40 Hz & SSAEP 86 Hz \\
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_qrs_all-crop.png} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40_qrs_all-crop.png} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86_qrs_all-crop.png}
\end{tabular}
\caption{Rabbit 10 live control. Cardiac activity is multiplied by 0.125.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
& VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_17_10_vep__qrs_all-crop.png} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40_qrs_all-crop.png} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86_qrs_all-crop.png} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_04_18_vep__qrs_all-crop.png} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_02_01_ssvep_40_qrs_all-crop.png} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_11_09_ssaep_86_qrs_all-crop.png} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_44_57_vep__qrs_all-crop.png} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_41_46_ssvep_40_qrs_all-crop.png} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_14_53_21_ssaep_86_qrs_all-crop.png} \\
%\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_13_50_vep__qrs_all-crop.png} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_11_25_ssvep_40_qrs_all-crop.png} &
%\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_20_29_ssaep_86_qrs_all-crop.png} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_50_43_vep__qrs_all-crop.png} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_48_24_ssvep_50_qrs_all-crop.png} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_15_57_52_ssaep_86_qrs_all-crop.png}
\end{tabular}
\caption{Rabbit 9 experimental responses. Cardiac activity is multiplied by 0.125.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
VEP On Response & SSVEP 40 Hz & SSAEP 86 Hz \\
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_25_22_vep__qrs_all-crop.png} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40_qrs_all-crop.png} &
\includegraphics[scale=0.150]{../qrs/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86_qrs_all-crop.png}
\end{tabular}
\caption{Rabbit 9 live control. Cardiac activity is multiplied by 0.125.}
\end{center}
\end{figure}

\end{document}

### 2014-08-07 analysis/figures/std.tex
Adding a bunch of layouts

\documentclass[]{article}

\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}

\pagestyle{plain}

\begin{document}

\begin{figure}[H]
\begin{center}
\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
\hspace{0.2cm}
\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
\vspace{0.5cm}
\begin{tabular}{ccc}
%& VEP On Response & VEP Off Response \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__std-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__std_late-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__std-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__std_late-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep__std-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep__std_late-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep__std-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep__std_late-crop.pdf} \\
\end{tabular}
\caption{Rabbit 10 experimental VEP.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
%VEP On Response & VEP Off Response \\
%\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_std-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_std_late-crop.pdf} \\
\end{tabular}
\caption{Rabbit 10 live control VEP.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\raisebox{-0.5\height}{\includegraphics[scale=0.8]{brain.pdf}}
\hspace{0.2cm}
\raisebox{-0.5\height}{\includegraphics[scale=1.0]{../config/legend.pdf}} \\
\vspace{0.5cm}
\begin{tabular}{ccc}
%& VEP On Response & VEP Off Response \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep__std-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep__std_late-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep__std-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep__std_late-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep__std-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep__std_late-crop.pdf} \\
%\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
%\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep__std-crop.pdf} &
%\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep__std_late-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep__std-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep__std_late-crop.pdf}
\end{tabular}
\caption{Rabbit 9 experimental responses.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
%VEP On Response & VEP Off Response \\
%\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep_-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep__std-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep__std_late-crop.pdf}
\end{tabular}
\caption{Rabbit 9 live control.}
\end{center}
\end{figure}

\end{document}

### 2014-08-07 analysis/figures/unprocessed.tex
Adding a bunch of layouts

\documentclass[]{article}

\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}

\pagestyle{plain}

\begin{document}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
& Endo & Bottom Precordial & Top Precordial \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_2_unprocessed-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_9_unprocessed-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_10_unprocessed-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep_2_unprocessed-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep_9_unprocessed-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep_10_unprocessed-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep_2_unprocessed-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep_9_unprocessed-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep_10_unprocessed-crop.pdf} \\
\rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep_2_unprocessed-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep_9_unprocessed-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep_10_unprocessed-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep_2_unprocessed-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep_9_unprocessed-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep_10_unprocessed-crop.pdf}
\end{tabular}
\caption{Rabbit 9 raw signals. VB Junction and Cervical Vertebral Dens have some rapid shifts in voltage.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
& Endo & Bottom Precordial & Top Precordial \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_2_unprocessed-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_9_unprocessed-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_10_unprocessed-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_2_unprocessed-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_9_unprocessed-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_10_unprocessed-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_2_unprocessed-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_9_unprocessed-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_10_unprocessed-crop.pdf} \\
\rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_2_unprocessed-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_9_unprocessed-crop.pdf} &
\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_10_unprocessed-crop.pdf}
\end{tabular}
\caption{Rabbit 10 raw signals. VB Junction and Cervical Vertebral Dens have some rapid shifts in voltage.}
\end{center}
\end{figure}

\end{document}

### 2014-08-07 analysis/figures/vep_snr.tex
Adding a bunch of layouts

--- 2014-07-27 analysis/figures/vep_all.tex
@@
 \rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
-\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__all.png} \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__fano.pdf} \\
 \rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
-\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__all.png} \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__fano.pdf} \\
 \rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
-\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep__all.png} \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep__fano.pdf} \\
 \rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
-\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep__all.png}
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep__fano.pdf}
 \end{tabular}
@@
 %VEP On Response & VEP Off Response \\
-\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_all.png}
+\includegraphics[scale=0.161]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_fano.pdf}
 \end{tabular}
@@
 \rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
-\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep__all.png} \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep__fano.pdf} \\
 \rotatebox{90}{\hspace{0.5cm}Mid-Basilar} &
-\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep__all.png} \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_04_18_vep__fano.pdf} \\
 \rotatebox{90}{\hspace{0.5cm}Vertebro-basilar} &
-\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep__all.png} \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_14_44_57_vep__fano.pdf} \\
 \rotatebox{90}{\hspace{0cm}Cervical Vertebral Dens} &
-\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep__all.png} \\
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_13_50_vep__fano.pdf} \\
 \rotatebox{90}{\hspace{0.5cm}Basilar Tip} &
-\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep__all.png}
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_15_50_43_vep__fano.pdf}
 \end{tabular}
@@
 %VEP On Response & VEP Off Response \\
-\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep__all.png}
+\includegraphics[scale=0.161]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep__fano.pdf}
 \end{tabular}

### 2014-08-07 analysis/qrs/qrs_figure.m
Qrs code

@@ -41,12 +41,17 @@ margins = 100; % extra space for labels
 position = [0 0 (width + 2 * margins) (height + 2 * margins)];
 
 % Open invisible screen for figure
-f1 = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'on'); axes('units', 'pixel', 'position', [margins margins width height]);
-f2 = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'on'); axes('units', 'pixel', 'position', [margins margins width height]);
-f3 = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'on'); axes('units', 'pixel', 'position', [margins margins width height]);
-f4 = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'on'); axes('units', 'pixel', 'position', [margins margins width height]);
-f5 = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'on'); axes('units', 'pixel', 'position', [margins margins width height]);
+f_start = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]);
+f_end = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]);
+f1 = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]);
+f2 = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]);
+f3 = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]);
+f4 = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]);
[…]

### 2014-08-07 analysis/qrs/qrs_removal.m

@@ -1,6 +1,6 @@
-function [] = qrs_removal(chData, cardiacData, name, color, f1, f2, f3, f4, f5)
+function [ chData ] = qrs_removal(chData, cardiacData, name, color, f1, f2, f3, f4, f5)
 
-    font_size = 20;
+    font_size = 10;
 
     % chData must be at least high pass filtered (to get rid of drifting
     % cardiacData probably has to be unfiltered to work
@@ -116,7 +116,7 @@ function [] = qrs_removal(chData, cardiacData, name, color, f1, f2, f3, f4, f5)
         %figure(f4);
         set(0, 'CurrentFigure', f4);
         hold on;
-        time_axis = ((1:numel(qrs)) - max_before) / 9600;
+        time_axis = ((1:numel(qrs)) - max_before) / 9600 * 1000;
         plot(time_axis, qrs, 'color', color, 'linewidth', 2);
         confMean = bootci(100, @nanmean, padded);
         %plot(time_axis, confMean(1,:),'--','color',color,'linewidth',2);
@@ -125,16 +125,18 @@ function [] = qrs_removal(chData, cardiacData, name, color, f1, f2, f3, f4, f5)
         py = [confMean(1,:), fliplr(confMean(2,:))];
         patch(px,py,1,'FaceColor',color,'EdgeColor','none');
     
-        xlabel('Time (seconds)');
+        xlabel('Time (ms)');
         ylabel('$\mu V$', 'interpreter', 'LaTeX');
-        set(findall(f4,'type','text'),'fontSize',font_size,'fontWeight','normal', 'color', [0 0 0]); % Mostly to get rid of the italics from latex
         %title(sprintf('QRS Complex Shape: %d trials', size(padded, 1)));
         %xlim([0 numel(qrs) / 9600]);
-        xlim([-median_before, median_after] / 9600);
+        xlim([-median_before, median_after] / 9600 * 1000);
         %ylim([-120 120]);
-        ylim([-150 150]);
+        %ylim([-150 150]);
+        ylim([-200 200]);
         set(findall(f4,'type','text'),'fontSize',font_size,'fontWeight','normal', 'color', [0,0,0]);
-        title(sprintf('QRS Complex Shape: %d trials', size(padded, 1)), 'Color', 'White');
+        %set(gca, 'YTick', [-150, -100, -50, 0, 50, 100, 150]);
+        set(gca,'YTick',[-200,-100,0,100,200]);
[…]

### 2014-08-07 analysis/qrs/qrs_plot.m
qrs_plot migrated into qrs_removal

@@ -1,165 +1,0 @@
-function [] = qrs_removal(chData, cardiacData, name, color, f1, f2, f3, f4, f5)
-
-    font_size = 20;
-
-    % chData must be at least high pass filtered (to get rid of drifting
-    % cardiacData probably has to be unfiltered to work
-    assert(all(size(chData) == size(cardiacData)));
-    %tic
-    [~,locs]=findpeaks(cardiacData,'minpeakdistance', round(0.18 * 9600));
-    % TODO: could take cardiac spikes as argument, rather than cardiacData
-    % findpeaks takes a long time
-    %toc
-    %locs = locs(2:(end-1));
-
-    if (nargin >= 5 && f1 ~= 0)
-        %% Plot Cardiac Data with Detected Peaks
-        %figure(f1);
-        set(0, 'CurrentFigure', f1);
-        hold on;
-        plot((1:numel(cardiacData)) / 9600, cardiacData, 'color', color);
-        yl = ylim;
-        for i = 1:numel(locs)
-            plot(locs(i) * [1 1] / 9600, yl, 'color', 'black');
-        end
-        plot((1:numel(cardiacData)) / 9600, cardiacData, 'color', color);
-        ylim(yl);
-        xlabel('Time (seconds)');
-        ylabel('$\mu V$', 'interpreter', 'LaTeX');
-        set(findall(f1,'type','text'),'fontSize',font_size,'fontWeight','normal', 'color', [0 0 0]); % Mostly to get rid of the italics from latex
-        title('Detected R Wave');
-        xlim([0 numel(cardiacData) / 9600]);
-    end
-
-    if (nargin >= 6 && f2 ~= 0)
-        %% Compute Distance between R Peaks
-        dt = diff(locs);
-    
-        %% Plot Distance between r peaks
-        %figure(f2);
-        set(0, 'CurrentFigure', f2);
-        scatter(1:numel(dt), dt / 9600 * 1000, 36, color);
-        xlabel('Interval Number');
-        ylabel('Interval Length (ms)');
-        title('Time Between R Peaks');
-        xlim([0 numel(dt)]);
-        ylim([150 300]);
-    
-        %[a,b] = min(dt);
-        %%figure(f1);
-        %set(0, 'CurrentFigure', f1);
-        %xlim(locs(b) / 9600 + [-0.4 0.4]);
-        %locs(b + (-1:1)) / 9600 * 1000
-    end
-
[…]

### 2014-08-07 analysis/utilities/qrs_removal_old.m
Older version of qrs_removal (didn't center the r peak properly)

@@ -1,0 +1,112 @@
+function [ filtered_data ] = qrs_removal(chData, cardiacData, name, color, channel)
+
+    if nargin >= 3 && nargin < 4
+        color = 'blue';
+    end
+
+    % chData must be at least high pass filtered (to get rid of drifting
+    % cardiacData probably has to be unfiltered to work
+    assert(all(size(chData) == size(cardiacData)));
+    %tic
+    [pks,locs]=findpeaks(cardiacData,'minpeakdistance', round(0.18 * 9600));
+    %toc
+    %locs = locs(2:(end-1));
+
+    if nargin >= 3
+        f1 = figure;
+        hold on;
+        plot((1:numel(cardiacData)) / 9600, cardiacData, 'color', color);
+        yl = ylim;
+        for i = 1:numel(locs)
+            plot(locs(i) * [1 1] / 9600, yl, 'color', 'black');
+        end
+        plot((1:numel(cardiacData)) / 9600, cardiacData, 'color', color);
+        ylim(yl);
+        xlabel('Time (seconds)');
+        ylabel('$\mu V$', 'interpreter', 'LaTeX');
+        title('Detected R Wave');
+        xlim([0 numel(cardiacData) / 9600]);
+
+        saveas(f1, ['matlab_data/' name '_' int2str(channel) '_r_peak.fig']);
+    end
+
+    dt = diff(locs);
+
+    if nargin >= 3
+        f2 = figure;
+        scatter(1:numel(dt), dt / 9600 * 1000, 36, color);
+        xlabel('Interval Number');
+        ylabel('Interval Length (ms)');
+        title('Time Between R Peaks');
+        xlim([0 numel(dt)]);
+        ylim([200 270]);
+
+        %[a,b] = min(dt);
+        %figure(f1);
+        %xlim(locs(b) / 9600 + [-0.4 0.4]);
+        %locs(b + (-1:1)) / 9600 * 1000
+
+        saveas(f1, ['matlab_data/' name '_' int2str(channel) '_dt.fig']);
+        save2pdf(['matlab_data/' name '_' int2str(channel) '_dt.pdf'], f2, 1200);
+    end
+
+    %% Gather and align the channel data
+    standard = round(median(dt));
+    padded = nan(numel(locs) + 1, max(dt));
+    % first period
+    padded(1, standard + ((-locs(1)+2):0)) = chData(1:(locs(1)-1));
[…]

### 2014-08-07 analysis/utilities/assert_match.m
Minor helper functions

@@ -16,7 +16,7 @@ for i = 1:length(S)
   S_minute = S{i}(22:23);
   assert(strcmp(S{i}(24:26), '%3A'))
   S_second = S{i}(27:28);
-  assert(strcmp(S{i}(29:35), '_ssvep_'))
+  %assert(strcmp(S{i}(29:35), '_ssvep_')) % TODO - make this check experiment type
   S_extra = S{i}(34:end);
 
   % Hard coded parsing of experiment log

### 2014-08-07 analysis/utilities/get_frequency.m

@@ -12,9 +12,10 @@ if ~isempty(strfind(comment{1}(9:35), '12'))
 end
 if ~isempty(strfind(comment{1}(9:35), '40'))
     nominal_frequency = [nominal_frequency 40];
-    frequency = [frequency 40.8333];
+    %frequency = [frequency 40.8333];
+    frequency = [frequency (40 + 5 / 6)];
 end
-if ~isempty(strfind(comment{1}(9:35), '42'))
+if ~isempty(strfind(comment{1}(9:45), '42'))
     nominal_frequency = [nominal_frequency 42];
     frequency = [frequency 42]; % TODO: check if this is exact
 end
@@ -25,6 +26,10 @@ end
 if ~isempty(strfind(comment{1}(9:35), '51'))
     nominal_frequency = [nominal_frequency 51];
     frequency = [frequency 51]; % TODO: check if this is exact
+end
+if ~isempty(strfind(comment{1}(9:35), '86'))
+    nominal_frequency = [nominal_frequency 86];
+    frequency = [frequency 86]; % TODO: check if this is exact
 end
 
 assert(numel(nominal_frequency) == 1);

### 2014-08-07 analysis/vep/check_qrs.m
Old code for figuring out qrs issues.

@@ -23,7 +23,8 @@
 %///////////////////////////////////////////////
 clear;
 
-rabbit_ID = '9rabbit_may_6_2014';
+%rabbit_ID = '9rabbit_may_6_2014';
+rabbit_ID = '10rabbit_may_15_2014';
 fs = 9600;
 
 publication_quality = 3;                                                   % generate the high quality figures with confidence intervals. this is much slower than having it set to zero
@@ -80,7 +81,8 @@ CM = [hex2dec('e9'), hex2dec('00'), hex2dec('3a');
 
 CM = CM/256;
 
-channelToPlot = [2,3,5,7,8];
+%channelToPlot = [2,3,5,7,8];
+channelToPlot = [2,9,10];
 
 
 
@@ -165,8 +167,8 @@ nf120 = design(n120);
 nf180 = design(n180);
 
 %for i=12
-for i = [2 10 11 12 13 3] % rabbit 9
-%for i = [4 10 12 15 5] % rabbit 10
+%for i = [2 10 11 12 13 3] % rabbit 9
+for i = [4 10 12 15 5] % rabbit 10
 
 
     close all;
@@ -207,13 +209,18 @@ for i = [2 10 11 12 13 3] % rabbit 9
     dataColumnDigDecimated = dataColumnDig(1:decimate_factor:end);                      %throw out intermediate samples to keep them aligned to the decimated channel data
     cleanDigitalInDecimated = (dataColumnDigDecimated>0);                                        %make sure the digital In takes on binary values: take any negative excursions to 0
 
-
-    fgh = figure('Color',[1 1 1],'units','pixels','outerposition',[0 0 1366 768]);
-    hold on;
+    name = S{i};
+    name(name == '.') = '_';
+    while any(name == '%')
+        index = find(name == '%', 1);
+        name = [name(1:(index-1)) '_' name((index+3):end)];
+    end
 
     plotline = [];
-    %for ii=1:length(channelToPlot)
-    for ii=1
+    for ii=1:length(channelToPlot)
+    %for ii=1
+        fgh = figure('Color',[1 1 1],'units','pixels','outerposition',[0 0 1366 768]);
+        hold on;
     
         fprintf(['ii: ' int2str(ii) '\n']);
 
@@ -227,32 +234,66 @@ for i = [2 10 11 12 13 3] % rabbit 9
         %chData = filtfilt(hpf.sosMatrix, hpf.ScaleValues,chData);
 
         %chData = filtfilt(lpf.sosMatrix, lpf.ScaleValues,chData);
+
[…]

### 2014-08-07 analysis/vep/publish_vep_all.m
Old changes to depreciated code

@@ -88,8 +88,10 @@ time_axis = (-preEventPlot_samples:postEventPlot_samples)/fs*1000;         %prep
 
 %fgh = figure('Color',[1 1 1],'units','normalized',...                      %get the figure handle, and draw the figure with white background and full screen
 %                                                'outerposition',[0 0 1 1]);
-fgh = figure('Color',[1 1 1],'units','pixels',...                      %get the figure handle, and draw the figure with white background and full screen
-                                                'outerposition',[0 0 1366 768]);
+%fgh = figure('Color',[1 1 1],'units','pixels',...                      %get the figure handle, and draw the figure with white background and full screen
+%                                                'outerposition',[0 0 1366 768]);
+fgh = figure('Color',[1 1 1],'units','pixels','outerposition',[0 0 1366 768],'visible','off');
+
 %CM = colorcube(size(data,1)+1);                                            % choose the colormap for the plots
 hold on;
 
@@ -133,6 +135,7 @@ for ii=1:length(channelToPlot)                                                  
     if use_lpf
         chData = filtfilt(lpf.sosMatrix, lpf.ScaleValues,chData);
     end    
+    chData = qrs_removal(chData, data{find(strcmp(data, 'Bottom Precordial')), 2});
     toc
     %fig = gcf;
     %figure;
@@ -194,6 +197,15 @@ for ii=1:length(channelToPlot)                                                  
             = detrend(chData((event_index_LED_ON(jj)-preEventPlot_samples):...
                             (event_index_LED_ON(jj)+postEventPlot_samples)));
     end
+    %if (strcmp(S{i}, '_Thu_15.05.2014_14%3A13%3A26_vep_'))
+    %    %valid = ~any(abs(chData_all_single_trial_collection_ON) > thresh, 2);
+    %    askdnadknad
+    %    valid = ~any(chData_all_single_trial_collection_ON > 92, 2);
+    %    chData_all_single_trial_collection_ON = chData_all_single_trial_collection_ON(valid, :);
+    %    fprintf('size: %d %d\n\n', size(chData_all_single_trial_collection_ON, 1), size(chData_all_single_trial_collection_ON, 2));
+    %end
+
+
[…]

### 2014-08-07 analysis/vep/publish_vep_off_v2.m

@@ -88,8 +88,9 @@ time_axis = (-preEventPlot_samples:postEventPlot_samples)/fs*1000;         %prep
 
 %fgh = figure('Color',[1 1 1],'units','normalized',...                      %get the figure handle, and draw the figure with white background and full screen
 %                                                'outerposition',[0 0 1 1]);
-fgh = figure('Color',[1 1 1],'units','pixels',...                      %get the figure handle, and draw the figure with white background and full screen
-                                                'outerposition',[0 0 1366 768]);
+%fgh = figure('Color',[1 1 1],'units','pixels',...                      %get the figure handle, and draw the figure with white background and full screen
+%                                                'outerposition',[0 0 1366 768]);
+fgh = figure('Color',[1 1 1],'units','pixels','outerposition',[0 0 1366 768],'visible','off');
 %CM = colorcube(size(data,1)+1);                                            % choose the colormap for the plots
 hold on;
 
@@ -133,6 +134,8 @@ for ii=1:length(channelToPlot)                                                  
     if use_lpf
         chData = filtfilt(lpf.sosMatrix, lpf.ScaleValues,chData);
     end    
+    chData = qrs_removal(chData, data{find(strcmp(data, 'Bottom Precordial')), 2});
+
     toc
     %fig = gcf;
     %figure;
@@ -194,6 +197,32 @@ for ii=1:length(channelToPlot)                                                  
             = detrend(chData((event_index_LED_ON(jj)-preEventPlot_samples):...
                             (event_index_LED_ON(jj)+postEventPlot_samples)));
     end
+    %sorted = sort(max(abs(chData_all_single_trial_collection_ON),[],2));
+    %thresh = sorted(ceil(0.95 * numel(sorted))); % TODO: use selection algorithm, rather than sort
+    %valid = ~any(abs(chData_all_single_trial_collection_ON) > thresh, 2);
+    %chData_all_single_trial_collection_ON = chData_all_single_trial_collection_ON(valid, :);
+    %fprintf('thresh: %f\nsize: %d %d\n\n', thresh, size(chData_all_single_trial_collection_ON, 1), size(chData_all_single_trial_collection_ON, 2));
[…]

### 2014-08-07 analysis/vep/generate_all.m
Script to generate figures

@@ -1,0 +1,13 @@
+% Figure 2
+%plot_all_vep('8rabbit_apr_24_2014', 1, [3]);
+plot_all_vep('9rabbit_may_6_2014', 1, [2]);
+plot_all_vep('10rabbit_may_15_2014', 1, [4 10 12 15 5 16]);
+
+% Figure 2 Control Version
+%plot_all_vep('8rabbit_apr_24_2014', 1, [15]); % this is a dead control
+plot_all_vep('9rabbit_may_6_2014', 1, [3]);
+%plot_all_vep('10rabbit_may_15_2014', 1, [5]);
+
+% Figure 5
+plot_all_vep('10rabbit_may_15_2014', 1, [10], false);
+

### 2014-08-07 analysis/vep/plot_all_vep.m

@@ -17,10 +17,11 @@
 %	
 %	The analysis code assumes a fixed sampling rate of 9600 Hz and digital input channel # of 65 (both designated in arduino_vep.m)
 
-function plot_all_vep(rabbit_ID, publication_quality, trials_list)
+function plot_all_vep(rabbit_ID, publication_quality, trials_list, filter_qrs)
 
 addpath('../config');
 addpath('../utilities');
+addpath('../qrs');
 
 %///////////////////////////////////////////////
 % START BLOCK: Hardcoded variables
@@ -89,22 +90,20 @@ if (nargin < 3)
     trials_list = 1:numel(S);
 end
 
-filters = get_filters(original_sampling_rate_in_Hz, true, true, true, true, true);
+if (nargin < 4)
+    filter_qrs = true;
+end
+
+%filters = get_filters(original_sampling_rate_in_Hz, true, true, true, true, true);
+%filters = get_filters(original_sampling_rate_in_Hz, true, true, false, false, false);
+%filters = get_filters(original_sampling_rate_in_Hz, true, false, true, false, false);
+filters = get_filters(original_sampling_rate_in_Hz, true, false, false, false, false);
 cardiac_filters = get_filters(original_sampling_rate_in_Hz, true, false, false, false, false);
 
 preEventPlot_sec = 0.05;                                                    %time in seconds to extend plot prior to event time (marked as time zero)
 postEventPlot_sec = 0.1;
 
-channelToPlot = [2,3,5,7,8];
-%CM = [hex2dec('e9'), hex2dec('00'), hex2dec('3a'); hex2dec('ff'), hex2dec('ba'),hex2dec('00'); hex2dec('18'),hex2dec('26'),hex2dec('b0'); hex2dec('58'),hex2dec('e0'), hex2dec('00'); hex2dec('00'),hex2dec('00'),hex2dec('00')];
-CM = [hex2dec('e9'), hex2dec('00'), hex2dec('3a');
-      hex2dec('ff'), hex2dec('ba'), hex2dec('00');
-      hex2dec('40'), hex2dec('40'), hex2dec('ff');
-      hex2dec('58'), hex2dec('e0'), hex2dec('00');
-      hex2dec('b0'), hex2dec('00'), hex2dec('b0')];
-
-CM = CM/256;
-
+[ channelToPlot, CM ] = plot_settings();
 
 for i = trials_list
     filename = S{i};
[…]

### 2014-08-07 analysis/vep/publish_vep_v2.m

@@ -1,20 +1,17 @@
-%arduino_vep.m
+% publish_vep
 %
-%This script runs the VEP analysis on a single file represented by 'pathname' and 'filename'
+% This script runs the VEP analysis on a single file represented by 'pathname' and 'filename'
 %
-%Requires:
+% Requires:
 %	pathname - path for the data in easter binary format
 %	filename - file name for the data in easter binary format
 %	data	 - cell array contains channel labels and channel values; does not include the digitalinCh channel
 %		   example: data{4,1} is the label for channel 4.
 %			    data{4,2} is the vector of voltage values (microvolts) for channel 4
-
-%//////////////////////////////////
-% if you want to ask the user to select a single binary data file, uncomment this block
-%run('../utilities/loaddata.m');		%populates the variable names pathname, filename, and data
+%////////////////////////////////// % if you want to ask the user to select a single binary data file, uncomment this block %run('../utilities/loaddata.m');		%populates the variable names pathname, filename, and data
 %//////////////////////////////////
 
-function [] = publish_vep_v2(data, cleanDigitalIn, fs, publication_quality, filters, cardiac_filters, preEventPlot_sec, postEventPlot_sec, comment, name, channelToPlot, CM, OnOff)
+function [] = publish_vep_v2(data, cleanDigitalIn, fs, publication_quality, filters, cardiac_filters, preEventPlot_sec, postEventPlot_sec, comment, name, channelToPlot, CM, OnOff, filter_qrs)
 
 %///// hardcoded values that you should keep unchanged
                                                                            %digital input channel convention is low is LED OFF, high is LED ON; verified for VEP aruino recording code with 5rabbit, 6rabbit, 7rabbit, etc.
@@ -41,8 +38,15 @@ totalEventPlot_samples = preEventPlot_samples + postEventPlot_samples + 1;   % t
 time_axis = (-preEventPlot_samples:postEventPlot_samples) / fs * 1000;       %prepare the time axis for the plots based on samples to plot
 
 
-fgh = figure('Color',[1 1 1],'units','pixels','outerposition',[0 0 1366 768],'visible','off');
-hold on;
[…]

### 2014-08-07 analysis/vep/publish_fano.m
Old code added

@@ -1,0 +1,474 @@
+%arduino_vep.m
+%
+%This script runs the VEP analysis on a single file represented by 'pathname' and 'filename'
+%
+%Requires:
+%	pathname - path for the data in easter binary format
+%	filename - file name for the data in easter binary format
+%	data	 - cell array contains channel labels and channel values; does not include the digitalinCh channel
+%		   example: data{4,1} is the label for channel 4.
+%			    data{4,2} is the vector of voltage values (microvolts) for channel 4
+
+%//////////////////////////////////
+% if you want to ask the user to select a single binary data file, uncomment this block
+%run('../utilities/loaddata.m');		%populates the variable names pathname, filename, and data
+%//////////////////////////////////
+
+
+%///// hardcoded values that you should keep unchanged
+
+fs = original_sampling_rate_in_Hz;
+                                                                           %digital input channel convention is low is LED OFF, high is LED ON; verified for VEP aruino recording code with 5rabbit, 6rabbit, 7rabbit, etc.
+LED_ON_edge = 1;                                                           %LED turns on with rising edge of digital in channel (diff = 1)
+LED_OFF_edge = -1;                                                         %LED turns off with falling edge of digital in channel (diff = -1)
+
+
+%////////////////////////////////////////////////////////////////////
+%///// hardcoded analysis options: VEP onset and offset
+%////////////////////////////////////////////////////////////////////
+
+% OPTION 1 /////// Choose how much time you would like to plot pre- and post- event onset                                                                            
+%preEventPlot_sec = 0.1;                                                    %time in seconds to extend plot prior to event time (marked as time zero)
+%postEventPlot_sec = 1/0.8942;                                               %time in seconds to extend plot following event time (marked as time zero). 0.9 Hz was frequency of light onset in VEP controlled by Arduino 
+preEventPlot_sec = 0.05;                                                    %time in seconds to extend plot prior to event time (marked as time zero)
+postEventPlot_sec = 0.5;
+
+
+% OPTION 2 /////// Choose which filters you want to use in the analysis                                                                            
[…]

### 2014-08-07 analysis/ssavep/artifact.m
All ssavep code

@@ -1,0 +1,288 @@
+function [] = artifact(rabbit_ID, ssavep, index1, index2)
+
+addpath('../config')
+addpath('../utilities')
+
+maxNumberOfChannels = 10;                                                  %# of consecutive analog input channels, starting with channel 1, to extract from the project easter binary files
+                                                                           %(which contain 64 analog channels and the digital in channel (channel 65)
+
+digitalInCh = 65;                                                          %designate the digital input channel, which is used to record
+                                                                           %the LED state to align EEG data with onset or offset to generate VEP graphs 
+
+original_sampling_rate_in_Hz = 9600;                                       % data is acquired with the g.Tech g.HiAmp at 9600 Hz. this is fixed for convenience. at higher rates, the 
+                                                                           % digital input channel does not work reliably.
+
+pathname = ['../../../../data/easter/' rabbit_ID '/neuro/binary_data/' ssavep '/'];%path for the data in easter binary format
+%pathname_comments = ['../../../../data/easter/' rabbit_ID '/neuro/vep.txt'];%file containing comments written on the experiment day to use as labels for the figure titles
+pathname_comments = ['../../../../data/easter/' rabbit_ID '/neuro/neuro_experiment_log.txt'];%file containing comments written on the experiment day to use as labels for the figure titles
+
+pathname_matdata = ['../../../../data/easter/' rabbit_ID '/neuro/matlab_data/' ssavep '/'];
+
+[ channelNames, gtechGND, earth ] = rabbit_information(rabbit_ID);
+
+[ S, allData ] = get_information(pathname, pathname_comments, upper(ssavep));
+
+publication_quality = 2;
+
[…]

### 2014-08-07 analysis/ssavep/generate_all.m

@@ -1,0 +1,16 @@
+%% For paper figure 2
+plot_all_ssavep('ssvep', '10rabbit_may_15_2014', 2, [11]);
+plot_all_ssavep('ssaep', '10rabbit_may_15_2014', 2, [15]);
+plot_all_ssavep('ssvep', '9rabbit_may_6_2014', 2, [5]);
+plot_all_ssavep('ssaep', '9rabbit_may_6_2014', 2, [8]);
+
+%% For paper figure 2 live control version
+plot_all_ssavep('ssvep', '9rabbit_may_6_2014', 2, [8]);
+plot_all_ssavep('ssaep', '9rabbit_may_6_2014', 2, [11]);
+plot_all_ssavep('ssvep', '10rabbit_may_15_2014', 2, [14]);
+plot_all_ssavep('ssaep', '10rabbit_may_15_2014', 2, [12]);
+
+%% For paper figure 3
+plot_all_ssavep('ssvep', '10rabbit_may_15_2014', 2, [2 11 23 32 35 14 38]);
+plot_all_ssavep('ssaep', '10rabbit_may_15_2014', 2, [3 15 24 33 36 12 40]);
+

### 2014-08-07 analysis/ssavep/generate_all_old.m

@@ -1,0 +1,77 @@
+%% For paper figure 2
+plot_all_ssavep('ssvep', '8rabbit_apr_24_2014', 2, [5]); 
+plot_all_ssavep('ssvep', '10rabbit_may_15_2014', 2, [11]);
+plot_all_ssavep('ssaep', '10rabbit_may_15_2014', 2, [15]);
+plot_all_ssavep('ssvep', '9rabbit_may_6_2014', 2, [5]);
+plot_all_ssavep('ssaep', '9rabbit_may_6_2014', 2, [8]);
+
+%ssavep_different('8rabbit_apr_24_2014', 'ssaep', 18, 'ssvep', 24);
+ssavep_different('8rabbit_apr_24_2014', 'ssaep', 5, 'ssvep', 5);
+
+%% For paper figure 2 live control version
+plot_all_ssavep('ssvep', '8rabbit_apr_24_2014', 2, [36]); 
+plot_all_ssavep('ssvep', '9rabbit_may_6_2014', 2, [8]);
+plot_all_ssavep('ssaep', '9rabbit_may_6_2014', 2, [11]);
+plot_all_ssavep('ssvep', '10rabbit_may_15_2014', 2, [14]);
+plot_all_ssavep('ssaep', '10rabbit_may_15_2014', 2, [12]);
+
+ssavep_different('8rabbit_apr_24_2014', 'ssaep', 26, 'ssvep', 36);
+
+%% For paper figure 3
+plot_all_ssavep('ssvep', '10rabbit_may_15_2014', 2, [2 11 23 32 35 14 38]);
+plot_all_ssavep('ssaep', '10rabbit_may_15_2014', 2, [3 15 24 33 36 12 40]);
+
+% Resting state (resting state - dead control) for SSAEP 86 Hz
+artifact('10rabbit_may_15_2014', 'ssaep', 15, 40); % basilar tip
+artifact('10rabbit_may_15_2014', 'ssaep', 24, 40); % mid-basilar
+artifact('10rabbit_may_15_2014', 'ssaep', 33, 40); % vb junction
+artifact('10rabbit_may_15_2014', 'ssaep', 36, 40); % basilar tip
+artifact('10rabbit_may_15_2014', 'ssaep', 12, 40); % live control
+artifact('10rabbit_may_15_2014', 'ssaep', 40, 40); % dead control
+
+% Resting state (resting state - dead control) for SSVEP 40 Hz
[…]

### 2014-08-07 analysis/ssavep/plot_all_ssavep.m

@@ -1,61 +1,25 @@
-%plot_all_vep.m
+% plot_all_ssavep.m
 %
-%Authors: M. Ebrahimi, L. Srinivasan / nspl.org
+% Description: This script processes the paper figures for the SSAEP
+%              experiments or the SSVEP experiments.
 %
-%Date: 4/17/14
+% Arguments:
+%   ssavep: either 'ssaep' or 'ssvep' (string) - selects which experiment to plot
+%   rabbit_ID: string ('9rabbit_may_6_2014' or '10rabbit_may_15_2014')
+%   publication_quality: either 1 or 2, 1 is supposed to plot confidence
+%                        intervals (not functional as of 8/6/14), 2 does not
+%                        plot confidence intervals (is functional)
+%                        [optional - defaults to 2]
+%   trials_list: list of indices to plot
+%                [optional - defaults to all experiments]
 %
-%Description: This script produces one VEP graph for each VEP data set recorded in experiment given by rabbit_ID
-%
-%Requires:  rabbit_ID - tag for the experiment, set in the hardcoded variables block below.
-%
-%Output:  One figure for each VEP session, with two panels, one for the 'on' response, one for the 'off' response.
-%
-%Notes:  The g.tech digital input, channel 65, goes high for LED ON with 5rabbit and 6rabbit, but low for LED ON with 7rabbit
-%	 This is accounted for in arduino_vep.m, which checks the pathname for '7rabbit' and chooses the appropriate convention.
-%	 In subsequent rabbits after 7rabbit, the arduino code in /code/easter/ should have been changed to reflect the intuitive
-%	 convention used in 5rabbit and 6rabbit of channel 65 going high for LED ON.
-%	
-%	The analysis code assumes a fixed sampling rate of 9600 Hz and digital input channel # of 65 (both designated in arduino_vep.m)
+% Output: Figures are saved as PDFs in matlab_data.
 
 function plot_all_ssavep(ssavep, rabbit_ID, publication_quality, trials_list)
-%clear;
-%close all;
-addpath('../config')
-addpath('../utilities')
 
-%% Parameters
-
-% rabbit_ID choices - which rabbit to plot
-% rabbit_ID = '1rabbit_dec_10_2012';
-% rabbit_ID = '2rabbit_jan_23_2013';
[…]

### 2014-08-07 analysis/ssavep/publish_ssavep.m

@@ -1,407 +1,143 @@
-function [] = publish_ssavep(data, fs, windlengthSeconds, noverlapPercent, cleanDigitalIn, channelToPlot, filters, CM, experiment, filename, comment, publication_quality, name)
+function [] = publish_ssavep(data, fs, windlengthSeconds, noverlapPercent, cleanDigitalIn, channelToPlot, filters, CM, experiment, filename, comment, publication_quality, name, cardiac_filters)
 
 % sampling rate
-%fs = 9600;
-%windlengthSeconds = 2;
 windlength = windlengthSeconds * fs;
-%noverlapPercent = 0.25;%windlength * 0.25; % number overlap percent
 noverlap = windlength * noverlapPercent; % number overlap (timesteps)
 
-threshold = 4; % Threshold for 60 Hz harmonics
+threshold_60 = 3; % Threshold for 60 Hz harmonics
+threshold_harmonics = 3; % Threshold to be considered a harmonic
 
 time_axis = (0:numel(cleanDigitalIn)-1)*1.0/fs;
-%figure;plot(time_axis,dataColumnDig);
 
 t1 = diff(cleanDigitalIn); % -1: experiment turns off, 0: no change, 1: experiment turns on
-t2 = find(t1 == 1); % first time when led turns on (experiment starts)
-t3 = find(t1 == -1); % last time when led turns off (experiment ends)
+t2 = find(t1 == 1);        % times when digital in turns on (experiment starts)
+t3 = find(t1 == -1);       % times when digital in turns off (experiment ends)
 
-if isempty(t3)
+if isempty(t3) % digital in never turns off
+    % experiment ends when data stops
     t3 = length(cleanDigitalIn);
 end
 
-cutLengthB = t2; %fs * cutSecondsBegining;
-cutLengthE = t3; %fs * cutSecondsEnd;
+cutLengthB = t2; % time steps to cut from beginning
+cutLengthE = t3; % time steps to cut from end
 
-assert(numel(cutLengthB) == 1);
-assert(numel(cutLengthE) == 1);
+assert(numel(cutLengthB) == 1); % bad data with multiple experiment starts
+assert(numel(cutLengthE) == 1); % bad data with multiple experiment ends
 
[…]

### 2014-08-07 analysis/ssavep/ssavep_different.m

@@ -1,0 +1,297 @@
+function [] = ssavep_different(rabbit_ID, ssavep1, index1, ssavep2, index2)
+
+addpath('../config')
+addpath('../utilities')
+
+maxNumberOfChannels = 10;                                                  %# of consecutive analog input channels, starting with channel 1, to extract from the project easter binary files
+                                                                           %(which contain 64 analog channels and the digital in channel (channel 65)
+
+digitalInCh = 65;                                                          %designate the digital input channel, which is used to record
+                                                                           %the LED state to align EEG data with onset or offset to generate VEP graphs 
+
+original_sampling_rate_in_Hz = 9600;                                       % data is acquired with the g.Tech g.HiAmp at 9600 Hz. this is fixed for convenience. at higher rates, the 
+                                                                           % digital input channel does not work reliably.
+
+pathname1 = ['../../../../data/easter/' rabbit_ID '/neuro/binary_data/' ssavep1 '/'];%path for the data in easter binary format
+pathname2 = ['../../../../data/easter/' rabbit_ID '/neuro/binary_data/' ssavep2 '/'];%path for the data in easter binary format
+%pathname_comments = ['../../../../data/easter/' rabbit_ID '/neuro/vep.txt'];%file containing comments written on the experiment day to use as labels for the figure titles
+pathname_comments = ['../../../../data/easter/' rabbit_ID '/neuro/neuro_experiment_log.txt'];%file containing comments written on the experiment day to use as labels for the figure titles
+
+pathname_matdata = ['../../../../data/easter/' rabbit_ID '/neuro/matlab_data/' ssavep1 '/'];
[…]

### 2014-08-07 analysis/qrs/qrs_removal.m
Make the qrs start and end in the standard locations.
Used to be TPQRS (R at 0.5).
Now PQRST (R at 0.63).

@@ -53,7 +53,7 @@ function [ chData ] = qrs_removal(chData, cardiacData, name, color, f1, f2, f3, 
     end
 
     %% Compute interval (include first, exclude last)
-    cutoff = [1; locs(1:(end-1)) + round(diff(locs) / 2); numel(chData) + 1];
+    cutoff = [1; locs(1:(end-1)) + round(0.63 * diff(locs)); numel(chData) + 1];
 
     if (nargin >= 7 && f3 ~= 0)
         %% Plot Distance between midpoints

### 2014-08-07 analysis/config/make_legend.m
Old code to create legend

@@ -1,0 +1,35 @@
+function [ f ] = make_legend()
+  f = figure;
+  hold on;
+
+  CM = [hex2dec('e9'), hex2dec('00'), hex2dec('3a');
+        hex2dec('ff'), hex2dec('ba'), hex2dec('00');
+        hex2dec('40'), hex2dec('40'), hex2dec('ff');
+        hex2dec('58'), hex2dec('e0'), hex2dec('00');
+        hex2dec('b0'), hex2dec('00'), hex2dec('b0');
+        hex2dec('00'), hex2dec('00'), hex2dec('00')];
+  CM = CM/256;
+
+  channelToPlot = [2,3,5,7,8];
+  channelToPlot = [2,3,5,7,8,9];
+  channelNames_VEP = {'Disconnected','Endo','Mid head','Disconnected','Right Eye','Right Leg','Back Head','Left Eye','Bottom Precordial','Top Precordial'};
+
+
+  legends = [];
+  for i = 1:numel(channelToPlot)
+    legends = [legends plot(0, 0, 'Color', CM(i, :), 'linewidth', 3)];
+  end
+legends
+  legend(legends, channelNames_VEP{channelToPlot})
+  %legend(channelNames_VEP{channelToPlot})
+
+  axis off;
+  set(legends, 'visible', 'off');
+  set(gca, 'visible', 'off');
+
+  %save2pdf('legend.pdf', f, 1200);
+  save2pdf('legend2.pdf', f, 1200);
+
+
+end
+

### 2014-08-07 analysis/figures/paper_figures.tex
Shifted cleaned/contaminated labels to left

@@
 Time     & 11:57:42    & 14:13:26    & 15:54:54    & 16:47:47    & 12:15:47     & 17:22:22 \\
+% Time     & 11:57:42    & 14:13:26    & 15:54:54    & 16:47:47    & 12:15:47     & 17:22:22 \\ % TODO: time relative to anesthesia? relative to surgery
 \hline
@@
 \begin{center}
-\begin{tabular}{c|cc|c}
+\begin{tabular}{cc|cc}
 \raisebox{-0.5\height}{\multirow{3}{*}{
@@
 }} &
-Raw Trace & VEP-Aligned \\
+& Raw Trace & VEP-Aligned \\
 \hline
 &
+\raisebox{-0.5\height}{\rotatebox{90}{Contaminated}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.32]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__start-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__cardiac_labelled-crop.pdf}} &
-\rotatebox{180}{\raisebox{-0.5\height}{\rotatebox{90}{Contaminated}}} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__cardiac_labelled-crop.pdf}} \\
 &
+\raisebox{-0.5\height}{\rotatebox{90}{Cleaned}} &
 \raisebox{-0.5\height}{\includegraphics[scale=0.32]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__end-crop.pdf}} &
-\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__labelled-crop.pdf}} &
-\rotatebox{180}{\raisebox{-0.5\height}{\rotatebox{90}{Cleaned}}}
+\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__labelled-crop.pdf}} \\
 \end{tabular}

### 2014-08-07 analysis/figures/paper_figures.tex
Difference time

@@
 Time     & 11:57:42    & 14:13:26    & 15:54:54    & 16:47:47    & 12:15:47     & 17:22:22 \\
-% Time     & 11:57:42    & 14:13:26    & 15:54:54    & 16:47:47    & 12:15:47     & 17:22:22 \\ % TODO: time relative to anesthesia? relative to surgery
+Time     & 0:00:00 & 2:15:44 & 3:57:12 & 4:50:05 & 0:18:05 & 5:24:40 \\ % TODO: time relative to anesthesia? relative to surgery
 \hline

### 2014-08-08 analysis/figures/qrs_to_pdf.sh
Code for cropping pdfs and converting svg to pdf (from yesterday)

@@ -1,0 +1,10 @@
+# for cardiac
+inkscape ../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__cardiac_labelled.svg --export-pdf=../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__cardiac_labelled.pdf
+pdfcrop ../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__cardiac_labelled.pdf
+
+inkscape ../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__qrs.svg --export-pdf=../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__qrs.pdf
+pdfcrop ../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__qrs.pdf
+
+pdfcrop ../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__start.pdf
+pdfcrop ../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__end.pdf
+

### 2014-08-08 analysis/figures/ssavep_to_pdf.sh

@@ -1,0 +1,20 @@
+pdfcrop ../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86_labelled.pdf
+pdfcrop ../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86.pdf
+pdfcrop ../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86.pdf
+pdfcrop ../ssavep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86.pdf
+pdfcrop ../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40_labelled.pdf
+pdfcrop ../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40.pdf
+pdfcrop ../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40.pdf
+pdfcrop ../ssavep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40.pdf
+pdfcrop ../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86_labelled.pdf
+pdfcrop ../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86.pdf
+pdfcrop ../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86.pdf
+pdfcrop ../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86.pdf
+pdfcrop ../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86.pdf
+pdfcrop ../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86.pdf
+pdfcrop ../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40_labelled.pdf
+pdfcrop ../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40.pdf
+pdfcrop ../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40.pdf
+pdfcrop ../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40.pdf
[…]

### 2014-08-08 analysis/figures/vep_to_pdf.sh

@@ -1,0 +1,54 @@
+inkscape ../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__labelled.svg --export-pdf=../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__labelled.pdf
+pdfcrop ../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__labelled.pdf
+inkscape ../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_.svg --export-pdf=../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_.pdf
+pdfcrop ../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_.pdf
+
+inkscape ../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_.svg --export-pdf=../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_.pdf
+pdfcrop ../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_.pdf
+inkscape ../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__labelled.svg --export-pdf=../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__labelled.pdf
+pdfcrop ../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__labelled.pdf
+
+inkscape ../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_.svg --export-pdf=../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_.pdf
+pdfcrop ../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_.pdf
+inkscape ../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_.svg --export-pdf=../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_.pdf
+pdfcrop ../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_.pdf
+inkscape ../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_.svg --export-pdf=../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_.pdf
+pdfcrop ../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_.pdf
[…]

### 2014-08-08 analysis/figures/paper_figures.tex
Legend added
Fixex spacing a little bit
Documentation of figures

@@
 \includegraphics[scale=1.0]{surgical_methods.pdf}
-\caption{Surgical approach, anatomy imaging.} % Figure 1
+\caption{Surgical approach, anatomy imaging.}
+\label{fig:surgical}
+% Figure 1
 \end{center}
@@
 \begin{center}
+\includegraphics[]{../config/legend2.pdf} % TODO: vertical center
+\hspace{0.3cm}
 \begin{tabular}{c|cc|cc}
@@
 In addition, the endovascular electrode achieved superior signals compared to the scalp electrodes for the VEP and SSAEP experiments.}
+\label{fig:both}
 % Figure 2
@@
 }
+\label{fig:position}
 % Figure 3
@@
 \end{tabular}
-\caption{Impedence characterization.} % Figure 4
+\caption{Impedance characterization.}
+\label{fig:impedance}
+% Figure 4
 \end{center}
@@
 \end{tabular}
-
-\caption{Cardiac contamination and cleaning. 1076 trials for qrs mean} % Figure 5
+\caption{Cardiac contamination and cleaning. 1076 trials for qrs mean}
+\label{fig:cardiac}
+% Figure 5
 \end{center}
@@
 
+\section*{Figure Information}
+This section is information about which trials where used for the figures and some information about the trials.
+\begin{table}[H]
+\begin{center}
+\begin{tabular}{c|cc|cc}
+& \multicolumn{2}{c|}{Experiment} & \multicolumn{2}{c}{Control} \\
+& Subject 1 & Subject 2 & Subject 1 & Subject 2 \\
+\hline
+\raisebox{-0.5\height}{\rotatebox{90}{VEP On}} &
+../vep/matlab\_data/\_Thu\_15\_05\_2014\_11\_57\_42\_vep\_\_labelled-crop.pdf &
+../vep/matlab\_data/\_Tue\_06\_05\_2014\_11\_17\_10\_vep\_-crop.pdf &
+../vep/matlab\_data/\_Thu\_15\_05\_2014\_12\_15\_47\_vep\_ctr-crop.pdf &
+../vep/matlab\_data/\_Tue\_06\_05\_2014\_11\_25\_22\_vep\_-crop.pdf \\
+\raisebox{-0.5\height}{\rotatebox{90}{VEP Off}} &
+../vep/matlab\_data/\_Thu\_15\_05\_2014\_11\_57\_42\_vep\_\_off\_labelled-crop.pdf &
+../vep/matlab\_data/\_Tue\_06\_05\_2014\_11\_17\_10\_vep\_\_off-crop.pdf &
+../vep/matlab\_data/\_Thu\_15\_05\_2014\_12\_15\_47\_vep\_ctr\_off-crop.pdf &
+../vep/matlab\_data/\_Tue\_06\_05\_2014\_11\_25\_22\_vep\_\_off-crop.pdf \\
+\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
+../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_14\_26\_54\_ssaep\_86\_labelled-crop.pdf &
+../ssavep/matlab\_data/\_Tue\_06\_05\_2014\_11\_37\_22\_ssaep\_86-crop.pdf &
+../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_12\_26\_26\_ssaep\_ctr\_86-crop.pdf &
+../ssavep/matlab\_data/\_Tue\_06\_05\_2014\_11\_42\_15\_ssaep\_86-crop.pdf \\
+\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
+../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_14\_20\_24\_ssvep\_40\_labelled-crop.pdf &
+../ssavep/matlab\_data/\_Tue\_06\_05\_2014\_11\_14\_51\_ssvep\_40-crop.pdf &
+../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_12\_13\_26\_ssvep\_ctr\_40-crop.pdf &
+../ssavep/matlab\_data/\_Tue\_06\_05\_2014\_11\_23\_01\_ssvep\_40-crop.pdf
+\end{tabular}
+\end{center}
+\caption{Figure \ref{fig:both} files used to generate plot.}
+\end{table}
+
+\begin{table}[H]
+\begin{center}
+\begin{tabular}{c|cccc|cc}
+         & \multicolumn{4}{c|}{Experiment}                       & \multicolumn{2}{c}{Control} \\
+         &             &             &             &             & Live         & Dead \\
+\hline
+Location & Basilar Tip & Mid-Basilar & VB Junction & Basilar Tip & Basilar Tip  & Basilar Tip \\
+Time     & 11:57:42    & 14:13:26    & 15:54:54    & 16:47:47    & 12:15:47     & 17:22:22 \\
+Time     & 0:00:00 & 2:15:44 & 3:57:12 & 4:50:05 & 0:18:05 & 5:24:40 \\ % TODO: time relative to anesthesia? relative to surgery
+\hline
+\raisebox{-0.5\height}{\rotatebox{90}{VEP On}} &
+../vep/matlab\_data/\_Thu\_15\_05\_2014\_11\_57\_42\_vep\_\_labelled-crop.pdf &
+../vep/matlab\_data/\_Thu\_15\_05\_2014\_14\_13\_26\_vep\_-crop.pdf &
+../vep/matlab\_data/\_Thu\_15\_05\_2014\_15\_54\_54\_vep\_-crop.pdf &
+../vep/matlab\_data/\_Thu\_15\_05\_2014\_16\_47\_47\_vep\_-crop.pdf &
+../vep/matlab\_data/\_Thu\_15\_05\_2014\_12\_15\_47\_vep\_ctr-crop.pdf &
+../vep/matlab\_data/\_Thu\_15\_05\_2014\_17\_22\_22\_vep\_-crop.pdf \\
+\raisebox{-0.5\height}{\rotatebox{90}{VEP Off}} &
+../vep/matlab\_data/\_Thu\_15\_05\_2014\_11\_57\_42\_vep\_\_off\_labelled-crop.pdf &
+../vep/matlab\_data/\_Thu\_15\_05\_2014\_14\_13\_26\_vep\_\_off-crop.pdf &
+../vep/matlab\_data/\_Thu\_15\_05\_2014\_15\_54\_54\_vep\_\_off-crop.pdf &
+../vep/matlab\_data/\_Thu\_15\_05\_2014\_16\_47\_47\_vep\_\_off-crop.pdf &
+../vep/matlab\_data/\_Thu\_15\_05\_2014\_12\_15\_47\_vep\_ctr\_off-crop.pdf &
+../vep/matlab\_data/\_Thu\_15\_05\_2014\_17\_22\_22\_vep\_\_off-crop.pdf \\
+\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
+../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_12\_31\_02\_ssaep\_86\_labelled-crop.pdf &
+../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_14\_26\_54\_ssaep\_86-crop.pdf &
+../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_16\_12\_19\_ssaep\_86-crop.pdf &
+../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_16\_58\_34\_ssaep\_86-crop.pdf &
+../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_12\_26\_26\_ssaep\_ctr\_86-crop.pdf &
+../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_17\_12\_38\_ssaep\_86-crop.pdf \\
+\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
+../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_12\_08\_22\_ssvep\_40\_labelled-crop.pdf &
+../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_14\_20\_24\_ssvep\_40-crop.pdf &
+../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_16\_02\_44\_ssvep\_40-crop.pdf &
+../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_16\_38\_47\_ssvep\_40-crop.pdf &
+../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_12\_13\_26\_ssvep\_ctr\_40-crop.pdf &
+../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_17\_18\_01\_ssvep\_40-crop.pdf
+\end{tabular}
+\caption{Figure \ref{fig:position} files used to generate plot.}
+\label{fig:position}
+% Figure 3
+\end{center}
+\end{table}
+
+\begin{table}[H]
+\begin{center}
+\begin{tabular}{cc|cc}
+Filename & Index & VEP On & VEP Off \\
+\hline
+\_Tue\_06.05.2014\_11\%3A17\%3A10\_vep\_ & 2 / 13 & 153 & 153 \\
+\_Thu\_15.05.2014\_11\%3A57\%3A42\_vep\_ & 4 / 16 & 205 & 206 \\
+\_Thu\_15.05.2014\_14\%3A13\%3A26\_vep\_ & 10 / 16 & 192 & 191 \\
+\_Thu\_15.05.2014\_15\%3A54\%3A54\_vep\_ & 12 / 16 & 208 & 208 \\
+\_Thu\_15.05.2014\_16\%3A47\%3A47\_vep\_ & 15 / 16 & 208 & 208 \\
+\_Thu\_15.05.2014\_12\%3A15\%3A47\_vep\_ctr & 5 / 16 & 208 & 208 \\
+\_Thu\_15.05.2014\_17\%3A22\%3A22\_vep\_ & 16 / 16 & 208 & 208 \\
+\_Tue\_06.05.2014\_11\%3A25\%3A22\_vep\_ & 3 / 13 & 153 & 153 \\
+\_Thu\_15.05.2014\_14\%3A13\%3A26\_vep\_ & 10 / 16 & 192 & 191
+\end{tabular}
+\end{center}
+\caption{Number of Trials Averaged for VEP (this may slightly smaller than the number of LED on/off, since some segments might have been skipped)}
+\end{table}
 %% VEP 
@@
 %Number of Trials: 191
+
+\begin{table}[H]
+\begin{center}
+\begin{tabular}{cc|cccc}
+&&\multicolumn{2}{c}{Experiment} & \multicolumn{2}{c}{Resting} \\
+Filename & Index & Time Step & Length & Time Step & Length \\
+\hline
+\_Thu\_15.05.2014\_12\%3A08\%3A22\_ssvep\_40      & 11 / 39 & 320640  584434 & 27.4785 & 9600 301440 & 30.4000 \\
+\_Thu\_15.05.2014\_12\%3A31\%3A02\_ssaep\_86      & 15 / 40 & 307603  585728 & 28.9714 & 9600 288403 & 29.0420 \\
+\_Tue\_06.05.2014\_11\%3A14\%3A51\_ssvep\_40      &  5 / 39 & 320045  583839 & 27.4785 & 9600 300845 & 30.3380 \\
+\_Tue\_06.05.2014\_11\%3A37\%3A22\_ssaep\_86      &  8 / 41 &  70740  585728 & 53.6446 & 9600  51540 &  4.3688 \\
+\_Tue\_06.05.2014\_11\%3A23\%3A01\_ssvep\_40      &  8 / 39 & 317488  581282 & 27.4785 & 9600 298288 & 30.0717 \\
+\_Tue\_06.05.2014\_11\%3A42\%3A15\_ssaep\_86      & 11 / 41 &  94848  585856 & 51.1467 & 9600  75648 &  6.8800 \\
+\_Thu\_15.05.2014\_12\%3A13\%3A26\_ssvep\_ctr\_40 & 14 / 39 & 328552  592346 & 27.4785 & 9600 309352 & 31.2242 \\
+\_Thu\_15.05.2014\_12\%3A26\%3A26\_ssaep\_ctr\_86 & 12 / 40 & 305364  585856 & 29.2179 & 9600 286164 & 28.8087 \\
+\_Thu\_15.05.2014\_09\%3A52\%3A53\_ssvep\_40      &  2 / 39 & 328875  592669 & 27.4785 & 9600 309675 & 31.2578 \\
+\_Thu\_15.05.2014\_12\%3A08\%3A22\_ssvep\_40      & 11 / 39 & 320640  584434 & 27.4785 & 9600 301440 & 30.4000 \\
+\_Thu\_15.05.2014\_14\%3A20\%3A24\_ssvep\_40      & 23 / 39 & 371398  587192 & 22.4785 & 9600 304198 & 30.6873 \\
+\_Thu\_15.05.2014\_16\%3A02\%3A44\_ssvep\_40      & 32 / 39 & 609145 1156050 & 56.9693 & 9600 589945 & 60.4526 \\
+\_Thu\_15.05.2014\_16\%3A38\%3A47\_ssvep\_40      & 35 / 39 & 611121 1158026 & 56.9693 & 9600 591921 & 60.6584 \\
+\_Thu\_15.05.2014\_12\%3A13\%3A26\_ssvep\_ctr\_40 & 14 / 39 & 328552  592346 & 27.4785 & 9600 309352 & 31.2242 \\
+\_Thu\_15.05.2014\_17\%3A18\%3A01\_ssvep\_40      & 38 / 39 & 606919 1153824 & 56.9693 & 9600 587719 & 60.2207 \\
+\_Thu\_15.05.2014\_10\%3A04\%3A16\_ssaep\_86      &  3 / 40 & 303843  585856 & 29.3764 & 9600 284643 & 28.6503 \\
+\_Thu\_15.05.2014\_12\%3A31\%3A02\_ssaep\_86      & 15 / 40 & 307603  585728 & 28.9714 & 9600 288403 & 29.0420 \\
+\_Thu\_15.05.2014\_14\%3A26\%3A54\_ssaep\_86      & 24 / 40 & 301020  585728 & 29.6571 & 9600 281820 & 28.3562 \\
+\_Thu\_15.05.2014\_16\%3A12\%3A19\_ssaep\_86      & 33 / 40 & 593190 1161856 & 59.2360 & 9600 573990 & 58.7906 \\
+\_Thu\_15.05.2014\_16\%3A58\%3A34\_ssaep\_86      & 36 / 40 & 595230 1161728 & 59.0102 & 9600 576030 & 59.0031 \\ \_Thu\_15.05.2014\_12\%3A26\%3A26\_ssaep\_ctr\_86 & 12 / 40 & 305364  585856 & 29.2179 & 9600 286164 & 28.8087 \\
+\_Thu\_15.05.2014\_17\%3A12\%3A38\_ssaep\_86      & 40 / 40 & 595109 1161728 & 59.0228 & 9600 575909 & 58.9905
+\end{tabular}
+\end{center}
+\caption{Start and end time step for experiment and resting state durign SSAEP and SSVEP.}
+\end{table}
+%[( 584434 - 320640) / 9600;
+% ( 585728 - 307603) / 9600;
+% ( 583839 - 320045) / 9600;
+% ( 585728 -  70740) / 9600;
+% ( 581282 - 317488) / 9600;
+% ( 585856 -  94848) / 9600;
+% ( 592346 - 328552) / 9600;
+% ( 585856 - 305364) / 9600;
+% ( 592669 - 328875) / 9600;
+% ( 584434 - 320640) / 9600;
+% ( 587192 - 371398) / 9600;
+% (1156050 - 609145) / 9600;
+% (1158026 - 611121) / 9600;
+% ( 592346 - 328552) / 9600;
+% (1153824 - 606919) / 9600;
+% ( 585856 - 303843) / 9600;
+% ( 585728 - 307603) / 9600;
+% ( 585728 - 301020) / 9600;
+% (1161856 - 593190) / 9600;
+% (1161728 - 595230) / 9600;
+% ( 585856 - 305364) / 9600;
+% (1161728 - 595109) / 9600]
+
+%[(301440 - 9600) / 9600;
+% (288403 - 9600) / 9600;
+% (300845 - 9600) / 9600;
+% ( 51540 - 9600) / 9600;
+% (298288 - 9600) / 9600;
+% ( 75648 - 9600) / 9600;
+% (309352 - 9600) / 9600;
+% (286164 - 9600) / 9600;
+% (309675 - 9600) / 9600;
+% (301440 - 9600) / 9600;
+% (304198 - 9600) / 9600;
+% (589945 - 9600) / 9600;
+% (591921 - 9600) / 9600;
+% (309352 - 9600) / 9600;
+% (587719 - 9600) / 9600;
+% (284643 - 9600) / 9600;
+% (288403 - 9600) / 9600;
+% (281820 - 9600) / 9600;
+% (573990 - 9600) / 9600;
+% (576030 - 9600) / 9600;
+% (286164 - 9600) / 9600;
+% (575909 - 9600) / 9600]
 

### 2014-08-08 analysis/figures/paper_figures.tex
Updated text

@@
 %% Rabbit 9 = Subject 2
+
+\section{Methods}
+This section describes the computational analysis performed on the data.
+For all analog channels, the data was first processed with a high-pass Butterworth filter with a stopband-edge frequency of 2 Hz, a passband-edge frequency of 10 Hz, a stopband attenuation of 90 dB, and passband ripple of 1 dB.
+Afterwards, cardiac removal is performed on all channels using the methods described in section \ref{section:cardiac}.
+
+\subsection{Visual Evoked Potential}
+During the VEP experiments, the digital in channel was synchronized with the LED turning on and off.
+For both the on and off edges, the signal from the electrodes were aligned to compute the mean signal and confidence intervals.
+[Some edges were removed if the the timing was inconsistent for some reason.]
+The displayed confidence intervals are a 95\% bootstrapped value for the mean.
+All VEP trials include between 153 and 208 events.
+
+\subsection{Steady-State Visual Evoked Potential}
+During the SSVEP experiment, and LED was flashed at 40 Hz with a 50\% duty cycle.
+For both a resting state and experimental period, Welsh's method was used to compute the power spectral density with a window length of 2 seconds and an overlap of 25\%.
+The ratio of the experimental power with the resting state power at each frequency is shown.
+All data within 3 Hz of a 60 Hz harmonics are excluded due to showing heavy artifacts from electrical equipment.
+The background data includes data more than 3 Hz away from harmonics of 40 Hz, and the harmonic data takes the maximum power at a frequency within 3 Hz of each harmonic.
+All experimental measurements lasted between 22.5 seconds and 57.0 seconds, and all resting state measurements lasted between 28.8 seconds and 60.7 seconds.
+\subsection{Steady-State Auditory Evoked Potential}
+[Same processing as SSVEP]
+All experimental measurements lasted between 29.0 seconds and 59.2 seconds, and all resting state measurements lasted between 4.4 seconds and 59.0 seconds.
+[Subject 2 has very short resting state measurements for SSAEP - shortest for subject 1 is 28.4 seconds]
+\subsection{Cardiac Artifacts and Removal}
+The cardiac data is high-passed.
+The maximum in a 0.18 second interval is considered the R peak.
+The segments are split 0.63 between the R peaks (this is so that the P-wave and T-wave end up on opposite sides).
+The mean is computed for each time step relative to the R peak, and a zero is averaged in for trials that do not extend that far out (the R peaks are not exactly equally centered).
+In some sense, this indicates uncertainty in what the cardiac artifacts are at that time, so a smaller adjustment is made.
+The mean for the cardiac shape is then subtraced out from each electrode.
+\label{section:cardiac}
 \begin{figure}[H]
@@
 The performance is consistent between the two basilar tip trials.
-}
+The responses measured during the experimental trials are much larger than the signals during the control trials.}
 \label{fig:position}
@@
 \end{tabular}
-\caption{Cardiac contamination and cleaning. 1076 trials for qrs mean}
+\caption{Cardiac contamination and cleaning.
+The cardiac aligned measurements shows the mean and 95\% bootstrap confidence intervals for 1076 segments of data.
+The endovascular electrode is located at the mid-basilar location, which demonstrated the largest contamination from cardiac activity.
+The P-wave, QRS complex, and T-wave are all visible in the signal from the cardiac electrode.
+The raw trace show highly repeatable cardiac artifacts in the endovascular electrode, which are removed in the cleaned version.
+The VEP-aligned data has the same general trend before and after cardiac artifacts are accounted for, but the confidence intervals are much smaller after accounting for cardiac artifacts.}
 \label{fig:cardiac}
@@
 \_Thu\_15.05.2014\_16\%3A12\%3A19\_ssaep\_86      & 33 / 40 & 593190 1161856 & 59.2360 & 9600 573990 & 58.7906 \\
-\_Thu\_15.05.2014\_16\%3A58\%3A34\_ssaep\_86      & 36 / 40 & 595230 1161728 & 59.0102 & 9600 576030 & 59.0031 \\ \_Thu\_15.05.2014\_12\%3A26\%3A26\_ssaep\_ctr\_86 & 12 / 40 & 305364  585856 & 29.2179 & 9600 286164 & 28.8087 \\
+\_Thu\_15.05.2014\_16\%3A58\%3A34\_ssaep\_86      & 36 / 40 & 595230 1161728 & 59.0102 & 9600 576030 & 59.0031 \\
+\_Thu\_15.05.2014\_12\%3A26\%3A26\_ssaep\_ctr\_86 & 12 / 40 & 305364  585856 & 29.2179 & 9600 286164 & 28.8087 \\
 \_Thu\_15.05.2014\_17\%3A12\%3A38\_ssaep\_86      & 40 / 40 & 595109 1161728 & 59.0228 & 9600 575909 & 58.9905

### 2014-08-14 analysis/release/cardiac/cardiac_figure.m
Documented code.

@@ -1,132 +1,193 @@
-% cardiac_figure.m
+function [ f_start, f_end, f1, f2, f3, f4, f5 ] = cardiac_figure(subject_ID, experiment, index, interval, filters, cardiac_filters)
+%CARDIAC_FIGURE  Generates figures demonstrating removal of cardiac artifacts.
 %
-% This function generates the figures for the cardiac artifact cleaning.
+%   [ FS, FE, F1, F2, F3, F4, F5 ] = CARDIAC_FIGURE(SUBJECT_ID, EXPERIMENT, ...
+%                                                   INDEX, INTERVAL, FILTERS, ...
+%                                                   CARDIAC_FILTERS)
+%
+% Parameters:
+%
+%   SUBJECT_ID is a string with the name of the subject (subject1 or subject2).
+%
+%   EXPERIMENT is a string with the name of the experiment to use (vep, ssaep,
+%   or ssvep).
+%
+%   INDEX is the trial number of this experiment to plot.
+%
+%   INTERVAL is the time interval in seconds to plot the example contaminated
+%   and cleaned signal for.
+%
+%   FILTERS is a list of filters to apply to all analog channels other than
+%   the cardiac channel.
+%
+%   CARDIAC_FILTERS is a list of filters to apply to the cardiac channel.
+%
+% Output:
+%
+%   FS is the figure handle for the starting, contaminated example signal.
+%
+%   FE is the figure handle for the ending, cleaned example signal.
+%
+%   F1 is the figure handle for the plot of the cardiac signal with the
+%   detected peaks.
+%
+%   F2 is the figure handle for the plot of the time between the detected
+%   peaks.
+%
+%   F3 is the figure handle for the plot of the time between complexes.
+%
+%   F4 is the figure handle for the plot of the averaged complexes and
+%   confidence intervals for the averages.
+%
+%   F5 is the figure handle for the plot of all of the complexes, aligned to
+%   the detected R peak.
+%
+%   Figures are saved as PDF, SVG, and FIG files in the directory figures.
 
-function [] = cardiac_figure()
-
-% Use subject 1 vep at mid-basilar for plot
-subject_ID = 'subject1';
-experiment = 'vep';
-index = 3;
 
 %% Constants
[…]

### 2014-08-14 analysis/release/cardiac/cardiac_removal.m

@@ -1,183 +1,188 @@
-% cardiac_removal.m
+function [ chData ] = cardiac_removal(chData, cardiacData, fs, color, f1, f2, f3, f4)
+%CARDIAC_REMOVAL  Removes cardiac artifact from another channel.
 %
-% This function removes cardiac artifacts from other channels and plots
-% relevant figures if requested. The channel that is having artifacts
-% removed must be highpass filtered, or the results will be poor.
+% CHDATA = CARDIAC_REMOVAL(CHDATA, CARDIACDATA, FS, COLOR, F1, F2, F3, F4)
 %
-% Arguments:
-%   chData: analog channel to filter cardiac artifacts from
-%   cardiacData: cardiac recording from the same period
-%   name: filename to save to (not currently used)
-%   color: color to plot with, if requested
-%   f1: figure handle for raw cardiac data plot with detected peaks
-%   f2: figure handle for plot of time between peaks
-%   f3: figure handle for plot of time between complexes
-%   f4: figure handle for plot of averaged signals and confidence intervals
-%   f5: figure handle for plot of all signals
+% Parameters:
+%
+%   CHDATA is an vector of data representing an analog channel from which to
+%   remove cardiac artifacts. This channel must be highpass filtered for this
+%   function to perform well.
+%
+%   CARDIACDATA is a vector of data representing a channel recording from a
+%   cardiac electrode.
+%
+%   COLOR specifies which color to plot this channel in (if plots are
+%   requested).
+%
+%   F1 is the figure handle for the plot of the cardiac signal with the
+%   detected peaks.
+%
+%   F2 is the figure handle for the plot of the time between the detected
+%   peaks.
+%
+%   F3 is the figure handle for the plot of the averaged complexes and
+%   confidence intervals for the averages.
+%
+%   F4 is the figure handle for the plot of all of the complexes, aligned to
+%   the detected R peak.
+%
+%   Note that any of F1, F2, F3, or F4 may be set to 0 or omitted if the plot
+%   is not desired.
 %
 % Output:
-%   chData: cardiac filtered data
+%
+%   CHDATA is the same as the original data, with cardiac artifacts filtered
+%   out.
 
[…]

### 2014-08-14 analysis/release/config/constants.m

@@ -1,23 +1,0 @@
-% constants.m
-%
-% This function gives information about the recordings.
-%
-% Arguments:
-%   None
-%
-% Output:
-%   maxNumberOfChannels: # of consecutive analog input channels, starting with
-%                        channel 1, to extract from the binary files (which
-%                        contain 64 analog channels and the digital in channel
-%                        (channel 65)
-%   digitalInCh: digital in channel number
-%   original_sampling_rate_in_Hz: sampling rate for the data
-function [ maxNumberOfChannels, digitalInCh, original_sampling_rate_in_Hz ] = constants()
-
-% 
-maxNumberOfChannels = 10;
-digitalInCh = 65;
-original_sampling_rate_in_Hz = 9600;
-
-end
-

### 2014-08-14 analysis/release/config/get_pathname.m

@@ -1,20 +1,31 @@
-% get_pathname.m
+function [ pathname, experiment_log ] = get_pathname(subject_ID, experiment)
+%GET_PATHNAME Returns paths to binary data file directory and experiment logs.
 %
-% Arguments:
-%   subject_ID: string ('subject1' or 'subject2') for which subject to get
-%               paths for
-%   experiment: string ('vep', 'ssaep', 'ssvep') for which experiment to get
-%               paths for
+%   [ PATHNAME, EXPERIMENT_LOG ] = GET_PATHNAME(SUBJECT_ID, EXPERIMENT) gives
+%   the relevant paths for subject SUBJECT_ID for experiment EXPERIMENT. The
+%   binary data files are contained in the directory PATHNAME, and the
+%   experiment log file has the name EXPERIMENT_LOG.
+%
+% Parameters:
+%
+%   SUBJECT_ID is a string ('subject1' or 'subject2') of the name of the
+%   subject. The available options are in the data directory.
+%
+%   EXPERIMENT is a string ('vep', 'ssaep', 'ssvep') of the experiment name.
+%
+% Output:
+%
+%   PATHNAME is the directory that contains the binary data files.
+%
+%   EXPERIMENT_LOG is the name of the experiment log for the experiment.
 
-function [ pathname, pathname_comments ] = get_pathname(subject_ID, experiment)
+experiment = lower(experiment); % pathnames use lowercase (vep, ssaep, ssvep)
 
-% pathnames use lowercase 'vep', 'ssaep', 'ssvep'
-experiment = lower(experiment);
-
-% path for the data in easter binary format
+% path for the binary files
 pathname = ['data/' subject_ID '/' experiment '/'];
-% file containing comments written on the experiment day to use as labels for the figure titles
-pathname_comments = ['data/' subject_ID '/neuro_experiment_log.txt'];
+
+% file containing comments written on the experiment day
+experiment_log = ['data/' subject_ID '/neuro_experiment_log.txt'];
 
 end
 

### 2014-08-14 analysis/release/config/plot_settings.m

@@ -1,16 +1,18 @@
-% plot_settings.m
+function [ channelToPlot, CM ] = plot_settings()
+%PLOT_SETTINGS  Specifies which channels to plot and colors for the channels.
 %
-% This function specifies which channels to plot and the colors to use for
-% them.
+%   [ CHANNELTOPLOT, CM ] = PLOT_SETTINGS()
 %
-% Arguments:
+% Parameters:
+%
 %   None.
 %
 % Output:
-%   channelToPlot: list of channels to be plotted
-%   CM: color matrix - colors for each channel in the plot
-
-function [ channelToPlot, CM ] = plot_settings()
+%
+%   CHANNELTOPLOT is a list of the channels to be plotted.
+%
+%   CM is a color matrix. Each row corresponds to one of the channels, and
+%   each of the columns corresponds to one of the RGB values.
 
 channelToPlot = [3,5,8,2]; 
 

### 2014-08-14 analysis/release/config/subject_information.m

@@ -1,28 +1,37 @@
-% subject_information.m
+function [ numChannels, digitalCh, fs, channelNames, GND, earth ] = subject_information(subject_ID)
+%SUBJECT_INFORMATION  Returns information about the data for the subject.
 %
-% This function gives information about the recordings.
+% [ NUMCHANNELS, DIGITALCH, FS, CHANNELNAMES, GND, EARTH ] = SUBJECT_INFORMATION(SUBJECT_ID)
 %
 % Arguments:
-%   subject_ID: not currently used
+%
+%   SUBJECT_ID is a string containing the name of the subject. This is not
+%   currently used due to the fact that all example subjects have the same
+%   information.
 %
 % Output:
-%   maxNumberOfChannels: # of consecutive analog input channels, starting with
-%                        channel 1, to extract from the binary files (which
-%                        contain 64 analog channels and the digital in channel
-%                        (channel 65)
-%   digitalInCh: digital in channel number
-%   original_sampling_rate_in_Hz: sampling rate for the data
-%   channelNames: list of strings for where the channels record from
-%   gtechGND: where the ground is connected to
-%   earth: which electrode is used as earth
+%
+%   NUMCHANNELS is an integer specifying how many channels in total are
+%   available for the subject.
+%
+%   DIGITALCH is the index of the digital channel for this subject.
+%
+%   FS is the sampling frequency for this subject.
+%
+%   CHANNELNAMES is a list of strings recording which electrode each channel
+%   was connected to.
+%
+%   GND is a string recording where the ground electrode on the recording
+%   device was connected to.
+%
+%   EARTH is a string recording which part of the subject was connected to
+%   earth.
 
-function [ maxNumberOfChannels, digitalInCh, original_sampling_rate_in_Hz, channelNames, gtechGND, earth ] = subject_information(subject_ID)
-
-maxNumberOfChannels = 10
-digitalInCh = 65;
-original_sampling_rate_in_Hz = 9600;
+numChannels = 11;
+digitalCh = 11;
+fs = 9600;
 channelNames = {'Disconnected','Endo','Mid head','Disconnected','Right Eye','Right Leg','Back Head','Left Eye','Bottom Precordial','Top Precordial'};
-gtechGND = 'Nose';
+GND = 'Nose';
 earth = 'Left Leg';
 
 end

### 2014-08-14 analysis/release/ssavep/plot_all_ssavep.m

@@ -1,39 +1,51 @@
-% plot_all_ssavep.m
+function [] = plot_all_ssavep(ssavep, subject_ID, index_list, filter_cardiac, filters, cardiac_filters)
+%PLOT_ALL_SSAVEP  Loads and plots SSAEP and SSVEP frequency responses.
 %
-% Script to load and plot (using plot_ssavep.m) all of the SSAEP or SSVEP
-% trials in a directory. The same type of plots are generated for both SSAEP
-% and SSVEP, so there is no difference in the code.
+%   PLOT_ALL_SSAVEP(SSAVEP, SUBJECT_ID, INDEX_LIST, FILTERS, CARDIAC_FILTERS)
 %
-% Arguments:
-%   ssavep: either 'ssaep' or 'ssvep' (string) - selects which experiment to plot
-%   subject_ID: string with the name of the subject
-%     - 'subject1' or 'subject2'
-%   publication_quality: either 1 or 2, 1 is supposed to plot confidence
-%                        intervals (not functional as of 8/6/14), 2 does not
-%                        plot confidence intervals (is functional)
-%                        [optional - defaults to 2]
-%   index_list: list of indices to plot
-%                [optional - defaults to all experiments]
-%   filters: filters to apply to all analog channels other than cardiac
+%   SSAVEP is a string that selects which experiment to plot (ssaep or ssvep).
+%
+%   SUBJECT_ID is a string with the name of the subject (subject1 or subject2).
+%
+%   INDEX_LIST is a list of indices to plot for this experiment on this
+%   subject (ordered based on time).
+%     [default: plot all recordings for this experiment on this subject]
+%
+%   FILTER_CARDIAC is a boolean value that indicates whether or not to perform
+%   removal of cardiac artifacts.
+%     [default: true]
+%
+%   FILTERS is a list of filters to apply to all analog channels other than
+%   the cardiac channel.
 %     [default: only high-pass filter]
-%   cardiac_filters: filters to apply to cardiac channel
-%     [default: only high-pass filter]
 %
-% Output:
-%   No return value.
-%   Figures are saved as FIG, PDF, and SVG files in figures/.
+%   CARDIAC_FILTERS is a list of filters to apply to the cardiac channel.
+%     [default: only high-pass filter]
 
-function plot_all_ssavep(ssavep, subject_ID, publication_quality, index_list, filters, cardiac_filters)
+% Output:
+%
+%   No return value.
+%
[…]

### 2014-08-14 analysis/release/ssavep/plot_ssavep.m

@@ -1,50 +1,90 @@
-% plot_ssavep.m
+function [ fgh ] = plot_ssavep(data, cleanDigitalIn, name, ssavep, fs, cardiac_data, windlengthSeconds, noverlapPercent, filters, cardiac_filters, CM, channelNames, comment)
+%PLOT_SSAVEP  Plots the SSAEP/SSVEP response for a single run.
 %
-% Plots the SSAEP/SSVEP response for a single experiment. In general, if the
-% data is in the same format as the example data, it is easier to use
-% plot_all_ssavep.m.
+% FGH = PLOT_SSAVEP(DATA, CLEANDIGITALIN, NAME, EXPERIMENT, FS, ...
+%                   CARDIAC_DATA, WINDLENGTHSECONDS, NOVERLAPPERCENT, ...
+%                   FILTERS, CARDIAC_FILTERS, CM, CHANNELNAMES, COMMENT)
 %
-% Arguments:
-%   data: cell array of the analog channel data
-%         each row corresponds to one of the channels
-%         first column is a string of the channel name
-%         second column is an array of the data
-%   cleanDigitalIn: binary array for the digital in channel (whether or not
-%                   experiment is running)
-%   experiment: either 'ssaep' or 'ssvep', specifying which experiment to plot
-%   fs: sampling frequency
-%   publication_quality: style of the plots
-%     - 1: shaded confidence intervals (not functional as of 8/6/14)
-%         WARNING: MATLAB appears to have a bug that causes figures with
-%                  shading to be saved improperly as PDF and EPS files.
-%                  plot2svg.m is an alternative method of saving, which
-%                  avoids the problem.
-%     - 2: no confidence intervals
-%   windlengthSeconds: window length in seconds for power spectral density
-%   noverlapPercent: overlap percentage for power spectral density windows
-%   filters: filters to apply to all analog channels other than cardiac
-%   cardiac_filters: filters to apply to cardiac channel
-%   channelToPlot: list of channel indices to plot
-%   CM: list of the colors for each of the channels in the plot
-%   name: filename to save to (does not include suffix)
-%   filter_cardiac: whether or not to perform cardiac removal
-%   comment: line from the experiment log corresponding to this run
[…]

### 2014-08-14 analysis/release/util/assert_match.m

@@ -1,19 +1,25 @@
-% assert_match.m
+function [] = assert_match(files, comments)
+%ASSERT_MATCH  Checks that the data files and experiment logs match.
+%
+% ASSERT_MATCH(FILES, COMMENTS)
 %
 % This function takes a list of the data files for an experiment and the
 % relevant lines in the experiment log to verify that the two match. A match
 % requires the two to have the same number of elements and to have the same
 % hour, minute, and second.
 %
-% Arguments:
-%   files: list of the filenames for an experiment
-%   comments: list of the lines in the experiment log for the experiment
+% Parameters:
+%
+%   FILES is a list of data filenames.
+%
+%   COMMENTS is a list of relevant lines from experiment log.
 %
 % Output:
+%
 %   No return value.
+%
 %   Results in an assertion error if there is a problem with matching.
 
-function [] = assert_match(files, comments)
 
 %% Check for matching experiment log and data files
 assert(length(files) == length(comments)); % check that the experiment log and data files have the same number of VEP runs
@@ -32,8 +38,6 @@ for i = 1:length(files)
   files_minute = files{i}(19:20);
   assert(strcmp(files{i}(21), '_'))
   files_second = files{i}(22:23);
-  %assert(strcmp(files{i}(29:35), '_ssvep_')) % TODO - make this check experiment type
-  %files_extra = files{i}(34:end);
 
   % Hard coded parsing of experiment log
   comment = comments{i};

### 2014-08-14 analysis/release/util/get_filters.m

@@ -1,19 +1,21 @@
-% get_filters.m
+function [ filters ] = get_filters(fs, use_hpf, use_lpf, use_nf_60, use_nf_120, use_nf_180)
+%GET_FILTERS  Returns a list of the requsted filters.
 %
-% This function returns a list of the requested filters.
+% FILTERS = GET_FILTERS(FS, USE_HPF, USE_LPF, USE_NF_60, USE_NF_120, USE_NF_180)
 %
-% Arguments:
-%   fs: sampling frequency
-%   use_hpf: use highpass filter
-%   use_lpf: use lowpass filter
-%   use_nf_60: use 60 Hz notch filter
-%   use_nf_120: use 120 Hz notch filter
-%   use_nf_180: use 180 Hz notch filter
+% Parameters:
+%
+%   FS is the sampling frequency.
+%
+%   USE_HPF is a boolean indicating if the highpass filter is needed.
+%   USE_LPF is a boolean indicating if the lowpass filter is needed.
+%   USE_NF_60 is a boolean indicating if the 60 Hz notch filter is needed.
+%   USE_NF_120 is a boolean indicating if the 120 Hz notch filter is needed.
+%   USE_NF_180 is a boolean indicating if the 180 Hz notch filter is needed.
 %
 % Output:
-%   filters: cell array of requested filters
-
-function [ filters ] = get_filters(fs, use_hpf, use_lpf, use_nf_60, use_nf_120, use_nf_180)
+%
+%   FILTERS is a cell array of requested filters.
 
 filters = {};
 

### 2014-08-14 analysis/release/util/get_frequency.m

@@ -1,37 +1,40 @@
-% get_frequency.m
+function [ nominal_frequency, frequency ] = get_frequency(comment, filename)
+%GET_FREQUENCY  Reads the experiment log to get the frequency of an experiment.
 %
-% This function reads the relevant line in the experiment log to determine the
-% frequency of the stimulus.
+% [ NOMINAL_FREQUENCY, FREQUENCY ] = GET_FREQUENCY(COMMENT, FILENAME)
 %
-% Arguments:
-%   comment: string of the relevant line in the experiment log
-%   filename: filename of the data (not currently used)
+% Parameters:
+%
+%   COMMENT is the string of the relevant line in the experiment log.
+%
+%   FILENAME is the filename of the data (not currently used).
 %
 % Output:
-%   nominal_frequency: frequency written in the data log
-%   frequency: true frequency of stimulus (tends to be an unrounded version
-%              of nominal_frequency)
-
-function [ nominal_frequency, frequency ] = get_frequency(comment, filename)
+%
+%   NOMINAL_FREQUENCY is the frequency written in the data log.
+%
+%   FREQUENCY is the true frequency of stimulus (this tends to be an unrounded
+%   version of nominal_frequency)
 
 nominal_frequency = [];
 frequency = [];
+
+% Search for the numbers in comment
 if ~isempty(strfind(comment{1}(9:35), '10'))
     nominal_frequency = [nominal_frequency 10];
     frequency = [frequency 9.8000];
 end
 if ~isempty(strfind(comment{1}(9:35), '12'))
     nominal_frequency = [nominal_frequency 12];
-    frequency = [frequency 12]; % TODO: check if this is exact
+    frequency = [frequency 12];
 end
 if ~isempty(strfind(comment{1}(9:35), '40'))
     nominal_frequency = [nominal_frequency 40];
-    %frequency = [frequency 40.8333];
-    frequency = [frequency (40 + 5 / 6)];
+    frequency = [frequency 40.8333];
 end
-if ~isempty(strfind(comment{1}(9:45), '42'))
+if ~isempty(strfind(comment{1}(9:35), '42'))
     nominal_frequency = [nominal_frequency 42];
-    frequency = [frequency 42]; % TODO: check if this is exact
+    frequency = [frequency 42];
 end
 if ~isempty(strfind(comment{1}(9:35), '50'))
     nominal_frequency = [nominal_frequency 50];
[…]

### 2014-08-14 analysis/release/util/get_information.m

@@ -1,15 +1,21 @@
-% get_information.m
+function [ files, comments ] = get_information(pathname, pathname_comments, experiment)
+%GET_INFORMATION  Returns a list of files and comments from experiment log.
 %
-% Arguments:
-%   pathname: directory that contains the data files
-%   pathname_comments: experiment log file
-%   experiment: string ('VEP', 'SSAEP', or 'SSVEP')
+% [ FILES, COMMENTS ] = GET_INFORMATION(PATHNAME, PATHNAME_COMMENTS, EXPERIMENT)
+%
+% Parameters:
+%   PATHNAME is the directory that contains the data files.
+%
+%   PATHNAME_COMMENTS is the filename of the experiment log file.
+%
+%   EXPERIMENT is a string specifying the experiment (VEP, SSAEP, or SSVEP).
 %
 % Output:
-%   files: list of data filenames
-%   comments: list of relevant lines from experiment log
+%
+%   FILES is a list of data filenames.
+%
+%   COMMENTS is a list of relevant lines from experiment log.
 
-function [ files, comments ] = get_information(pathname, pathname_comments, experiment)
 
 % experiment log uses capitalized 'VEP', 'SSAEP', 'SSVEP'
 experiment = upper(experiment);
@@ -18,16 +24,13 @@ tmp = dir(pathname);       % get the list of data filenames for this particular 
 files = {tmp(3:end).name}; % chop out the '.' and '..' filename entries that are in every directory
 
 fid = fopen(pathname_comments);
-if fid==-1 % if the vep.txt comments file doesn't exist, display an error message to the console and skip the textscan
-    fprintf('Experiment log not found.\n');
-    allData = []; % TODO: make this an assert?
-else
-    comments = textscan(fid,'%s','Delimiter','\n'); % read log file
-    C = strfind(comments{1}, ['- ' experiment]);    % get rows for this experiment
-    rows = find(~cellfun('isempty', C));            % grab just the relevant rows
-    comments = comments{1}(rows);
-    fclose(fid);
-end
+assert(fid ~= -1) % check that the experiment log exist
+
+comments = textscan(fid,'%s','Delimiter','\n'); % read log file
+C = strfind(comments{1}, ['- ' experiment]);    % get rows for this experiment
+rows = find(~cellfun('isempty', C));            % grab just the relevant rows
+comments = comments{1}(rows);
+fclose(fid);                                    % close file
 
 % check that the files and experiment log match
 assert_match(files, comments);

### 2014-08-14 analysis/release/util/load_data.m

@@ -1,48 +1,39 @@
-% load_data.m
+function [ data, samples ] = load_data(filename, num_channels)
+%LOAD_DATA  Loads data from binary data files.
 %
-% This function loads the requested number of analog channels and the digital in channel.
+%   [ DATA, SAMPLES ] = LOAD_DATA(FILENAME, NUM_CHANNELS) reads binary data
+%   from the file FILENAME with NUM_CHANNELS channels recorded.
+% 
+% Parameters:
 %
-% Arguments:
-%   full_filename: file to be loaded
-%   maxNumberOfChannels: number of analog channels to load
-%   digitalInCh: index of the digital in channel
-%   channelNames: list of the names of the channels
+%   FILENAME is a string that can be either a relative or absolute path.
+%
+%   NUM_CHANNELS is the number of channels recorded in the binary file.
 %
 % Output:
-%   data: cell array (maxNumberOfChannels x 2) of analog channels
-%         each row corresponds to one of the channels
-%         first column is a string of the channel name
-%         second column is an array of the data
-%   cleanDigitalIn: boolean array of digital in channel
+%
+%   DATA is a matrix of single values. Each of the NUM_CHANNELS rows
+%   corresponds to one of the channels. Each of the SAMPLES columns
+%   corresponds to a sample from one of the timesteps.
+%
+%   SAMPLES is an integer that is the number of samples for each channel in
+%   the binary file.
 
-function [ data, cleanDigitalIn ] = load_data(full_filename, maxNumberOfChannels, digitalInCh, channelNames)
+%% Constants
+sample_size = 4;      % number of bytes in each sample
+precision = 'single'; % type of variable to read as
 
-% Open data file
-fid = fopen(full_filename, 'r');
+%% Check that data is complete
+F = dir(filename);                                     % get file information
+bytes = F.bytes;                                       % file size in bytes
+assert(mod(bytes, (num_channels * sample_size)) == 0); % check same number of samples in each channel
+samples = bytes / (num_channels * sample_size);        % number of samples in each channel
 
-% Create cell array for data
-data = cell(maxNumberOfChannels, 2);
-
-% Load each of the channels
-for j=1:maxNumberOfChannels
-    fseek(fid, 4*(j-1), 'bof');                   % move to first timestamp
-    dataColumn = fread(fid, Inf, 'single', 4*64); % read only this channel
-    channelName = channelNames{j};
-
-    % record data to output
-    data(j, 1) = {channelName};
-    data(j, 2) = {dataColumn};
-end
-
[…]

### 2014-08-14 analysis/release/util/make_legend.m

@@ -1,41 +1,57 @@
-% make_legend.m
+function [ f ] = make_legend(include_cardiac)
+%MAKE_LEGEND  Creates and saves a figure with the legend.
 %
-% This function creates and saves the legend.
+%   [ F ] = MAKE_LEGEND(INCLUDE_CARDIAC)
 %
-% Arguments:
-%   None
+% Parameters:
+%
+%   INCLUDE_CARDIAC is a boolean variable that indicated whether or not the
+%   cardiac channel should be included in the legend. This variable is
+%   optional and defaults to false.
 %
 % Output:
-%   f: figure handle
-%   Saves the legend as legend.pdf.
+%
+%   F is the figure handle of the figure with the legend.
+%
+% The figure is saved as legend.pdf and legend.svg in the directory figures.
 
-function [ f ] = make_legend()
+% Constants
+linewidth = 2;
+fontsize = 10;
 
-    % Create figure
-    f = figure;
-    hold on;
+% Create figure
+f = figure;
+hold on;
 
-    % Get plotting information
-    [ channelToPlot, CM ] = plot_settings();
-    [ channelNames, gtechGND, earth ] = subject_information('subject1');
+% Get plotting information
+[ channelToPlot, CM ] = plot_settings();
+[ numChannels, digitalCh, fs, channelNames, GND, earth ] = subject_information('subject1');
 
-    % Plot garbage to have something for the legend
-    legends = [];
-    for i = 1:numel(channelToPlot)
-      legends = [legends plot(0, 0, 'Color', CM(i, :), 'linewidth', 2)];
-    end
-    legends = [legends plot(0, 0, 'Color', 'black', 'linewidth', 2)];
+% Plot garbage to have something for the legend
+legends = [];
+for i = 1:numel(channelToPlot)
+  legends = [legends plot(0, 0, 'Color', CM(i, :), 'linewidth', linewidth)];
+end
+if (nargin >= 1) && include_cardiac
+    legends = [legends plot(0, 0, 'Color', 'black', 'linewidth', linewidth)];
+end
 
-    % make the legend
-    legend(legends, {channelNames{channelToPlot}, 'Cardiac'}, 'fontsize', 10);
+% make the legend
+if (nargin >= 1) && include_cardiac
+    legend(legends, {channelNames{channelToPlot}, 'Cardiac'}, 'fontsize', fontsize);
+else
+    legends
[…]

### 2014-08-14 analysis/release/util/reduce_all_data.m

@@ -1,7 +1,27 @@
-% example:
+function [] = reduce_all_data(start_dir, end_dir)
+%REDUCE_ALL_DATA  Recursively reduces all data in this directory.
+%
+% REDUCE_ALL_DATA(START_DIR, END_DIR)
+%
+% Parameters:
+%
+%   START_DIR is the directory to copy from.
+%
+%   END_DIR is the directory to copy into.
+%
+% Output:
+%
+%   No return value.
+%
+%   The new files are copied into END_DIR.
+%
+% Directory names are copied directly. Text files are considered special
+% cases, and are copied directly. All other files are assumed to be data
+% files, and are reduced.
+%
+% Example:
 % >> reduce_all_data('../data_complete', '../data');
 
-function [] = reduce_all_data(start_dir, end_dir)
 
 % print current directory
 fprintf('%s\t%s\n', start_dir, end_dir);
@@ -25,19 +45,24 @@ for i = 1:numel(files)
         continue;
     end
 
+    start = [start_dir '/' file.name];
+    finish = [end_dir '/' file.name];
+
     if (file.isdir)
         % recurse on directories
-        reduce_all_data([start_dir '/' file.name], [end_dir '/' file.name]);
+        reduce_all_data(start, finish);
     else
-        % skip text files (experiment logs)
+        % print current file
+        fprintf('%s\t%s\n', start, finish);
+
         if ((numel(file.name) >= 4) && strcmp(file.name(end + (-3:0)), '.txt'))
-            continue;
+            % just copy text files (experiment logs)
+            copyfile(start, finish);
+        else
+            % keep only the first 10 channels and digital in channel
+            reduce_data(start, finish, 65, [1:10, 65]);
         end
 
-        % print current file
-        fprintf('%s\t%s\n', [start_dir '/' file.name], [end_dir '/' file.name]);
-        % keep only the first 10 channels and digital in channel
-        reduce_data([start_dir '/' file.name], [end_dir '/' file.name], 65, [1:10, 65]);
     end
 end
 

### 2014-08-14 analysis/release/util/reduce_data.m

@@ -1,4 +1,21 @@
 function [ data ] = reduce_data(start_file, end_file, num_channels, channels_to_keep)
+%REDUCE_DATA  Creates a new data file containing only some channels.
+%
+% DATA = REDUCE_DATA(START_FILE, END_FILE, NUM_CHANNELS, CHANNELS_TO_KEEP)
+%
+% Parameters:
+%
+%   START_FILE is the filename of the original binary data file.
+%
+%   END_FILE is the filename of the reduced binary data file.
+%
+%   NUM_CHANNELS is the number of channels in the original file.
+%
+%   CHANNELS_TO_KEEP is a list of the channels to keep in the reduced file.
+%
+% Output:
+%
+%   DATA is the matrix of the remaining data.
 
 % Constants
 element_size = 4;

### 2014-08-14 analysis/release/util/run_filters.m

@@ -1,15 +1,17 @@
-% run_filters.m
+function [ data ] = run_filters(data, filters)
+%RUN_FILTERS  Processes a signal with the requested filters.
 %
-% This function processes a signal with the requested filters.
+% DATA = RUN_FILTERS(DATA, FILTERS)
 %
-% Arguments:
-%   data: signal to run the filters on
-%   filters: array of requested filters
+% Parameters:
+%
+%   DATA is a vector representing the signal to run the filters on.
+%
+%   FILTERS is a cell array of requested filters.
 %
 % Output:
-%   data: filtered version of signal
-
-function [ data ] = run_filters(data, filters)
+%
+%   DATA is the filtered version of signal.
 
 for filter = filters
     data = filtfilt(filter{1}.sosMatrix, filter{1}.ScaleValues, data);

### 2014-08-14 analysis/release/cardiac/cardiac_removal.m
Fix to figure number used.

@@ -138,7 +138,7 @@ if (nargin >= 7 && f3 ~= 0)
     time_axis = ((1:numel(cardiac)) - max_before) / fs * 1000;
 
     % plot mean of cardiac activity
-    set(0, 'CurrentFigure', f4);
+    set(0, 'CurrentFigure', f3);
     hold on;
     plot(time_axis, cardiac, 'color', color, 'linewidth', 2);
 
@@ -165,7 +165,7 @@ if (nargin >= 8 && f4 ~= 0)
     time_axis = ((1:numel(cardiac)) - max_before) / fs * 1000;
 
     % plot all cardiac activity trials
-    set(0, 'CurrentFigure', f5);
+    set(0, 'CurrentFigure', f4);
     hold on;
     plot(time_axis, padded, 'color', color);
 

### 2014-08-14 analysis/release/cardiac/cardiac_figure.m
No filename is requred anymore

@@ -154,7 +154,7 @@ for ii=1:length(channelToPlot)
     plot(time_axis, chData(time), 'LineWidth', 2, 'Color', CM(ii, :));
 
     % Remove cardiac artifacts and generate plots
-    chData = cardiac_removal(chData, cardiac_data, fs, filename, CM(ii, :), 0, 0, f3, f4);
+    chData = cardiac_removal(chData, cardiac_data, fs, CM(ii, :), 0, 0, f3, f4);
 
     % Plot cleaned data
     set(0, 'CurrentFigure', f_end);

### 2014-08-14 analysis/release/util/make_legend.m
Remove debugging output

@@ -40,7 +40,6 @@ end
 if (nargin >= 1) && include_cardiac
     legend(legends, {channelNames{channelToPlot}, 'Cardiac'}, 'fontsize', fontsize);
 else
-    legends
     legend(legends, channelNames(channelToPlot), 'fontsize', fontsize);
 end
 

### 2014-08-14 analysis/release/layout/figures.tex
Add more documented code.

\documentclass[]{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{multirow}

\pagestyle{plain}

\begin{document}

\setlength{\tabcolsep}{2pt}
\begin{figure}[H]
\begin{center}
\includegraphics[]{../figures/legend.pdf}
\hspace{0.3cm}
\begin{tabular}{c|cc|cc}
& \multicolumn{2}{c|}{Experiment} & \multicolumn{2}{c}{Control} \\
& Subject 1 & Subject 2 & Subject 1 & Subject 2 \\
\hline
\raisebox{-0.5\height}{\rotatebox{90}{VEP On}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../figures/Thu_15_05_2014_11_57_42_labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../figures/Tue_06_05_2014_11_17_10-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../figures/Thu_15_05_2014_12_15_47-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../figures/Tue_06_05_2014_11_25_22-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{VEP Off}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../figures/Thu_15_05_2014_11_57_42_off_labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../figures/Tue_06_05_2014_11_17_10_off-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../figures/Thu_15_05_2014_12_15_47_off-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../figures/Tue_06_05_2014_11_25_22_off-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../figures/Thu_15_05_2014_14_26_54_labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../figures/Tue_06_05_2014_11_37_22-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../figures/Thu_15_05_2014_12_26_26-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../figures/Tue_06_05_2014_11_42_15-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../figures/Thu_15_05_2014_14_20_24_labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../figures/Tue_06_05_2014_11_14_51-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../figures/Thu_15_05_2014_12_13_26-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../figures/Tue_06_05_2014_11_23_01-crop.pdf}}
\end{tabular}
\caption{}
\end{center}
\end{figure}
\setlength{\tabcolsep}{6pt}

\clearpage

\setlength{\tabcolsep}{2pt}
\begin{figure}[H]
\begin{center}
\begin{tabular}{c|cccc|cc}
         & \multicolumn{4}{c|}{Experiment}                       & \multicolumn{2}{c}{Control} \\
         &             &             &             &             & Live         & Dead \\
\hline
Location & Basilar Tip & Mid-Basilar & VB Junction & Basilar Tip & Basilar Tip  & Basilar Tip \\
Time     & 11:57:42    & 14:13:26    & 15:54:54    & 16:47:47    & 12:15:47     & 17:22:22 \\
Time     & 0:00:00 & 2:15:44 & 3:57:12 & 4:50:05 & 0:18:05 & 5:24:40 \\ % TODO: time relative to anesthesia? relative to surgery
\hline
\raisebox{-0.5\height}{\rotatebox{90}{VEP On}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_11_57_42_labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_14_13_26-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_15_54_54-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_16_47_47-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_12_15_47-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_17_22_22-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{VEP Off}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_11_57_42_off_labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_14_13_26_off-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_15_54_54_off-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_16_47_47_off-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_12_15_47_off-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_17_22_22_off-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_12_31_02_labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_14_26_54-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_16_12_19-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_16_58_34-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_12_26_26-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_17_12_38-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_12_08_22_labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_14_20_24-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_16_02_44-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_16_38_47-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_12_13_26-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.30]{../figures/Thu_15_05_2014_17_18_01-crop.pdf}}
\end{tabular}
\caption{}
\label{fig:position}
\end{center}
\end{figure}
\setlength{\tabcolsep}{6pt}

\clearpage

\begin{figure}[H]
\begin{center}
\begin{tabular}{cc|cc}
\raisebox{-0.5\height}{\multirow{3}{*}{
\begin{tabular}{c}
Cardiac-Aligned  Measurements \vspace{0.7cm} \\
\includegraphics[scale=0.64]{../figures/Thu_15_05_2014_14_13_26_cardiac-crop.pdf}
\end{tabular}
}} &
& Raw Trace & VEP-Aligned \\
\hline
&
\raisebox{-0.5\height}{\rotatebox{90}{Contaminated}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../figures/Thu_15_05_2014_14_13_26_start-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../figures/Thu_15_05_2014_14_13_26_cardiac_labelled-crop.pdf}} \\
&
\raisebox{-0.5\height}{\rotatebox{90}{Cleaned}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../figures/Thu_15_05_2014_14_13_26_end-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../figures/Thu_15_05_2014_14_13_26_labelled-crop.pdf}} \\
\end{tabular}
\caption{}
\end{center}
\end{figure}
\end{document}

### 2014-08-14 analysis/release/generate_all.m

@@ -1,4 +1,15 @@
 function [] = generate_all()
+%GENERATE_ALL  Generates all figures required for the paper figures.
+%
+% GENERATE_ALL()
+%
+% Parameters:
+%
+%   None.
+%
+% Output:
+%
+%   Figures saved to the directory figures.
 
 addpath('cardiac');
 addpath('config');
@@ -6,9 +17,14 @@ addpath('ssavep');
 addpath('util');
 addpath('vep');
 
-mkdir(pwd(),  'figures');
+if ~exist('figures', 'dir')
+    mkdir(pwd(),  'figures');
+end
+
+make_legend();
 
 plot_all_vep('subject1');
+plot_all_vep('subject1', 2, [3], false);
 plot_all_ssavep('ssaep', 'subject1');
 plot_all_ssavep('ssvep', 'subject1');
 
@@ -16,7 +32,7 @@ plot_all_vep('subject2');
 plot_all_ssavep('ssaep', 'subject2');
 plot_all_ssavep('ssvep', 'subject2');
 
-cardiac_figure();
+cardiac_figure('subject1', 'vep', 3, [10, 11]); % Use subject 1 vep at mid-basilar for plot
 
 end
 

### 2014-08-14 analysis/release/layout/convert_to_pdf.sh

@@ -1,0 +1,72 @@
+#! /bin/bash -x
+inkscape ../figures/Thu_15_05_2014_11_57_42_labelled.svg --export-pdf=../figures/Thu_15_05_2014_11_57_42_labelled.pdf
+inkscape ../figures/Tue_06_05_2014_11_17_10.svg --export-pdf=../figures/Tue_06_05_2014_11_17_10.pdf
+inkscape ../figures/Thu_15_05_2014_12_15_47.svg --export-pdf=../figures/Thu_15_05_2014_12_15_47.pdf
+inkscape ../figures/Tue_06_05_2014_11_25_22.svg --export-pdf=../figures/Tue_06_05_2014_11_25_22.pdf
+inkscape ../figures/Thu_15_05_2014_11_57_42_off_labelled.svg --export-pdf=../figures/Thu_15_05_2014_11_57_42_off_labelled.pdf
+inkscape ../figures/Tue_06_05_2014_11_17_10_off.svg --export-pdf=../figures/Tue_06_05_2014_11_17_10_off.pdf
+inkscape ../figures/Thu_15_05_2014_12_15_47_off.svg --export-pdf=../figures/Thu_15_05_2014_12_15_47_off.pdf
+inkscape ../figures/Tue_06_05_2014_11_25_22_off.svg --export-pdf=../figures/Tue_06_05_2014_11_25_22_off.pdf
+inkscape ../figures/Thu_15_05_2014_11_57_42_labelled.svg --export-pdf=../figures/Thu_15_05_2014_11_57_42_labelled.pdf
+inkscape ../figures/Thu_15_05_2014_14_13_26.svg --export-pdf=../figures/Thu_15_05_2014_14_13_26.pdf
+inkscape ../figures/Thu_15_05_2014_15_54_54.svg --export-pdf=../figures/Thu_15_05_2014_15_54_54.pdf
+inkscape ../figures/Thu_15_05_2014_16_47_47.svg --export-pdf=../figures/Thu_15_05_2014_16_47_47.pdf
+inkscape ../figures/Thu_15_05_2014_12_15_47.svg --export-pdf=../figures/Thu_15_05_2014_12_15_47.pdf
[…]

### 2014-08-14 analysis/release/vep/plot_all_vep.m

@@ -1,49 +1,62 @@
-% plot_all_vep.m
+function [] = plot_all_vep(subject_ID, publication_quality, index_list, filter_cardiac, preEventPlot_sec, postEventPlot_sec, filters, cardiac_filters)
+%PLOT_ALL_VEP  Loads and plots VEP on/off responses.
 %
-% Script to load and plot (using plot_vep.m) all of the VEP trials in a
-% directory.
+%   PLOT_ALL_VEP(SUBJECT_ID, PUBLICATION_QUALITY, INDEX_LIST, FILTER_CARDIAC, ...
+%                PREEVENTPLOT_SEC, POSTEVENTPLOT_SEC, FILTERS, CARDIAC_FILTERS)
 %
-% Arguments:
-%   subject_ID: string with the name of the subject
-%     - 'subject1' or 'subject2'
-%   publication_quality: style of the plots
+% Parameters:
+%
+%   SUBJECT_ID is a string with the name of the subject (subject1 or subject2).
+%
+%   PUBLICATION_QUALITY is an integer specifying the style of the plots.
 %     - 1: shaded confidence intervals
 %         WARNING: MATLAB appears to have a bug that causes figures with
 %                  shading to be saved improperly as PDF and EPS files.
-%                  plot2svg.m is an alternative method of saving, which
+%                  PLOT2SVG is an alternative method of saving, which
 %                  avoids the problem.
 %     - 2: no confidence intervals
 %     - 3: dashed line for confidence intervals
 %     - 4: all trials rather than confidence intervals
 %     [default: 2]
-%   index_list: list of indices to plot
-%     [default: plot all available recordings for subject]
-%   filter_cardiac: whether or not to perform cardiac removal
+%
+%   INDEX_LIST is a list of indices to plot for this subject (ordered based
+%   on time).
+%     [default: plot all recordings for this experiment on this subject]
+%
+%   FILTER_CARDIAC is a boolean value that indicates whether or not to perform
+%   removal of cardiac artifacts.
 %     [default: true]
-%   preEventPlot_sec: number of seconds before event to start plotting
+%
+%   PREEVENTPLOT_SEC is the number of seconds before the event to start plot.
 %     [default: 0.05]
-%   postEventPlot_sec: number of seconds after event to stop plotting
+%
+%   POSTEVENTPLOT_SEC is the number of seconds after the event to stop plot.
 %     [default: 0.1]
[…]

### 2014-08-14 analysis/release/vep/plot_vep.m

@@ -1,42 +1,86 @@
-% plot_vep.m
+function [ fgh ] = plot_vep(data, cleanDigitalIn, name, fs, publication_quality, cardiac_data, on_off, preEventPlot_sec, postEventPlot_sec, filters, cardiac_filters, CM, channelNames, comment)
+%PLOT_VEP  Plots the VEP response for a single run.
 %
-% Plots the VEP response for a single experiment. In general, if the data is
-% in the same format as the example data, it is easier to use plot_all_vep.m.
+% FGH = PLOT_VEP(DATA, CLEANDIGITALIN, NAME, FS, PUBLICATION_QUALITY, ...
+%                CARDIAC_DATA, ON_OFF, PREEVENTPLOT_SEC, POSTEVENTPLOT_SEC, ...
+%                FILTERS, CARDIAC_FILTERS, CM, CHANNELNAMES, COMMENT)
 %
-% Arguments:
-%   data: cell array of the analog channel data
-%         each row corresponds to one of the channels
-%         first column is a string of the channel name
-%         second column is an array of the data
-%   cleanDigitalIn: binary array for the digital in channel (whether or not
-%                   LED is on)
-%   name: filename to save to (does not include suffix)
-%   fs: sampling frequency
-%   publication_quality: style of the plots
+% Parameters:
+%
+%   DATA is a matrix of values from the analog channels connected to the
+%   electrodes. Each of the rows corresponds to one of the channels. Each of
+%   the columns corresponds to a sample from one of the timesteps.
+%
+%   CLEANDIGITALIN is a binary vector of the digital in channel (whether or not
+%   the LED is on at each time step).
+%
+%   NAME is a string of the filename to save to (should not include suffix).
+%
+%   FS is the sampling frequency in Hz.
+%
+%   PUBLICATION_QUALITY is an integer specifying the style of the plots.
 %     - 1: shaded confidence intervals
 %         WARNING: MATLAB appears to have a bug that causes figures with
 %                  shading to be saved improperly as PDF and EPS files.
-%                  plot2svg.m is an alternative method of saving, which
+%                  PLOT2SVG is an alternative method of saving, which
 %                  avoids the problem.
 %     - 2: no confidence intervals
 %     - 3: dashed line for confidence intervals
 %     - 4: all trials rather than confidence intervals
[…]

### 2014-08-14 analysis/release/vep/plot_vep.m
Remove pause

@@ -124,7 +124,6 @@ fgh = figure('Color',[1 1 1],'units','pixels','position',[0 0 (width + 2 * margi
 % make axes with correct margins
 axes('units', 'pixel', 'position', [margins margins width height]);
 hold on; % Allow all channels to be shown
-pause
 
 
 %% Miscellaneous preparation for figure

### 2015-01-04 analysis/release/classify/classify_all.m
Updates to classifier

@@ -1,7 +1,7 @@
 function [ ] = classify_all()
 addpath(genpath('..'));
 file_experiment = '../data/subject1/vep/Thu_15_05_2014_11_57_42';
-file_control = '../data/subject1/vep/Thu_15_05_2014_12_15_47';
+file_control    = '../data/subject1/vep/Thu_15_05_2014_12_15_47';
 on_off = 'on';
 evaluate('../data/subject1/vep/Thu_15_05_2014_11_57_42', '../data/subject1/vep/Thu_15_05_2014_12_15_47', 'on')
 end

### 2015-01-04 analysis/release/classify/evaluate.m

@@ -9,7 +9,7 @@ elseif strfind(file_experiment, 'subject2')
     subject_ID = 'subject2';
 end
 
-[ accuracy, sensitivity, specificity ] = evaluate(experiment, control, subject_ID);
+[ accuracy, sensitivity, specificity ] = evaluate_h(experiment, control, subject_ID);
 
 end
 

### 2015-01-04 analysis/release/classify/evaluate_h.m

@@ -6,33 +6,93 @@ accuracy = [];
 sensitivity = [];
 specificity = [];
 
+%% Preliminary information about plotting
+
+% Information about recording 
+[ numChannels, digitalCh, fs, channelNames, GND, earth ] = subject_information(subject_ID);
+
+% Load names of data files and experiment log
+[ pathname, experiment_log ] = get_pathname(subject_ID, 'vep');
+[ files, comments ] = get_information(['../' pathname], ['../' experiment_log], 'vep');
+
+% Get list of channels to plot and colors for each channel
+[ channelToPlot, CM ] = plot_settings();
+channelToPlot = channelToPlot([end, 1:(end-1)]);
+
+chName = channelNames(channelToPlot);
+
 %for i = 1:numel(experiment)
 %  experiment{i} = experiment{i}(:, 1:10:end);
 %  control{i} = control{i}(:, 1:10:end);
 %end
 
 %for num_trials_mean = 206%1:100
-for num_trials_mean = 1:100
+%for num_trials_mean = 1:100
 %for num_trials_mean = 1:2
+for num_trials_mean = [1, 5, 10, 50, 100]
+%for num_trials_mean = 100
 
   % preprocess - calculate mean
   exp_data = {};
   con_data = {};
   for i = 1:numel(experiment)
-    several_trial_mean = nan(size(experiment{i}, 1) - num_trials_mean + 1, ...
-                             size(experiment{i}, 2));
-    for j = 0:(size(experiment{i}, 1) - num_trials_mean)
-        several_trial_mean(j + 1, :) = mean(experiment{i}(j + (1:num_trials_mean), :), 1);
+    %several_trial_mean = nan(size(experiment{i}, 1) - num_trials_mean + 1, ...
+    %                         size(experiment{i}, 2));
+    several_trial_mean = [];
+    %for j = 0:(size(experiment{i}, 1) - num_trials_mean)
+    for j = 0:num_trials_mean:(size(experiment{i}, 1) - num_trials_mean)
+        %several_trial_mean(j + 1, :) = mean(experiment{i}(j + (1:num_trials_mean), :), 1);
+        several_trial_mean((j / num_trials_mean) + 1, :) = mean(experiment{i}(j + (1:num_trials_mean), :), 1);
     end
     exp_data{i} = several_trial_mean;
   
[…]

### 2015-01-04 analysis/release/classify/test.m

@@ -15,12 +15,16 @@ for i = 1:numel(experiment)
   spec_num = 0;
   spec_den = 0;
 
+  %Guess = (data(:, 1:10:end) * model.B{i} > 0);
+  Guess = (data(:, 1:10:end) * model.B{i} > 0.5);
+
   for j = 1:size(data, 1)
     logp_exp = logmvnpdf(data(j, :), model.experiment_mean{i}, model.experiment_cov{i}, model.experiment_invcov{i}, model.experiment_logdetcov{i});
     logp_con = logmvnpdf(data(j, :), model.control_mean{i}, model.control_cov{i}, model.control_invcov{i}, model.control_logdetcov{i});
     %logp_exp = -sum((data(j, :) - model.experiment_mean{i}) .^ 2);
     %logp_con = -sum((data(j, :) - model.control_mean{i}) .^ 2);
     guess = (logp_exp > logp_con);
+    %guess = Guess(j);
     if (guess == isexp(j))
       num_correct = num_correct + 1;
     end

### 2015-01-04 analysis/release/classify/train.m

@@ -1,5 +1,6 @@
 function [ model ] = train(experiment, control)
 
+
 experiment_mean = cell(numel(experiment), 1);
 experiment_cov = cell(numel(experiment), 1);
 control_mean = cell(numel(control), 1);
@@ -15,13 +16,22 @@ for i = 1:numel(experiment)
 
   experiment_mean{i} = mean(experiment{i});
   experiment_cov{i} = cov(experiment{i});
-  experiment_invcov{i} = inv(experiment_cov{i} + 0.001 * eye(size(experiment_cov{i})));
+  experiment_invcov{i} = inv(experiment_cov{i} + 100 * eye(size(experiment_cov{i})));
   experiment_logdetcov{i} = logdet(experiment_cov{i});
 
   control_mean{i} = mean(control{i});
   control_cov{i} = cov(control{i});
-  control_invcov{i} = inv(control_cov{i} + 0.001 * eye(size(control_cov{i})));
+  control_invcov{i} = inv(control_cov{i} + 100 * eye(size(control_cov{i})));
   control_logdetcov{i} = logdet(control_cov{i});
+
+  X = [experiment{i}(:, 1:10:end);
+       control{i}(:, 1:10:end)];
+  N = size(X, 1);
+  Y = false(N, 1);
+  Y(1:size(experiment{1}, 1)) = true;
+  %B{i} = glmfit(X, Y, 'binomial', 'link', 'logit', 'constant', 'off');
+  B{i} = regress(Y, X);
+  %mean(Y == (X * B{i} > 0.5))
 end
 
 model.experiment_mean = experiment_mean;
@@ -33,6 +43,8 @@ model.control_mean    = control_mean;
 model.control_cov     = control_cov;
 model.control_invcov     = control_invcov;
 model.control_logdetcov  = control_logdetcov;
+
+model.B = B;
 
 end
 

### 2015-01-05 analysis/release/classify/classify_all.m
Formatting of plots

@@ -3,6 +3,8 @@ addpath(genpath('..'));
 file_experiment = '../data/subject1/vep/Thu_15_05_2014_11_57_42';
 file_control    = '../data/subject1/vep/Thu_15_05_2014_12_15_47';
 on_off = 'on';
-evaluate('../data/subject1/vep/Thu_15_05_2014_11_57_42', '../data/subject1/vep/Thu_15_05_2014_12_15_47', 'on')
+evaluate('../data/subject1/vep/Thu_15_05_2014_11_57_42', '../data/subject1/vep/Thu_15_05_2014_12_15_47', 'on', 'live')
+
+evaluate('../data/subject1/vep/Thu_15_05_2014_11_57_42', '../data/subject1/vep/Thu_15_05_2014_17_22_22', 'on', 'dead')
 end
 

### 2015-01-05 analysis/release/classify/evaluate.m

@@ -1,7 +1,7 @@
-function [ accuracy, sensitivity, specificity ] = evaluate(file_experiment, file_control, on_off)
+function [ accuracy, sensitivity, specificity ] = evaluate(file_experiment, file_control, on_off, control_type)
 
 experiment = load_vep(file_experiment, on_off);
-control = load_vep(file_control, on_off);
+[ control, digital_data, pre, post ] = load_vep(file_control, on_off);
 
 if strfind(file_experiment, 'subject1')
     subject_ID = 'subject1';
@@ -9,7 +9,7 @@ elseif strfind(file_experiment, 'subject2')
     subject_ID = 'subject2';
 end
 
-[ accuracy, sensitivity, specificity ] = evaluate_h(experiment, control, subject_ID);
+[ accuracy, sensitivity, specificity ] = evaluate_h(experiment, control, subject_ID, digital_data, pre, post, control_type);
 
 end
 

### 2015-01-05 analysis/release/classify/evaluate_h.m

@@ -1,4 +1,4 @@
-function [ accuracy, sensitivity, specificity ] = evaluate(experiment, control, subject_ID)
+function [ accuracy, sensitivity, specificity ] = evaluate(experiment, control, subject_ID, digital_data, pre, post, control_type)
 
 assert(numel(experiment) == numel(control));
 
@@ -17,7 +17,11 @@ specificity = [];
 
 % Get list of channels to plot and colors for each channel
 [ channelToPlot, CM ] = plot_settings();
+
+experiment = experiment([end, 1:(end-1)]);
+control = control([end, 1:(end-1)]);
 channelToPlot = channelToPlot([end, 1:(end-1)]);
+CM = CM([end, 1:(end-1)], :);
 
 chName = channelNames(channelToPlot);
 
@@ -29,7 +33,7 @@ chName = channelNames(channelToPlot);
 %for num_trials_mean = 206%1:100
 %for num_trials_mean = 1:100
 %for num_trials_mean = 1:2
-for num_trials_mean = [1, 5, 10, 50, 100]
+for num_trials_mean = [1, 2, 5, 10, 50, 100]
 %for num_trials_mean = 100
 
   % preprocess - calculate mean
@@ -56,40 +60,56 @@ for num_trials_mean = [1, 5, 10, 50, 100]
     end
     con_data{i} = several_trial_mean;
   end
-  exp_data
-  con_data
 
+  yl = [Inf, -Inf];
   for i = 1:numel(chName)
-    yl = [min(min([exp_data{i}; con_data{i}])),
-          max(max([exp_data{i}; con_data{i}]))];
+    yl = [min([min(min([exp_data{i}; con_data{i}])), yl(1)]),
+          max([max(max([exp_data{i}; con_data{i}])), yl(2)])];
   end
+  yl = [min([ yl(1), -yl(2)])
+        max([-yl(1),  yl(2)])];
 
   N = size(exp_data{1}, 2);
   f = figure;
   hold on;
   handle = [];
   for i = 1:numel(chName)
-    h = plot((1:N) / fs, exp_data{i}', 'Color', CM(i, :), 'LineWidth', 3);
+    if (size(exp_data{i}, 1) > 10)
+      h = plot(1000 * (1:N) / fs - pre, exp_data{i}(1:10, :)', 'Color', CM(i, :), 'LineWidth', 3);
[…]

### 2015-01-05 analysis/release/classify/load_vep.m

@@ -1,4 +1,4 @@
-function [ vep_data ] = load_vep(filename, on_off)
+function [ vep_data, digital_data, pre, post ] = load_vep(filename, on_off)
 
 if strfind(filename, 'subject1')
     subject_ID = 'subject1';
@@ -29,14 +29,19 @@ if (nargin < 5) || isempty(preEventPlot_sec)
     %preEventPlot_sec = 0.05;
     %preEventPlot_sec = -0.05;
     preEventPlot_sec = -0.005;
+    %preEventPlot_sec = 0.05;
 end
 
 % Default postEventPlot_sec is to end plot 0.1 seconds (100 ms) after event
 if (nargin < 6) || isempty(postEventPlot_sec)
     %postEventPlot_sec = 0.5;
     %postEventPlot_sec = 0.1;
-    postEventPlot_sec = 0.08;
+    %postEventPlot_sec = 0.08;
+    postEventPlot_sec = 0.1;
 end
+
+pre = 1000 * preEventPlot_sec;
+post = 1000 * postEventPlot_sec;
 
 % Default filters is to only use high-pass filter
 % Note: allow filters to be empty (do not enforce default)
@@ -105,6 +110,7 @@ event_index_LED_ONOFF = eval(['event_index_LED_' upper(on_off)]);
 
 %% process each channel
 vep_data = cell(size(data, 1), 1);
+digital_data = cell(size(data, 1), 1);
 for ii = 1:size(data, 1)
 
     chDataRaw = data(ii, :);                  % get unprocessed analog channel from electrode
@@ -118,6 +124,7 @@ for ii = 1:size(data, 1)
 
     % matrix of all single trial responses for the single channel stored in chData, aligned to the on or off edge
     chData_all_single_trial_collection = [];
+    digital = [];
 
     %for each LED on/off event, snip out that segment and append it as a row in chData_all_single_trial_responses
     for jj=2:length(event_index_LED_ONOFF)-1,
@@ -140,8 +147,11 @@ for ii = 1:size(data, 1)
         chData_all_single_trial_collection(end+1, 1:totalEventPlot_samples)...
             = detrend(chData((event_index_LED_ONOFF(jj)-preEventPlot_samples):...
                             (event_index_LED_ONOFF(jj)+postEventPlot_samples)));
+        digital = cleanDigitalIn((event_index_LED_ONOFF(jj)-preEventPlot_samples):...
[…]

### 2015-07-04 analysis/figures/paper_figures.tex
Add old changes

@@
 \begin{center}
-\includegraphics[scale=1.0]{surgical_methods.pdf}
+\includegraphics[scale=1.0]{../../../../Dropbox/Bryan_Easter/paper_figures/anatomy v1.pdf}
 \caption{Surgical approach, anatomy imaging.}
@@
 \begin{tabular}{cc}
-\includegraphics[scale=0.5]{impedance.pdf}
+\raisebox{-0.5\height}{\includegraphics[scale=0.4]{../../../../Dropbox/Bryan_Easter/paper_figures/impedance_characterization-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.4]{../../../../Dropbox/ExtractImpedancesFromDTAGAMRYFiles/impedance-crop.pdf}} \\
+\vspace{0.5cm} \\
+\raisebox{-0.5\height}{\includegraphics[scale=0.4]{../../../../Dropbox/Bryan_Easter/paper_figures/system_characterization-crop.pdf}} &
+\raisebox{-0.5\height}{\includegraphics[scale=0.4]{../../../../Dropbox/analyzesinewaves/system-crop.pdf}}
 \end{tabular}

### 2015-07-04 analysis/config/make_legend.m

@@ -2,26 +2,17 @@ function [ f ] = make_legend()
   f = figure;
   hold on;
 
-  CM = [hex2dec('e9'), hex2dec('00'), hex2dec('3a');
-        hex2dec('ff'), hex2dec('ba'), hex2dec('00');
-        hex2dec('40'), hex2dec('40'), hex2dec('ff');
-        hex2dec('58'), hex2dec('e0'), hex2dec('00');
-        hex2dec('b0'), hex2dec('00'), hex2dec('b0');
-        hex2dec('00'), hex2dec('00'), hex2dec('00')];
-  CM = CM/256;
+  [ channelToPlot, CM ] = plot_settings();
 
-  channelToPlot = [2,3,5,7,8];
-  channelToPlot = [2,3,5,7,8,9];
-  channelNames_VEP = {'Disconnected','Endo','Mid head','Disconnected','Right Eye','Right Leg','Back Head','Left Eye','Bottom Precordial','Top Precordial'};
+  [ channelNames, gtechGND, earth ] = rabbit_information('10rabbit_may_15_2014');
 
 
   legends = [];
   for i = 1:numel(channelToPlot)
-    legends = [legends plot(0, 0, 'Color', CM(i, :), 'linewidth', 3)];
+    legends = [legends plot(0, 0, 'Color', CM(i, :), 'linewidth', 2)];
   end
-legends
-  legend(legends, channelNames_VEP{channelToPlot})
-  %legend(channelNames_VEP{channelToPlot})
+  legends = [legends plot(0, 0, 'Color', 'black', 'linewidth', 2)];
+  legend(legends, {channelNames{channelToPlot}, 'Cardiac'}, 'fontsize', 10);
 
   axis off;
   set(legends, 'visible', 'off');

### 2015-07-04 analysis/qrs/qrs_figure.m

@@ -41,13 +41,13 @@ margins = 100; % extra space for labels
 position = [0 0 (width + 2 * margins) (height + 2 * margins)];
 
 % Open invisible screen for figure
-f_start = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]);
-f_end = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]);
-f1 = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]);
-f2 = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]);
-f3 = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]);
-f4 = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]);
-f5 = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]);
+f_start = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]); box on;
+f_end = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]); box on;
+f1 = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]); box on;
+f2 = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]); box on;
+f3 = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]); box on;
+f4 = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]); box on;
[…]

### 2015-07-04 analysis/release/cardiac/cardiac_figure.m

@@ -110,12 +110,12 @@ cardiac_data = run_filters(cardiac_data, cardiac_filters);             % filter 
 %% Preparing figures
 
 % Open invisible screens for figures
-f_start = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]); box on;
-f_end   = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]); box on;
-f1      = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]); box on;
-f2      = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]); box on;
-f3      = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]); box on;
-f4      = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'off'); axes('units', 'pixel', 'position', [margins margins width height]); box on;
+f_start = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'on'); axes('units', 'pixel', 'position', [margins margins width height]); box on;
+f_end   = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'on'); axes('units', 'pixel', 'position', [margins margins width height]); box on;
+f1      = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'on'); axes('units', 'pixel', 'position', [margins margins width height]); box on;
+f2      = figure('Color',[1 1 1],'units','pixels','position',position, 'visible', 'on'); axes('units', 'pixel', 'position', [margins margins width height]); box on;
[…]

### 2015-07-04 analysis/release/classify/classify_all.m

@@ -1,4 +1,4 @@
-functio ni ] = classify_all()
+function [ ] = classify_all()
 addpath(genpath('..'));
 
 file_experiment = '../data/subject1/vep/Thu_15_05_2014_11_57_42';

### 2015-07-04 analysis/release/classify/evaluate.m

@@ -1,12 +1,12 @@
 function [ accuracy, sensitivity, specificity ] = evaluate(file_experiment, file_control, on_off, control_type)
 
-%experiment = load_vep_decimate(file_experiment, on_off);
-%%[ control, digital_data, pre, post, decimate_rate ] = load_vep(file_control, on_off);
-%[ control, digital_data, pre, post, decimate_rate ] = load_vep_decimate(file_control, on_off);
+experiment = load_vep_decimate(file_experiment, on_off);
+%[ control, digital_data, pre, post, decimate_rate ] = load_vep(file_control, on_off);
+[ control, digital_data, pre, post, decimate_rate ] = load_vep_decimate(file_control, on_off);
 
-experiment = load_vep(file_experiment, on_off);
-[ control, digital_data, pre, post ] = load_vep(file_control, on_off);
-decimate_rate = 1;
+%experiment = load_vep(file_experiment, on_off);
+%[ control, digital_data, pre, post ] = load_vep(file_control, on_off);
+%decimate_rate = 1;
 
 if strfind(file_experiment, 'subject1')
     subject_ID = 'subject1';

### 2015-07-04 analysis/release/classify/evaluate_h.m

@@ -162,6 +162,8 @@ for num_trials_mean = 1:10
   %experiment_test  = true(size(exp_data{1}, 1), 1);
   %control_train    = true(size(con_data{1}, 1), 1);
   %control_test     = true(size(con_data{1}, 1), 1);
+  time_slots = [190:250, 590:700];
+  time_slots = [16:18, 22:24, 25:27];
   
   % Train
   for i = 1:numel(exp_data)
@@ -169,8 +171,8 @@ for num_trials_mean = 1:10
   
     %e_train{i} = exp_data{i}(experiment_train, :);
     %c_train{i} = con_data{i}(control_train, :);
-    e_train{i} = exp_data{i}(experiment_train, [190:250, 590:700]);
-    c_train{i} = con_data{i}(control_train, [190:250, 590:700]);
+    e_train{i} = exp_data{i}(experiment_train, time_slots);
+    c_train{i} = con_data{i}(control_train, time_slots);
   end
   model = train(e_train, c_train);
   
@@ -182,8 +184,8 @@ for num_trials_mean = 1:10
   
     %e_test{i} = exp_data{i}(experiment_test, :);
     %c_test{i} = con_data{i}(control_test, :);
-    e_test{i} = exp_data{i}(experiment_test, [190:250, 590:700]);
-    c_test{i} = con_data{i}(control_test, [190:250, 590:700]);
+    e_test{i} = exp_data{i}(experiment_test, time_slots);
+    c_test{i} = con_data{i}(control_test, time_slots);
   end
   
   [acc, sen, spec] = test(model, e_test, c_test);

### 2015-07-04 analysis/release/generate_all.m

@@ -17,22 +17,38 @@ addpath('ssavep');
 addpath('util');
 addpath('vep');
 
+set(0,'defaultAxesFontName', 'SansSerif');
+set(0,'defaultTextFontName', 'SansSerif');
+set(0,'DefaultAxesFontSize', 20);
+set(0,'DefaultTextFontSize', 20);
+
 if ~exist('figures', 'dir')
     mkdir(pwd(),  'figures');
 end
 
-make_legend();
+%make_legend(true);
+%
+%plot_hypothesis_vep();
+%plot_hypothesis_vep_control();
+%
+%plot_hypothesis_ssaep();
+%plot_hypothesis_ssavep_control();
+%plot_hypothesis_ssvep();
 
-plot_all_vep('subject1');
-plot_all_vep('subject1', 2, [3], false);
-plot_all_ssavep('ssaep', 'subject1');
-plot_all_ssavep('ssvep', 'subject1');
+%plot_all_vep('subject1', 1);
+%plot_all_vep('subject1', 4);
+plot_all_vep('subject1', 5);
+%plot_all_vep('subject1', 1, [3], false);
+%plot_all_ssavep('ssaep', 'subject1');
+%plot_all_ssavep('ssvep', 'subject1');
 
-plot_all_vep('subject2');
-plot_all_ssavep('ssaep', 'subject2');
-plot_all_ssavep('ssvep', 'subject2');
+%plot_all_vep('subject2', 1);
+%plot_all_vep('subject2', 4);
+plot_all_vep('subject2', 5);
+%plot_all_ssavep('ssaep', 'subject2');
+%plot_all_ssavep('ssvep', 'subject2');
 
-cardiac_figure('subject1', 'vep', 3, [10, 11]); % Use subject 1 vep at mid-basilar for plot
+%cardiac_figure('subject1', 'vep', 3, [10, 11]); % Use subject 1 vep at mid-basilar for plot
 
 end
 

### 2015-07-04 analysis/release/ssavep/plot_all_ssavep.m

@@ -95,9 +95,33 @@ for i = index_list
     end
 
     % Plot SSAEP/SSVEP response
-    plot_ssavep(data, cleanDigitalIn, filename, ssavep, fs, cardiac_data, windlengthSeconds, noverlapPercent, filters, cardiac_filters, CM, channelNames(channelToPlot), comments(i));
+    if (strcmp(filename, 'Tue_06_05_2014_11_37_22'))
+        [ data2, cleanDigitalIn2 ] = load_data([pathname 'Tue_06_05_2014_11_31_23'], numChannels);
+        data_all2 = load_data([pathname 'Tue_06_05_2014_11_31_23'], numChannels);                % data from all channels
+        cleanDigitalIn2 = (data_all2(digitalCh, :) > 0);                         % binary digital in channel
+        data2 = data_all2(channelToPlot, :);                                     % data for relevant channels
+        cardiac_data2 = []; % empty array if no cardiac artifact filtering
+        if (filter_cardiac)
+            % cardiac channel for removal of cardiac artifacts
+            cardiac_data2 = data_all2(strcmp(channelNames, 'Bottom Precordial'), :);
+        end
+        plot_ssavep(data, cleanDigitalIn, filename, ssavep, fs, cardiac_data, windlengthSeconds, noverlapPercent, filters, cardiac_filters, CM, channelNames(channelToPlot), comments(i), data2, cleanDigitalIn2, cardiac_data2);
+    else if (strcmp(filename, 'Tue_06_05_2014_11_42_15'))
+        [ data2, cleanDigitalIn2 ] = load_data([pathname 'Tue_06_05_2014_11_39_46'], numChannels);
+        data_all2 = load_data([pathname 'Tue_06_05_2014_11_39_46'], numChannels);                % data from all channels
+        cleanDigitalIn2 = (data_all2(digitalCh, :) > 0);                         % binary digital in channel
+        data2 = data_all2(channelToPlot, :);                                     % data for relevant channels
+        cardiac_data2 = []; % empty array if no cardiac artifact filtering
+        if (filter_cardiac)
+            % cardiac channel for removal of cardiac artifacts
+            cardiac_data2 = data_all2(strcmp(channelNames, 'Bottom Precordial'), :);
+        end
[…]

### 2015-07-04 analysis/release/ssavep/plot_ssavep.m

@@ -1,4 +1,4 @@
-function [ fgh ] = plot_ssavep(data, cleanDigitalIn, name, ssavep, fs, cardiac_data, windlengthSeconds, noverlapPercent, filters, cardiac_filters, CM, channelNames, comment)
+function [ fgh ] = plot_ssavep(data, cleanDigitalIn, name, ssavep, fs, cardiac_data, windlengthSeconds, noverlapPercent, filters, cardiac_filters, CM, channelNames, comment, data2, cleanDigitalIn2, cardiac_data2)
 %PLOT_SSAVEP  Plots the SSAEP/SSVEP response for a single run.
 %
 % FGH = PLOT_SSAVEP(DATA, CLEANDIGITALIN, NAME, EXPERIMENT, FS, ...
@@ -53,6 +53,10 @@ function [ fgh ] = plot_ssavep(data, cleanDigitalIn, name, ssavep, fs, cardiac_d
 % easier to use PLOT_ALL_SSAVEP.
 %
 % See also PLOT_ALL_SSAVEP.
+set(0,'defaultAxesFontName', 'SansSerif');
+set(0,'defaultTextFontName', 'SansSerif');
+set(0,'DefaultAxesFontSize', 20);
+set(0,'DefaultTextFontSize', 20);
 
 
 %% Constants
@@ -63,11 +67,13 @@ height = 225;  % height of figure (just plot itself, not labels)
 margins = 100; % extra space for labels
 
 % Axes for figure
-if (strcmp(ssavep, 'ssvep'))
-    xrange = ([0 800] / 1000);                    % x-axis limits for ssvep
-else
-    xrange = ([0 4800] / 1000);                   % x-axis limits for ssaep
-end
+%if (strcmp(ssavep, 'ssvep'))
+%    xrange = ([0 800] / 1000);                    % x-axis limits for ssvep
+%else
+%    xrange = ([0 4800] / 1000);                   % x-axis limits for ssaep
+%end
+xrange = [0 4800];
+%xrange = [0 1000];
 yrange = (10 .^ [-1 3]);                          % y-axis limits
 xticks = linspace(xrange(1), xrange(2), 5);       % tick marks on x-axis
 yticks = logspace(log10(yrange(1)), log10(yrange(2)), 5); % tick marks on y-axis
@@ -82,6 +88,16 @@ threshold_harmonics = 3; % Threshold to be considered a harmonic
 
 % whether or not to plot points on harmonics
[…]

### 2015-07-04 analysis/release/util/load_data.m

@@ -22,7 +22,7 @@ function [ data, samples ] = load_data(filename, num_channels)
 %% Constants
 sample_size = 4;      % number of bytes in each sample
 precision = 'single'; % type of variable to read as
-
+%filename
 %% Check that data is complete
 F = dir(filename);                                     % get file information
 bytes = F.bytes;                                       % file size in bytes

### 2015-07-04 analysis/release/util/make_legend.m

@@ -29,6 +29,7 @@ hold on;
 
 % Plot garbage to have something for the legend
 legends = [];
+  legends = [legends plot(0, 0, 'Color', [0 0.75 0], 'linewidth', linewidth)];
 for i = 1:numel(channelToPlot)
   legends = [legends plot(0, 0, 'Color', CM(i, :), 'linewidth', linewidth)];
 end
@@ -38,7 +39,8 @@ end
 
 % make the legend
 if (nargin >= 1) && include_cardiac
-    legend(legends, {channelNames{channelToPlot}, 'Cardiac'}, 'fontsize', fontsize);
+    %legend(legends, {channelNames{channelToPlot}, 'Cardiac'}, 'fontsize', fontsize);
+    legend(legends, {'Precordical', channelNames{channelToPlot}, 'LED Status'}, 'fontsize', fontsize);
 else
     legend(legends, channelNames(channelToPlot), 'fontsize', fontsize);
 end
@@ -49,8 +51,8 @@ set(legends, 'visible', 'off');
 set(gca, 'visible', 'off');
 
 % Save figure
-save2pdf('figures/legend.pdf', f, 1200);
-plot2svg('figures/legend.svg', f, 'png');
+save2pdf('figures/legend_cardiac.pdf', f, 1200);
+plot2svg('figures/legend_cardiac.svg', f, 'png');
 
 end
 

### 2015-07-04 analysis/release/vep/plot_vep.m

@@ -74,9 +74,15 @@ margins = 100; % extra space for labels
 
 % Axes for figure
 xrange = [-preEventPlot_sec, postEventPlot_sec] * 1000; % x-axis limits for figure
-yrange = [-26 26];                                      % y-axis limits for figure
+%yrange = [-26 26];                                      % y-axis limits for figure
+%yrange = [-100 100];                                      % y-axis limits for figure
+%yrange = [-150 150];                                      % y-axis limits for figure
+yrange = [-70 70];                                      % y-axis limits for figure
 xticks = [-50, 0, 50, 100];                             % tick marks on x-axis
-yticks = [-26, -13, 0, 13, 26];                         % tick marks on y-axis
+%yticks = [-26, -13, 0, 13, 26];                         % tick marks on y-axis
+%yticks = [-100, -50, 0, 50, 100];                         % tick marks on y-axis
+%yticks = [-150, -75, 0, 75, 150];                         % tick marks on y-axis
+yticks = [-70, -35, 0, 35, 70];                         % tick marks on y-axis
 
 % Figure formatting
 font_size = 20; % font size of figure labels
@@ -127,9 +133,6 @@ hold on; % Allow all channels to be shown
 
 
 %% Miscellaneous preparation for figure
-
-% prepare to accumulate plot line handles for the figure legend
-plotline_handles = zeros(size(channelNames));
 
 % filter cardiac data, if cardiac data is available
 if (~isempty(cardiac_data))
@@ -183,7 +186,9 @@ for ii = 1:size(data, 1)
         digitalInDataPlot = digitalInDataPlot + yrange(1) + (1 - dig_height) / 2 * abs(yrange(2) - yrange(1));
 
         % digital in plotted in black
-        plot(time_axis, digitalInDataPlot, 'k', 'linewidth', 2);
+        if (jj == 2)
+            plot(time_axis, digitalInDataPlot, 'k', 'linewidth', 2);
+        end
 
         % copy relevant segment into list
         % Note: detrend may not really be needed if the data is high-passed
@@ -195,26 +200,52 @@ for ii = 1:size(data, 1)
 
 
     %% compute and plot the average event-aligned LED ON response for this channel
-    if (publication_quality == 4)
-        % Version of figure showing all trials
[…]

### 2015-07-04 analysis/ssaep/plot_all_ssaep.m

@@ -1,4 +1,4 @@
-%plot_all_ssaep.m
+%plot_all_vep.m
 %
 %Authors: M. Ebrahimi, L. Srinivasan / nspl.org
 %
@@ -17,13 +17,22 @@
 %	
 %	The analysis code assumes a fixed sampling rate of 9600 Hz and digital input channel # of 65 (both designated in arduino_vep.m)
 
+clear;
+close all;
+addpath('../utilities')
 
 %///////////////////////////////////////////////
 % START BLOCK: Hardcoded variables
 %///////////////////////////////////////////////
+rabbit_ID = '1rabbit_dec_10_2012';
+rabbit_ID = '2rabbit_jan_23_2013';
+rabbit_ID = '4rabbit_feb_5_2014';
+rabbit_ID = '5rabbit_mar_4_2014';
+rabbit_ID = '6rabbit_apr_11_2014';
 %rabbit_ID = '7rabbit_apr_15_2014';                                         %'7rabbit_apr_15_2014' corresponds to the experiment performed 4/15/14
-rabbit_ID = '8rabbit_apr_24_2014';
-%rabbit_ID = '9rabbit_may_6_2014';
+%rabbit_ID = '8rabbit_apr_24_2014';
+rabbit_ID = '9rabbit_may_6_2014';
+rabbit_ID = '10rabbit_may_15_2014';
 
 decimate_factor = 10;                                                      % decimate the data to speed up plotting (decimate_factor = 1 is no decimation; 10 is reasonable)
                                                                            %(this Matlab function implements proper downsampling using anti-aliasing, with decimate.m).
@@ -54,12 +63,21 @@ pathname_comments = ['../../../../data/easter/' rabbit_ID '/neuro/neuro_experime
 pathname_matdata = ['../../../../data/easter/' rabbit_ID '/neuro/matlab_data/ssaep/'];
 
 %Channel labels during VEP for all rabbits (5,6,7, etc.)
-switch rabbit_ID
-    case {'7rabbit_apr_15_2014', '8rabbit_apr_24_2014','9rabbit_may_6_2014'}
         channelNames_VEP = {'Disconnected','Endo','Mid head','Disconnected','Right Eye','Right Leg','Back Head','Left Eye','Bottom Precordial','Top Precordial'};
[…]

### 2015-07-04 analysis/ssaep/publish_ssaep_v2.m

@@ -2,33 +2,35 @@
 fs = 9600;
 windlengthSeconds = 2;
 windlength = windlengthSeconds * fs;
-noverlapPercent = 0.45;%windlength * 0.25;
-noverlap = windlength * noverlapPercent;
+noverlapPercent = 0.25;%windlength * 0.25; % number overlap percent
+noverlap = windlength * noverlapPercent; % number overlap (timesteps)
 
 % ask the user to select the data file
 %run('../loaddata.m');
 
-fid = fopen([pathname filename], 'r');
-digitalinCh = 65;
-fseek(fid, 4*(digitalinCh-1), 'bof');
-dataColumn = fread(fid, Inf, 'single', 4*64);
-time_axis = (0:length(dataColumn)-1)*1.0/fs;
-figure;plot(time_axis,dataColumn);
+time_axis = (0:length(dataColumnDig)-1)*1.0/fs;
+%figure;plot(time_axis,dataColumnDig);
 
-tmp = (dataColumn>0);
-t1 = diff(tmp);
-t2 = find(t1==1);
-t3 = find(t1==-1);
+tmp = (dataColumnDig>0); % true when experiment is on, false when off
+t1 = diff(tmp); % -1: experiment turns off, 0: no change, 1: experiment turns on
+t2 = find(t1==1); % first time when led turns on (experiment starts)
+t3 = find(t1==-1); % last time when led turns off (experiment ends)
 
 if isempty(t3)
-    t3 = length(dataColumn);
+    t3 = length(dataColumnDig);
 end
 
 cutSecondsBegining = 10;
 cutSecondsEnd = 15;
 
 cutLengthB = t2; %fs * cutSecondsBegining;
-cutLengthE = length(dataColumn); %fs * cutSecondsEnd;
+%cutLengthE = length(dataColumn); %fs * cutSecondsEnd;
+cutLengthE = t3;
+
+assert(numel(cutLengthB) == 1);
+assert(numel(cutLengthE) == 1);
+
+assert(cutLengthB < cutLengthE);
 
 if strcmp(rabbit_ID, '9rabbit_may_6_2014')
     if isempty(t2),
@@ -48,15 +50,32 @@ if strcmp(rabbit_ID, '9rabbit_may_6_2014')
     
 end
 
[…]

### 2015-07-04 analysis/ssvep/plot_all_ssvep.m

@@ -17,13 +17,22 @@
 %	
 %	The analysis code assumes a fixed sampling rate of 9600 Hz and digital input channel # of 65 (both designated in arduino_vep.m)
 
+clear;
+close all;
+addpath('../utilities')
 
 %///////////////////////////////////////////////
 % START BLOCK: Hardcoded variables
 %///////////////////////////////////////////////
+rabbit_ID = '1rabbit_dec_10_2012';
+rabbit_ID = '2rabbit_jan_23_2013';
+rabbit_ID = '4rabbit_feb_5_2014';
+rabbit_ID = '5rabbit_mar_4_2014';
+%rabbit_ID = '6rabbit_apr_11_2014';
 %rabbit_ID = '7rabbit_apr_15_2014';                                         %'7rabbit_apr_15_2014' corresponds to the experiment performed 4/15/14
-rabbit_ID = '8rabbit_apr_24_2014';
-%rabbit_ID = '9rabbit_may_6_2014';
+%rabbit_ID = '8rabbit_apr_24_2014';
+rabbit_ID = '9rabbit_may_6_2014';
+%rabbit_ID = '10rabbit_may_15_2014';
 
 decimate_factor = 10;                                                      % decimate the data to speed up plotting (decimate_factor = 1 is no decimation; 10 is reasonable)
                                                                            %(this Matlab function implements proper downsampling using anti-aliasing, with decimate.m).
@@ -54,14 +63,21 @@ pathname_comments = ['../../../../data/easter/' rabbit_ID '/neuro/neuro_experime
 pathname_matdata = ['../../../../data/easter/' rabbit_ID '/neuro/matlab_data/ssvep/'];
 
 %Channel labels during VEP for all rabbits (5,6,7, etc.)
+        channelNames_VEP = {'Disconnected','Endo','Mid head','Disconnected','Right Eye','Right Leg','Back Head','Left Eye','Bottom Precordial','Top Precordial'};
+        gtechGND = 'Nose';
+        earth = 'Left Leg';
 switch rabbit_ID
     case '7rabbit_apr_15_2014'
     case '8rabbit_apr_24_2014'
     case '9rabbit_may_6_2014'
         channelNames_VEP = {'Disconnected','Endo','Mid head','Disconnected','Right Eye','Right Leg','Back Head','Left Eye','Bottom Precordial','Top Precordial'};
[…]

### 2015-07-04 analysis/ssvep/publish_ssvep_v2.m

@@ -2,19 +2,19 @@
 fs = 9600;
 windlengthSeconds = 2;
 windlength = windlengthSeconds * fs;
-noverlapPercent = 0.45;%windlength * 0.25;
-noverlap = windlength * noverlapPercent;
+noverlapPercent = 0.25;%windlength * 0.25; % number overlap percent
+noverlap = windlength * noverlapPercent; % number overlap (timesteps)
 
 % ask the user to select the data file
 %run('../loaddata.m');
 
 time_axis = (0:length(dataColumnDig)-1)*1.0/fs;
-figure;plot(time_axis,dataColumnDig);
+%figure;plot(time_axis,dataColumnDig);
 
-tmp = (dataColumnDig>0);
-t1 = diff(tmp);
-t2 = find(t1==1);
-t3 = find(t1==-1);
+tmp = (dataColumnDig>0); % true when experiment is on, false when off
+t1 = diff(tmp); % -1: experiment turns off, 0: no change, 1: experiment turns on
+t2 = find(t1==1); % first time when led turns on (experiment starts)
+t3 = find(t1==-1); % last time when led turns off (experiment ends)
 
 if isempty(t3)
     t3 = length(dataColumnDig);
@@ -26,15 +26,36 @@ cutSecondsEnd = 15;
 cutLengthB = t2; %fs * cutSecondsBegining;
 cutLengthE = t3; %fs * cutSecondsEnd;
 
+assert(numel(cutLengthB) == 1);
+assert(numel(cutLengthE) == 1);
+
+assert(cutLengthB < cutLengthE);
+
+%channelToPlot = [1,4,2,3,5,7,8];
 channelToPlot = [2,3,5,7,8];
 channels_plotted = [];
 
+hp = fdesign.highpass('Fst,Fp,Ast,Ap',(2.0),(10.0),90,1,fs);             %highpass filter; passband 90 Hz, stopband 105 Hz, 1dB passband ripple, 90 dB stopband attenuation, sampling frequency fs, butterworth 
+hpf = design(hp, 'butter');
+
 % choose the colormap for the plots
+%CM = [hex2dec('00'), hex2dec('00'), hex2dec('00');
+%      hex2dec('00'), hex2dec('00'), hex2dec('00');
+%      hex2dec('e9'), hex2dec('00'), hex2dec('3a');
+%      hex2dec('ff'), hex2dec('ba'), hex2dec('00'); 
[…]

### 2015-07-09 analysis/release/ssavep/plot_all_ssavep_baseline.m
Code to plot baseline freq

@@ -1,0 +1,137 @@
+function [] = plot_all_ssavep(ssavep, subject_ID, index_list, filter_cardiac, filters, cardiac_filters)
+%PLOT_ALL_SSAVEP  Loads and plots SSAEP and SSVEP frequency responses.
+%
+%   PLOT_ALL_SSAVEP(SSAVEP, SUBJECT_ID, INDEX_LIST, FILTERS, CARDIAC_FILTERS)
+%
+%   SSAVEP is a string that selects which experiment to plot (ssaep or ssvep).
+%
+%   SUBJECT_ID is a string with the name of the subject (subject1 or subject2).
+%
+%   INDEX_LIST is a list of indices to plot for this experiment on this
+%   subject (ordered based on time).
+%     [default: plot all recordings for this experiment on this subject]
+%
+%   FILTER_CARDIAC is a boolean value that indicates whether or not to perform
+%   removal of cardiac artifacts.
+%     [default: true]
+%
+%   FILTERS is a list of filters to apply to all analog channels other than
+%   the cardiac channel.
+%     [default: only high-pass filter]
+%
+%   CARDIAC_FILTERS is a list of filters to apply to the cardiac channel.
+%     [default: only high-pass filter]
+
+% Output:
+%
+%   No return value.
+%
+%   Figures are saved as FIG, PDF, and SVG files in figures/.
+%
+% See also PLOT_SSAVEP.
+
+
+%% Constants
+
+% Information about how to compute power spectral density
+windlengthSeconds = 2;  % window length in seconds
+noverlapPercent = 0.25; % number overlap percent
+
+
+%% Preliminary information about data
+
+% Information about recording 
+[ numChannels, digitalCh, fs, channelNames, GND, earth ] = subject_information(subject_ID);
+
+% Load names of data files and experiment log
+[ pathname, experiment_log ] = get_pathname(subject_ID, ssavep);
+[ files, comments ] = get_information(pathname, experiment_log, ssavep);
+if (strcmp(subject_ID, 'subject1') == 1)
+  pathname = 'data/subject1/ssvep/';
+  files = {'Thu_15_05_2014_12_08_22', 'Thu_15_05_2014_16_38_47'};
+else
+  pathname = 'data/subject2/ssvep/';
+  files = {'Tue_06_05_2014_11_14_51', 'Tue_06_05_2014_15_48_24'};
+end
+
+% Get list of channels to plot and colors for each channel
+[ channelToPlot, CM ] = plot_settings();
+
+
[…]

### 2015-07-09 analysis/release/ssavep/plot_ssavep_baseline.m

@@ -1,0 +1,365 @@
+function [ fgh ] = plot_ssavep_baseline(data, fgh, cleanDigitalIn, name, ssavep, fs, cardiac_data, windlengthSeconds, noverlapPercent, filters, cardiac_filters, CM, channelNames, comment, data2, cleanDigitalIn2, cardiac_data2)
+%PLOT_SSAVEP  Plots the SSAEP/SSVEP response for a single run.
+%
+% FGH = PLOT_SSAVEP(DATA, CLEANDIGITALIN, NAME, EXPERIMENT, FS, ...
+%                   CARDIAC_DATA, WINDLENGTHSECONDS, NOVERLAPPERCENT, ...
+%                   FILTERS, CARDIAC_FILTERS, CM, CHANNELNAMES, COMMENT)
+%
+% Parameters:
+%
+%   DATA is a matrix of values from the analog channels connected to the
+%   electrodes. Each of the rows corresponds to one of the channels. Each of
+%   the columns corresponds to a sample from one of the timesteps.
+%
+%   CLEANDIGITALIN is a binary vector of the digital in channel (whether or not
+%   the LED is on at each time step).
+%
+%   NAME is a string of the filename to save to (should not include suffix).
+%
+%   SSAVEP is a string that selects which experiment to plot (ssaep or ssvep).
+%
+%
+%   CARDIAC_DATA is a vector of the values from the analog channel connected
+%   to the cardiac electrode. This vector should be empty if removal of
+%   cardiac artifacts is not desired.
+%
+%   WINDLENGTHSECONDS is the length of the windows in seconds to be used for
+%   calculating the power spectral density.
+%
+%   NOVERLAPPERCENT is the fraction of windows that overlap for calculating
+%   the power spectral density.
+%
+%   FILTERS is a list of filters to apply to all analog channels other than
+%   the cardiac channel.
+%
+%   CARDIAC_FILTERS is a list of filters to apply to the cardiac channel.
+%
+%   CM is a matrix of the colors for each of the channels in the plot. Each
+%   row corresponds to one of the channels, and the three columns are the RGB
+%   values for the color.
+%
+%   CHANNELSNAMES is a list of strings for the names of the channels. This is not
+%   currently used, but is available to use in the legend.
+%
+%   COMMENT is a string that is the line from the experiment log corresponding
+%   to this run. This is not currently used, but is available to use as the
[…]

### 2015-07-16 analysis/release/ssavep/plot_all_ssavep_baseline.m
Fig changes

@@ -46,16 +46,29 @@ noverlapPercent = 0.25; % number overlap percent
 % Load names of data files and experiment log
 [ pathname, experiment_log ] = get_pathname(subject_ID, ssavep);
 [ files, comments ] = get_information(pathname, experiment_log, ssavep);
-if (strcmp(subject_ID, 'subject1') == 1)
-  pathname = 'data/subject1/ssvep/';
-  files = {'Thu_15_05_2014_12_08_22', 'Thu_15_05_2014_16_38_47'};
-else
-  pathname = 'data/subject2/ssvep/';
-  files = {'Tue_06_05_2014_11_14_51', 'Tue_06_05_2014_15_48_24'};
-end
+comments = {'1', '2', '3', '4'};
+comments = {'11:14:51 - SSVEP 40 Hz, experiment, electrode = X-pedion-10 @ catheter tip, position = basilar tip', '11:23:01 - SSVEP 40 Hz, live-animal-control, electrode = X-pedion-10 @ catheter tip, position = basilar tip', '15:48:24 - SSVEP 40 hz, experiment, electrode =  guidewire @ catheter tip, position = basilar tip', '15:48:24 - SSVEP 40 hz, experiment, electrode =  guidewire @ catheter tip, position = basilar tip', '15:48:24 - SSVEP 40 hz, experiment, electrode =  guidewire @ catheter tip, position = basilar tip', '15:48:24 - SSVEP 40 hz, experiment, electrode =  guidewire @ catheter tip, position = basilar tip'}
 
 % Get list of channels to plot and colors for each channel
 [ channelToPlot, CM ] = plot_settings();
+endo = strcmp(channelNames(channelToPlot), 'Endo');
+
+CMi = CM;
+CMi(endo, :) = [1.0 0.0 0.0];
+CMi(~endo, :) = repmat([0.0 1.0 0.0], sum(~endo), 1);
+CMf = CM;
+CMf(endo, :) = [0.0 0.0 0.0];
+CMf(~endo, :) = repmat([0.0 0.0 1.0], sum(~endo), 1);
+
+if (strcmp(subject_ID, 'subject1') == 1)
+  pathnames = {'data/subject1/ssvep/', 'data/subject1/ssaep/', 'data/subject1/ssaep/', 'data/subject1/ssvep/', 'data/subject1/ssaep/', 'data/subject1/ssaep/'};
[…]

### 2015-07-16 analysis/release/ssavep/plot_hypothesis_ssaep.m

@@ -1,0 +1,105 @@
+clear;
+close all;
+
+% Figure window size
+width = 275;   % width of figure (just plot itself, not labels)
+height = 225;  % height of figure (just plot itself, not labels)
+margins = 100; % extra space for labels
+
+%% Create the figure
+
+% make the figure with white background, with fixed size (in pixels) and invisible
+%fgh = figure('Color',[1 1 1],'units','pixels','position',[0 0 (width + 2 * margins) (height + 2 * margins)], 'visible', 'off');
+fgh = figure('Color',[1 1 1],'units','pixels','position',[0 0 (width + 2 * margins) (height + 2 * margins)], 'visible', 'on');
+% make axes with correct margins
+axes('units', 'pixel', 'position', [margins margins width height]);
+hold on; % Allow all channels to be shown
+box on;
+
+
+% Get list of channels to plot and colors for each channel
+[ channelToPlot, CM ] = plot_settings();
+
+f_harmonic = 0:0.001:1;
+
+for i = 1:size(CM, 1)
+  switch (i)
+    case 1
+      ratio_harmonic = spline([0 0.25 0.5 0.75 1], [0.3 0.95 0.55 0.15 0], f_harmonic);
+    case 2
+      ratio_harmonic = spline([0 0.25 0.5 0.75 1], [0.4 1.3 0.45 0.20 0], f_harmonic);
+    case 3
+      ratio_harmonic = spline([0 0.25 0.5 0.75 1], [0.5 1.1 0.5 0.13 0], f_harmonic);
+    case 4
+      ratio_harmonic = spline([0 0.25 0.5 0.75 1], [1 2.6 1.0 0.3 0], f_harmonic);
+  end
+  ratio_harmonic = 10 .^ ratio_harmonic;
+  plot(f_harmonic, ratio_harmonic,'color',CM(i,:),'linewidth',5);
+end
+
+xrange = [0 1];
+xlim(xrange);
+yrange = [1e-1 1e3];
+ylim(yrange);
+set(gca, 'yscale', 'log');
+
+
+name = 'ssaep_hypothesis';
+% Constant for font size
+font_size = 20;
+
+%% Figure with labels
+% set ticks on axes
+xticks = [0 0.25 0.5 0.75 1];
+yticks = [1e-1 1e0 1e1 1e2 1e3];
+set(gca, 'XTick', xticks);
[…]

### 2015-07-16 analysis/release/ssavep/plot_hypothesis_ssavep_control.m

@@ -1,0 +1,97 @@
+clear;
+close all;
+
+% Figure window size
+width = 275;   % width of figure (just plot itself, not labels)
+height = 225;  % height of figure (just plot itself, not labels)
+margins = 100; % extra space for labels
+
+%% Create the figure
+
+% make the figure with white background, with fixed size (in pixels) and invisible
+%fgh = figure('Color',[1 1 1],'units','pixels','position',[0 0 (width + 2 * margins) (height + 2 * margins)], 'visible', 'off');
+fgh = figure('Color',[1 1 1],'units','pixels','position',[0 0 (width + 2 * margins) (height + 2 * margins)], 'visible', 'on');
+% make axes with correct margins
+axes('units', 'pixel', 'position', [margins margins width height]);
+hold on; % Allow all channels to be shown
+box on;
+
+
+
+% Get list of channels to plot and colors for each channel
+[ channelToPlot, CM ] = plot_settings();
+
+f_harmonic = 0:0.001:1;
+
+for i = 1:size(CM, 1)
+  ratio_harmonic = spline([0 0.25 0.5 0.75 1], [0 0 0 0 0], f_harmonic);
+  ratio_harmonic = ratio_harmonic + i * 0.02;
+  ratio_harmonic = 10 .^ ratio_harmonic;
+  plot(f_harmonic, ratio_harmonic,'color',CM(i,:),'linewidth',5);
+end
+
+xrange = [0 1];
+xlim(xrange);
+yrange = [1e-1 1e3];
+ylim(yrange);
+set(gca, 'yscale', 'log');
+
+
+name = 'ssavep_hypothesis_control';
+% Constant for font size
+font_size = 20;
+
+%% Figure with labels
+% set ticks on axes
+xticks = [0 0.25 0.5 0.75 1];
+yticks = [1e-1 1e0 1e1 1e2 1e3];
+set(gca, 'XTick', xticks);
+set(gca, 'YTick', yticks);
+% label axes
+xlabel('Frequency (kHz)');
+ylabel('p_{exp} / p_{rest}');
+xlabh = get(gca,'XLabel');
+set(xlabh,'Position',get(xlabh,'Position') ./ [1 (yrange(2) / yrange(1)) ^ 0.05 1]);
+ylabh = get(gca,'YLabel');
+set(ylabh,'Position',get(ylabh,'Position') - [0.10 * diff(xrange) 0 0]);
+
[…]

### 2015-07-16 analysis/release/ssavep/plot_hypothesis_ssvep.m

@@ -1,0 +1,106 @@
+clear;
+close all;
+
+% Figure window size
+width = 275;   % width of figure (just plot itself, not labels)
+height = 225;  % height of figure (just plot itself, not labels)
+margins = 100; % extra space for labels
+
+%% Create the figure
+
+% make the figure with white background, with fixed size (in pixels) and invisible
+%fgh = figure('Color',[1 1 1],'units','pixels','position',[0 0 (width + 2 * margins) (height + 2 * margins)], 'visible', 'off');
+fgh = figure('Color',[1 1 1],'units','pixels','position',[0 0 (width + 2 * margins) (height + 2 * margins)], 'visible', 'on');
+% make axes with correct margins
+axes('units', 'pixel', 'position', [margins margins width height]);
+hold on; % Allow all channels to be shown
+box on;
+
+
+% Get list of channels to plot and colors for each channel
+[ channelToPlot, CM ] = plot_settings();
+
+f_harmonic = 0:0.001:1;
+
+for i = 1:size(CM, 1)
+  switch (i)
+    case 1
+      ratio_harmonic = spline([0 0.25 0.5 0.75 1], [0.3 0.95 0.55 0.15 0], f_harmonic);
+    case 2
+      ratio_harmonic = spline([0 0.25 0.5 0.75 1], [0.4 1.3 0.45 0.20 0], f_harmonic);
+    case 3
+      ratio_harmonic = spline([0 0.25 0.5 0.75 1], [0.5 1.1 0.5 0.13 0], f_harmonic);
+    case 4
+      ratio_harmonic = spline([0 0.25 0.5 0.75 1], [0.6 1.2 0.5 0.20 0], f_harmonic);
+  end
+  ratio_harmonic = 10 .^ ratio_harmonic;
+  plot(f_harmonic, ratio_harmonic,'color',CM(i,:),'linewidth',5);
+end
+
+xrange = [0 1];
+xlim(xrange);
+yrange = [1e-1 1e3];
+ylim(yrange);
+set(gca, 'yscale', 'log');
+
+
+name = 'ssvep_hypothesis';
+% Constant for font size
+font_size = 20;
+
+%% Figure with labels
+% set ticks on axes
+xticks = [0 0.25 0.5 0.75 1];
+yticks = [1e-1 1e0 1e1 1e2 1e3];
+set(gca, 'XTick', xticks);
[…]

### 2015-07-16 analysis/release/ssavep/plot_ssavep.m

@@ -74,9 +74,10 @@ margins = 100; % extra space for labels
 %end
 xrange = [0 4800];
 %xrange = [0 1000];
-yrange = (10 .^ [-1 3]);                          % y-axis limits
+%yrange = (10 .^ [-1 3]);                          % y-axis limits
+yrange = (10 .^ [-4 1]);                          % y-axis limits
 xticks = linspace(xrange(1), xrange(2), 5);       % tick marks on x-axis
-yticks = logspace(log10(yrange(1)), log10(yrange(2)), 5); % tick marks on y-axis
+yticks = logspace(log10(yrange(1)), log10(yrange(2)), 6); % tick marks on y-axis
 
 % constants for computing power spectral density (psd)
 windlength = windlengthSeconds * fs;     % window length
@@ -94,7 +95,7 @@ SPLICING = (nargin >= 15);
 %% Create the figure
 
 % make the figure with white background, with fixed size (in pixels) and invisible
-fgh = figure('Color',[1 1 1],'units','pixels','position',[0 0 (width + 2 * margins) (height + 2 * margins)], 'visible', 'on');
+fgh = figure('Color',[1 1 1],'units','pixels','position',[0 0 (width + 2 * margins) (height + 2 * margins)], 'visible', 'off');
 % make axes with correct margins
 axes('units', 'pixel', 'position', [margins margins width height]);
 hold on; % Allow all channels to be shown
@@ -227,6 +228,7 @@ for ii=1:size(data, 1)
 
     % ratio of experimental psd to resting psd
     ratio = expPSDs ./ ctrPSDs;
+    ratio = ctrPSDs;
     
     % get harmonics of stimulus
     num_harmonics = floor(f(end)/frequency);      % highest harmonic that is relevant

### 2015-07-16 analysis/release/ssavep/plot_ssavep_baseline.m

@@ -1,4 +1,4 @@
-function [ fgh ] = plot_ssavep_baseline(data, fgh, cleanDigitalIn, name, ssavep, fs, cardiac_data, windlengthSeconds, noverlapPercent, filters, cardiac_filters, CM, channelNames, comment, data2, cleanDigitalIn2, cardiac_data2)
+function [ fgh ] = plot_ssavep_baseline(data, fgh, final, cleanDigitalIn, name, ssavep, fs, cardiac_data, windlengthSeconds, noverlapPercent, filters, cardiac_filters, CM, channelNames, comment, data2, cleanDigitalIn2, cardiac_data2)
 %PLOT_SSAVEP  Plots the SSAEP/SSVEP response for a single run.
 %
 % FGH = PLOT_SSAVEP(DATA, CLEANDIGITALIN, NAME, EXPERIMENT, FS, ...
@@ -84,31 +84,32 @@ windlength = windlengthSeconds * fs;     % window length
 noverlap = windlength * noverlapPercent; % number of overlap timesteps
 
 % Thresholds for being considered close to a harmonic
-threshold_60 = 3;        % Threshold for 60 Hz harmonics
+threshold_60 = 6;        % Threshold for 60 Hz harmonics
 threshold_harmonics = 3; % Threshold to be considered a harmonic
 
 % whether or not to plot points on harmonics
 harmonic_points = false;
 
-SPLICING = (nargin >= 16);
+SPLICING = (nargin >= 17);
 
 %% Create the figure
 
-final = (fgh ~= -1); % TODO
+%final = (fgh ~= -1); % TODO
 if (fgh == -1)
     % make the figure with white background, with fixed size (in pixels) and invisible
     fgh = figure('Color',[1 1 1],'units','pixels','position',[0 0 (width + 2 * margins) (height + 2 * margins)], 'visible', 'on');
     % make axes with correct margins
     axes('units', 'pixel', 'position', [margins margins width height]);
     hold on; % Allow all channels to be shown
-else
-    for ii=1:size(data, 1)
-        %color = 0.65 * [1 1 1]; % default color for scalp electrodes
-        %if strcmp(channelNames(ii), 'Endo')
-            %color = CM(ii,:) + 0.6 * (1 - CM(ii,:)); % special color for endo
-        %end
[…]
